---
title: "Adjust P (MAR) — Moderation Multiple-Comparison Correction"
author: "Siyuan Huang"
date: "2026-05-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

set.seed(42)
```

## Multiple-comparison correction for H3 moderation effects (MAR 175 & Follow-Up Only 84)

This corrects p-values for the H3 attitude-change **moderation** analysis for
**both** the MAR full sample (175) and the Follow-Up Only completer sample (84),
under one scheme so the two are comparable. Two points define the correction
family:

1. **Only the focal moderation terms enter the family.** The hypothesis is
   *whether the moderator alters the change over `Phase` (and its dependence on
   `Label`)* — i.e. the interaction terms involving the moderator. Main effects
   (`Phase`, `Label`, `ModeratorScore`) and covariates (`Age`, `Gender`,
   `Field`, `Used_LLM_Hours`, `BaselineScore`) are not tested and are excluded
   (including them inflated the family ~3× and made Holm far too conservative).
2. **`mod == outcome` baseline-adjusted models are dropped** (`BaselineScore`
   models with no `ModeratorScore` term are not moderation tests).

Family = focal terms, corrected **within each DV** and **separately for PF
(Pre→Follow) and PPF (Pre→Post→Follow)** (different outcome sets and phase
structure). Holm (FWER) and BH (FDR) both reported; for an exploratory
10-moderator screen **BH/FDR is primary**, Holm a conservative check.

```{r multiple-comparison-correction-for-h3-moderation-1, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
library(readxl)
library(openxlsx)

# Focal moderation terms = interaction terms involving the moderator.
# If a single focal term is pre-specified per model, set focal_terms to just
# that one (e.g. "Phase:ModeratorScore") to shrink the family to one test per
# outcome x moderator.
focal_terms <- c(
  "Phase:ModeratorScore",
  "Label:ModeratorScore",
  "Phase:Label:ModeratorScore"
)

adjust_moderation <- function(path_in, path_out, analysis_label) {
  mods <- read_xlsx(path_in)

  mods_focal <- mods %>%
    filter(DV != Moderator) %>%        # drop mod == outcome baseline models
    filter(Term %in% focal_terms)      # keep only focal moderation terms

  mods_adj <- mods_focal %>%
    group_by(DV) %>%
    mutate(
      n_in_family = n(),
      p_holm = p.adjust(p_value, method = "holm"),
      p_BH   = p.adjust(p_value, method = "BH")
    ) %>%
    ungroup() %>%
    mutate(Analysis = analysis_label, .before = 1) %>%
    arrange(DV, p_value)

  if (!dir.exists(dirname(path_out))) {
    dir.create(dirname(path_out), recursive = TRUE)
  }
  write.xlsx(mods_adj, path_out, overwrite = TRUE)

  cat("\n===", analysis_label, "=== family sizes per DV:\n")
  print(mods_adj %>% distinct(DV, n_in_family))
  cat("\nSurviving BH < .05:\n")
  print(as.data.frame(mods_adj %>% filter(p_BH < 0.05)))
  cat("\nSurviving Holm < .05:\n")
  print(as.data.frame(mods_adj %>% filter(p_holm < 0.05)))

  mods_adj
}

# --- MAR sample (175) -------------------------------------------------------
mar_pf <- adjust_moderation(
  "results/MAR/H3/H3_Attitude_Longterm_Moderation_Summary_PF.xlsx",
  "results/MAR/H3/H3_Moderation_Padjust_PF.xlsx",
  "MAR | Pre-Follow"
)

mar_ppf <- adjust_moderation(
  "results/MAR/H3/H3_Attitude_Longterm_Moderation_Summary_PPF.xlsx",
  "results/MAR/H3/H3_Moderation_Padjust_PPF.xlsx",
  "MAR | Pre-Post-Follow"
)

# --- Follow-Up Only sample (84, completer) ---------------------------------
# This Rmd lives in MAR/; the Follow-Up Only results are in the sibling
# "Follow-Up Completers Only/" folder, hence the "../Follow-Up Completers Only/"
# prefix.
fu_pf <- adjust_moderation(
  "../Follow-Up Completers Only/results/Follow-Up Activity/H3/H3_Attitude_Longterm_Moderation_Summary_PF.xlsx",
  "../Follow-Up Completers Only/results/Follow-Up Activity/H3/H3_Moderation_Padjust_PF.xlsx",
  "FollowUpOnly | Pre-Follow"
)

fu_ppf <- adjust_moderation(
  "../Follow-Up Completers Only/results/Follow-Up Activity/H3/H3_Attitude_Longterm_Moderation_Summary_PPF.xlsx",
  "../Follow-Up Completers Only/results/Follow-Up Activity/H3/H3_Moderation_Padjust_PPF.xlsx",
  "FollowUpOnly | Pre-Post-Follow"
)
```

## Multiple-comparison correction for H3 Performance & Confidence moderation (MAR 175 & Follow-Up Only)

Same scheme for the accuracy and confidence long-term moderation models, for
**both** samples. These span the four phases (`stage1`/`stage2`/`stage3`/`follow`)
with `Phase * Label * ModeratorScore`, so the focal family matches the attitude
analysis: the moderator interactions. The `DV != Moderator` filter is a no-op
and no baseline-adjusted models exist to drop. Family corrected **within each
DV** (accuracy, confidence); Holm and BH reported, BH/FDR primary.

```{r multiple-comparison-correction-for-h3-performance-1, message=FALSE, warning=FALSE, echo=TRUE}
mar_perf_conf <- adjust_moderation(
  "results/MAR/H3/H3_Performance_Confidence_Longterm_Moderation_Summary.xlsx",
  "results/MAR/H3/H3_Performance_Confidence_Moderation_Padjust.xlsx",
  "MAR | Performance & Confidence (Stage1-3, Follow)"
)

# --- Follow-Up Only sample (completer) -------------------------------------
# This Rmd lives in MAR/; the Follow-Up Only results are in the sibling
# "Follow-Up Completers Only/" folder, hence the "../Follow-Up Completers Only/"
# prefix.
fu_perf_conf <- adjust_moderation(
  "../Follow-Up Completers Only/results/Follow-Up Activity/H3/H3_Performance_Confidence_Longterm_Moderation_Summary.xlsx",
  "../Follow-Up Completers Only/results/Follow-Up Activity/H3/H3_Performance_Confidence_Moderation_Padjust.xlsx",
  "FollowUpOnly | Performance & Confidence (Stage1-3, Follow)"
)
```

## Reproducibility

```{r session-info}
sessionInfo()
```
