---
title: "Study 2 — Dropout vs. Completer Comparison"
author: "Siyuan Huang"
date: "2025-10-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

set.seed(42)
```

# Study 2 — Dropout vs. Completer Comparison

To characterise attrition, this document compares participants who
completed the follow-up session (`drop == 0`) with those who did not
(`drop == 1`) on baseline and initial-session measures. For each measure
we report per-group descriptive statistics and a Welch two-sample
t-test. Variables that differ significantly between groups are the
candidate dropout predictors used as attrition-adjustment covariates in
the follow-up sensitivity analyses.

As elsewhere in Study 2, participants with a Stage-1 baseline (task 0)
accuracy of `>= 0.90` are excluded by a ceiling-effect screen.

## Packages
```{r packages-1}
library(broom)
library(car)
library(DescTools)
library(dplyr)
library(DT)
library(effectsize)
library(emmeans)
library(ggplot2)
library(janitor)
library(lme4)
library(lmerTest)
library(lsr)
library(MASS)
library(openxlsx)
library(ordinal)
library(performance)
library(readxl)
library(stringr)
library(tidyr)
library(report)
library(interactions)
```

## Data Preprocessing

The full-sample data are loaded, the ceiling-effect screen
(`stage1_task0_accuracy < 0.9`) is applied, and background variables are
recoded. The `drop` indicator (0 = completed follow-up, 1 = did not)
defines the comparison groups.

```{r data-preprocessing-1}
# Load Data
df <- read_xlsx("data/Study_2_Full_Data.xlsx")
```

```{r data-preprocessing-2}
# Create a named vector to define the new column names
# The format is: "new_name" = "old_name"
rename_vars <- c(
  "Pre_GLAT_Objective_AI_Literacy",
  "Pre_AILS_CCS_Subjective_AI_Literacy",
  "Pre_AI_Trust",
  "Pre_AI_Usefulness",
  "Pre_AI_Affect",
  "Pre_AI_Self_Efficacy",
  "Pre_Behavioral_Intention",
  
  "stage1_task0_accuracy",
  "stage1_task1_accuracy",
  "stage1_task2_accuracy",
  "stage1_task3_accuracy",
  "stage2_task0_accuracy",
  "stage2_task1_accuracy",
  "stage2_task2_accuracy",
  "stage2_task3_accuracy",
  "stage3_task0_accuracy",
  "stage3_task1_accuracy",
  "stage3_task2_accuracy",
  "stage3_task3_accuracy",
  
  "stage1_task0_confidence",
  "stage1_task1_confidence",
  "stage1_task2_confidence",
  "stage1_task3_confidence",
  "stage2_task0_confidence",
  "stage2_task1_confidence",
  "stage2_task2_confidence",
  "stage2_task3_confidence",
  "stage3_task0_confidence",
  "stage3_task1_confidence",
  "stage3_task2_confidence",
  "stage3_task3_confidence",

  "stage2_task0_willing",
  "stage2_task1_willing",
  "stage2_task2_willing",
  "stage2_task3_willing",
  "stage3_task0_willing",
  "stage3_task1_willing",
  "stage3_task2_willing",
  "stage3_task3_willing",

  "stage2_task0_useful",
  "stage2_task1_useful",
  "stage2_task2_useful",
  "stage2_task3_useful",
  "stage3_task0_useful",
  "stage3_task1_useful",
  "stage3_task2_useful",
  "stage3_task3_useful",

  "Post_AI_Trust",
  "Post_AI_Usefulness",
  "Post_AI_Affect",
  "Post_Behavioral_Intention"
)

# Convert the 'Label' column into a factor data type
df$Label <- factor(df$Label, levels = c("AI", "AI Human", "Human"))
```

```{r data-preprocessing-3}
ggplot(df, aes(x = stage1_task0_accuracy)) +
  geom_histogram(binwidth = 0.05, fill = "skyblue", color = "black") +
  stat_bin(binwidth=0.05, geom="text", aes(label=..count..), vjust=-0.3) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = sprintf("%.2f", seq(0, 1, by = 0.05))) +
  labs(title = "Distribution of stage1_task0_accuracy", x = "stage1_task0_accuracy", y = "Frequency") +
  theme(axis.text.x = element_text(angle=45, hjust=1))
```

```{r data-preprocessing-4}
Count <- sum(df$stage1_task0_accuracy >= 0.9)
Count

df <- df %>%
  filter(stage1_task0_accuracy < 0.9)
```

```{r data-preprocessing-5}
# Statistical Background: 1-8 scale -> 3-level factor
df$Stats_Background <- cut(
  as.numeric(as.character(df$Stats_Background)),
  breaks = c(1, 3, 5, 8),
  labels = c("Low", "Medium", "High"),
  right = TRUE,
  include.lowest = TRUE
)

df$Used_LLM_Frequency <- forcats::fct_collapse(
  as.character(df$Used_LLM_Frequency),
  Rarely = c("Never", "Less than once a month", "1–3 times per month"),
  Often  = c("Weekly", "Daily")
)
df$Used_LLM_Hours <- forcats::fct_collapse(
  as.character(df$Used_LLM_Hours),
  None = "0",
  Low  = c("1–5", "6–10"),
  High = c("11–20", ">20")
)
```

```{r data-preprocessing-6}
summary(df$Label)
```

## Dropout vs. Completer Comparison

Each measure below is compared between completers (`drop == 0`) and
non-completers (`drop == 1`) via per-group means/SDs and a Welch
two-sample t-test.

### Accuracy
#### Descriptive
```{r descriptive-1}
drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(stage1_task0_accuracy, na.rm=TRUE), 2),
    SD = round(sd(stage1_task0_accuracy, na.rm=TRUE), 2),
  )
drop_table

drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(stage2_task0_accuracy, na.rm=TRUE), 2),
    SD = round(sd(stage2_task0_accuracy, na.rm=TRUE), 2),
  )
drop_table

drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(stage3_task0_accuracy, na.rm=TRUE), 2),
    SD = round(sd(stage3_task0_accuracy, na.rm=TRUE), 2),
  )
drop_table
```

#### T-Tests
```{r t-tests-1}
cat("Stage 1\n")
t.test(df$stage1_task0_accuracy~df$drop)
cat("Stage 2\n")
t.test(df$stage2_task0_accuracy~df$drop)
cat("Stage 3\n")
t.test(df$stage3_task0_accuracy~df$drop)
```

### Confidence
#### Descriptive
```{r descriptive-2}
drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(stage1_task0_confidence, na.rm=TRUE), 2),
    SD = round(sd(stage1_task0_confidence, na.rm=TRUE), 2),
  )
drop_table

drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(stage2_task0_confidence, na.rm=TRUE), 2),
    SD = round(sd(stage2_task0_confidence, na.rm=TRUE), 2),
  )
drop_table

drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(stage3_task0_confidence, na.rm=TRUE), 2),
    SD = round(sd(stage3_task0_confidence, na.rm=TRUE), 2),
  )
drop_table
```

#### T-Tests
```{r t-tests-2}
cat("Stage 1\n")
t.test(df$stage1_task0_confidence~df$drop)
cat("Stage 2\n")
t.test(df$stage2_task0_confidence~df$drop)
cat("Stage 3\n")
t.test(df$stage3_task0_confidence~df$drop)
```

### AI Trust
#### Descriptive
```{r descriptive-3}
drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(Pre_AI_Trust, na.rm=TRUE), 2),
    SD = round(sd(Pre_AI_Trust, na.rm=TRUE), 2),
  )
drop_table

drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(Post_AI_Trust, na.rm=TRUE), 2),
    SD = round(sd(Post_AI_Trust, na.rm=TRUE), 2),
  )
drop_table
```

#### T-Tests
```{r t-tests-3}
cat("Pre AI Trust\n")
t.test(df$Pre_AI_Trust~df$drop)
cat("Post AI Trust\n")
t.test(df$Post_AI_Trust~df$drop)
```

### AI Affect
#### Descriptive
```{r descriptive-4}
drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(Pre_AI_Affect, na.rm=TRUE), 2),
    SD = round(sd(Pre_AI_Affect, na.rm=TRUE), 2),
  )
drop_table

drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(Post_AI_Affect, na.rm=TRUE), 2),
    SD = round(sd(Post_AI_Affect, na.rm=TRUE), 2),
  )
drop_table
```

#### T-Tests
```{r t-tests-4}
cat("Pre AI Affect\n")
t.test(df$Pre_AI_Affect~df$drop)
cat("Post AI Affect\n")
t.test(df$Post_AI_Affect~df$drop)
```

### AI Usefulness
#### Descriptive
```{r descriptive-5}
drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(Pre_AI_Usefulness, na.rm=TRUE), 2),
    SD = round(sd(Pre_AI_Usefulness, na.rm=TRUE), 2),
  )
drop_table

drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(Post_AI_Usefulness, na.rm=TRUE), 2),
    SD = round(sd(Post_AI_Usefulness, na.rm=TRUE), 2),
  )
drop_table
```

#### T-Tests
```{r t-tests-5}
cat("Pre AI Usefulness\n")
t.test(df$Pre_AI_Usefulness~df$drop)
cat("Post AI Usefulness\n")
t.test(df$Post_AI_Usefulness~df$drop)
```

### Behavior Intention
#### Descriptive
```{r descriptive-6}
drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(Pre_Behavioral_Intention, na.rm=TRUE), 2),
    SD = round(sd(Pre_Behavioral_Intention, na.rm=TRUE), 2),
  )
drop_table

drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(Post_Behavioral_Intention, na.rm=TRUE), 2),
    SD = round(sd(Post_Behavioral_Intention, na.rm=TRUE), 2),
  )
drop_table
```

#### T-Tests
```{r t-tests-6}
cat("Pre Behavior Intention\n")
t.test(df$Pre_Behavioral_Intention~df$drop)
cat("Post Behavior Intention\n")
t.test(df$Post_Behavioral_Intention~df$drop)
```

### AI Efficacy
#### Descriptive
```{r descriptive-7}
drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(Pre_AI_Self_Efficacy, na.rm=TRUE), 2),
    SD = round(sd(Pre_AI_Self_Efficacy, na.rm=TRUE), 2),
  )
drop_table
```

#### T-Tests
```{r t-tests-7}
cat("Pre Efficacy\n")
t.test(df$Pre_AI_Self_Efficacy~df$drop)
```

### Objective Literacy
#### Descriptive
```{r descriptive-8}
drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(Pre_GLAT_Objective_AI_Literacy, na.rm=TRUE), 2),
    SD = round(sd(Pre_GLAT_Objective_AI_Literacy, na.rm=TRUE), 2),
  )
drop_table
```

#### T-Tests
```{r t-tests-8}
cat("Pre Objective Literacy\n")
t.test(df$Pre_GLAT_Objective_AI_Literacy~df$drop)
```

### Subjective Literacy
#### Descriptive
```{r descriptive-9}
drop_table <- df %>%
  group_by(drop) %>%
  summarise(
    Mean = round(mean(Pre_AILS_CCS_Subjective_AI_Literacy, na.rm=TRUE), 2),
    SD = round(sd(Pre_AILS_CCS_Subjective_AI_Literacy, na.rm=TRUE), 2),
  )
drop_table
```

#### T-Tests
```{r t-tests-9}
cat("Pre Subjective Literacy\n")
t.test(df$Pre_AILS_CCS_Subjective_AI_Literacy~df$drop)
```

## Reproducibility

```{r session-info}
sessionInfo()
```
