---
title: "Study 1 — Subjective Ratings: Mixed Models"
author: "Siyuan Huang"
date: "2025-04-25"
output:
  cleanrmd::html_document_clean:
    theme: marx
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  highlight = TRUE,
  message = FALSE,
  warning = FALSE
)

set.seed(42)
```

# Overview

This document models overall response quality (the mean of the four
rating dimensions) for Top vs. Bottom models, as judged by the two rater
groups (students, instructors). The primary model (`model1`) clusters
repeated ratings on the explanation output (`Model × Task × Iteration`)
via `(1 | Explanation)` — the unit the eight raters score in common —
together with `(1 | Rater)`. This primary model is reported in full with
Type-III ANOVA, effect sizes, post-hoc contrasts, and diagnostics. A
supplementary section then refits the model with random effects of `(1 | Attempt)` together with `(1 | Rater)`.

## Packages

```{r packages}
library(readxl)
library(dplyr)
library(stringr)
library(lme4)
library(lmerTest)
library(car)
library(effectsize)
library(emmeans)
library(performance)
library(report)
library(ggplot2)
```

## Load Data

```{r load-data}
df <- read_excel("data/Study_1_Subjective_Data.xlsx")
head(df)
```

## Recode Core Variables

Design variables are coerced to factors; a unique `Rater` identifier and
the composite `OverallQuality` outcome are constructed, and models are
grouped into Top/Bottom/Other from the objective benchmark ranking.

```{r recode-core}
df <- df %>%
  mutate(
    Model = factor(Model),
    Profession = factor(Profession),
    Task = factor(Task),
    Iteration = factor(Iteration),
    ID = factor(ID),
    RaterGroup = Profession,
    Attempt = Iteration,
    Rater = factor(paste(RaterGroup, ID, sep = "_")),
    # Explanation = the unique output that all raters score in common
    # (Model × Task × Iteration), used as the repeated-measures
    # clustering unit in the primary model.
    Explanation = factor(paste(Model, Task, Iteration, sep = "_")),
    OverallQuality = rowMeans(
      across(
        c(
          Statistical_Accuracy,
          Clarity_and_Structure,
          Conceptual_Depth,
          Pedagogical_Effectiveness
        )
      ),
      na.rm = TRUE
    ),
    ModelGroup = case_when(
      str_detect(Model, regex("ChatGPT_4o", ignore_case = TRUE)) ~ "Top",
      str_detect(Model, regex("ChatGPT_o1", ignore_case = TRUE)) ~ "Top",
      str_detect(Model, regex("Grok3", ignore_case = TRUE)) ~ "Bottom",
      str_detect(Model, regex("Gemini_2\\.0", ignore_case = TRUE)) ~ "Bottom",
      TRUE ~ "Other"
    ),
    ModelGroup = factor(ModelGroup, levels = c("Bottom", "Top", "Other"))
  )

# Sanity check: number of unique explanation outputs, and how many raters
# score each one (should be a constant panel size of 8).
length(levels(df$Explanation))
table(table(df$Explanation))
```

## Filter Top and Bottom Models

```{r filter-top-bottom}
df_tb <- df %>%
  filter(ModelGroup %in% c("Top", "Bottom")) %>%
  droplevels()
```

## Model Fitting

### Raw Data Plot

```{r raw-plot}
ggplot(df, aes(x = ModelGroup, y = OverallQuality)) +
  geom_point(aes(color = Rater)) +
  geom_smooth(method = "lm", se = FALSE, aes(group = Rater, color = Rater)) +
  facet_wrap(~Rater) +
  theme_minimal()
```

### Model 1 — Primary: `(1 | Rater) + (1 | Explanation)`

```{r model1}
# Model 1 (primary): repeated ratings are clustered on the
# explanation output (Model × Task × Iteration) via (1 | Explanation),
# the unit the 8 raters score in common.
model1 <- lmer(
  OverallQuality ~ ModelGroup * RaterGroup * Task +
    (1 | Rater) + (1 | Explanation),
  data = df
)

summary(model1)
```

### Standardised Parameters

```{r model1-standardized}
standardize_parameters(model1)
```

### Type-III ANOVA and Effect Sizes

```{r model1-anova}
aov_model1 <- anova(model1)
aov_model1
eta_squared(model1)
```

### Post-hoc

```{r model1-posthoc}
emmeans(model1, pairwise ~ ModelGroup, infer = c(TRUE, TRUE))
emmip(model1, RaterGroup ~ ModelGroup, CIs = TRUE)
```

```{r model1-posthoc-interaction}
emmeans(model1, pairwise ~ ModelGroup * RaterGroup, infer = c(TRUE, TRUE))
```

```{r model1-report}
report(aov_model1)
```

### Diagnostics

```{r model1-diagnostics}
performance::check_model(model1)
performance::check_collinearity(model1)

res <- residuals(model1)
qqnorm(res)
qqline(res)
```

---

# Supplementary Analysis — Original Iteration-Only Clustering

## Refit with `(1 | Attempt)`

```{r model1-attempt}
model1_attempt <- lmer(
  OverallQuality ~ ModelGroup * RaterGroup * Task +
    (1 | Rater) + (1 | Attempt),
  data = df
)

summary(model1_attempt)
```

## Comparing the two clustering structures

```{r model1-attempt-compare}
compare_performance(model1, model1_attempt, rank = TRUE)
VarCorr(model1)          # primary: explanation-level SD is non-zero
VarCorr(model1_attempt)  # iteration-only: Attempt variance is estimated at 0
```

## Inferential consequence

```{r model1-attempt-anova}
aov_model1_attempt <- anova(model1_attempt)
aov_model1_attempt
```

### Post-hoc

```{r model1-attempt-posthoc}
emmeans(model1_attempt, pairwise ~ ModelGroup, infer = c(TRUE, TRUE))
emmip(model1_attempt, RaterGroup ~ ModelGroup, CIs = TRUE)
```

```{r model1-attempt-posthoc-interaction}
emmeans(model1_attempt, pairwise ~ ModelGroup * RaterGroup, infer = c(TRUE, TRUE))
```

Relative to the primary model, the iteration-only structure assigns the
between-explanation terms (e.g. `ModelGroup`, `ModelGroup:Task`) a larger
denominator df — 270 versus 30 — and correspondingly smaller standard
errors. Under this structure the `ModelGroup × Task` interaction reaches
p ≈ .034, whereas under the explanation-level structure it is p ≈ .072.
The main `ModelGroup` effect and the `ModelGroup × RaterGroup` interaction
are significant under both structures, so the headline Top > Bottom
conclusion is unchanged.

## Reproducibility

```{r session-info}
sessionInfo()
```
