---
title: "Study 1 — Subjective Ratings: Descriptive Results"
author: "Siyuan Huang"
date: "2025-07-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

set.seed(42)
```

# Overview

This document summarises the Study 1 subjective ratings: human raters
(students and instructors) scored model responses on four dimensions
(statistical accuracy, clarity and structure, conceptual depth, and
pedagogical effectiveness). Ratings are reshaped to long format and
summarised overall and by model group, rater profession, model, task,
and dimension. The "Top"/"Bottom" model grouping mirrors the objective
benchmark ranking.

## Packages

```{r packages}
library(readxl)
library(dplyr)
library(tidyr)
library(stringr)
```

## Load Data

```{r load-data}
df <- read_excel("data/Study_1_Subjective_Data.xlsx")
head(df)
```

## Recode Factors

```{r factor-recode}
df <- df %>%
  mutate(
    Model = factor(Model),
    Profession = factor(Profession),
    ID = factor(ID)
  )
```

## Reshape to Long Format

```{r long-format}
df_long <- df %>%
  pivot_longer(
    cols = c(
      Statistical_Accuracy,
      Clarity_and_Structure,
      Conceptual_Depth,
      Pedagogical_Effectiveness
    ),
    names_to = "Dimension",
    values_to = "Rating"
  )
df_long
```

## Assign Model Group

Models are grouped into Top, Bottom, or Other based on the objective
benchmark ranking.

```{r model-group}
df_long_tb <- df_long %>%
  mutate(
    ModelGroup = case_when(
      str_detect(Model, regex("ChatGPT_4o", ignore_case = TRUE)) ~ "Top",
      str_detect(Model, regex("ChatGPT_o1", ignore_case = TRUE)) ~ "Top",
      str_detect(Model, regex("Grok3", ignore_case = TRUE)) ~ "Bottom",
      str_detect(Model, regex("Gemini_2\\.0", ignore_case = TRUE)) ~ "Bottom",
      TRUE ~ "Other"
    ),
    ModelGroup = factor(ModelGroup, levels = c("Top", "Bottom", "Other"))
  )
```

## Top vs. Bottom: Overall Summary

```{r top-bottom-overall}
TopBottom_comparison_overall <- df_long_tb %>%
  group_by(ModelGroup) %>%
  summarise(
    Mean_Rating = mean(Rating, na.rm = TRUE),
    SD_Rating = sd(Rating, na.rm = TRUE),
    .groups = "drop"
  )
TopBottom_comparison_overall
```

## Student Summary by Model and Task

```{r student-summary}
df_long_tb_stu <- df_long_tb %>%
  filter(Profession == "Student")

stu <- df_long_tb_stu %>%
  group_by(Model, Task) %>%
  summarise(
    Mean_Rating = mean(Rating, na.rm = TRUE),
    SD_Rating = sd(Rating, na.rm = TRUE),
    .groups = "drop"
  )
stu
```

## Instructor Summary by Model and Task

```{r instructor-summary}
df_long_tb_ins <- df_long_tb %>%
  filter(Profession == "Instructor")

ins <- df_long_tb_ins %>%
  group_by(Model, Task) %>%
  summarise(
    Mean_Rating = mean(Rating, na.rm = TRUE),
    SD_Rating = sd(Rating, na.rm = TRUE),
    .groups = "drop"
  )
ins
```

## Full Summary by Dimension, Model, Task, and Profession

```{r full-summary}
all <- df_long_tb %>%
  group_by(Dimension, Model, Task, Profession) %>%
  summarise(
    Mean_Rating = mean(Rating, na.rm = TRUE),
    SD_Rating = sd(Rating, na.rm = TRUE),
    .groups = "drop"
  )
all
```

## Reproducibility

```{r session-info}
sessionInfo()
```
