---
title: "Study 2 Results"
author: "Spike Huang"
date: "2025-07-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Study 2 Results
## Load Packages
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
library(broom)
library(car)
library(DescTools)
library(dplyr)
library(DT)
library(effectsize)
library(emmeans)
library(ggplot2)
library(janitor)
library(lme4)
library(lmerTest)
library(lsr)
library(MASS)
library(openxlsx)
library(ordinal)
library(performance)
library(readxl)
library(stringr)
library(tidyr)
library(report)
library(interactions)
```

## Data Preprocessing
```{r, message=FALSE, warning=FALSE, echo=TRUE}
df <- read_xlsx("data/Study_2_Followup_Data.xlsx")
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
# Define Variables and Factor Levels
rename_vars <- c(
  "Pre_GLAT_Objective_AI_Literacy",
  "Pre_AILS_CCS_Subjective_AI_Literacy",
  "Pre_AI_Trust",
  "Pre_AI_Usefulness",
  "Pre_AI_Affect",
  "Pre_AI_Self_Efficacy",
  "Pre_Behavioral_Intention",
  "stage1_task0_accuracy",
  "stage1_task1_accuracy",
  "stage1_task2_accuracy",
  "stage1_task3_accuracy",
  "stage2_task0_accuracy",
  "stage2_task1_accuracy",
  "stage2_task2_accuracy",
  "stage2_task3_accuracy",
  "stage3_task0_accuracy",
  "stage3_task1_accuracy",
  "stage3_task2_accuracy",
  "stage3_task3_accuracy",
  "stage1_task0_confidence",
  "stage1_task1_confidence",
  "stage1_task2_confidence",
  "stage1_task3_confidence",
  "stage2_task0_confidence",
  "stage2_task1_confidence",
  "stage2_task2_confidence",
  "stage2_task3_confidence",
  "stage3_task0_confidence",
  "stage3_task1_confidence",
  "stage3_task2_confidence",
  "stage3_task3_confidence",
  "stage2_task0_willing",
  "stage2_task1_willing",
  "stage2_task2_willing",
  "stage2_task3_willing",
  "stage3_task0_willing",
  "stage3_task1_willing",
  "stage3_task2_willing",
  "stage3_task3_willing",
  "stage2_task0_useful",
  "stage2_task1_useful",
  "stage2_task2_useful",
  "stage2_task3_useful",
  "stage3_task0_useful",
  "stage3_task1_useful",
  "stage3_task2_useful",
  "stage3_task3_useful",
  "Post_AI_Trust",
  "Post_AI_Usefulness",
  "Post_AI_Affect",
  "Post_Behavioral_Intention"
)

df$Label <- factor(df$Label, levels = c("AI", "AI Human", "Human"))
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
# Check Distribution
ggplot(df, aes(x = stage1_task0_accuracy)) +
  geom_histogram(binwidth = 0.05, fill = "skyblue", color = "black") +
  stat_bin(binwidth = 0.05, geom = "text", aes(label = ..count..), vjust = -0.3) +
  scale_x_continuous(
    breaks = seq(0, 1, by = 0.05),
    labels = sprintf("%.2f", seq(0, 1, by = 0.05))
  ) +
  labs(
    title = "Distribution of stage1_task0_accuracy",
    x = "stage1_task0_accuracy",
    y = "Frequency"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
# Filter Out stage1_task0_accuracy >= 0.9
Count <- sum(df$stage1_task0_accuracy >= 0.9)
Count

df <- df %>%
  filter(stage1_task0_accuracy < 0.9)
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
# Recode Background and LLM Usage
df$Stats_Background <- cut(
  as.numeric(as.character(df$Stats_Background)),
  breaks = c(1, 3, 5, 8),
  labels = c("Low", "Medium", "High"),
  right = TRUE,
  include.lowest = TRUE
)

df$Used_LLM_Frequency <- forcats::fct_collapse(
  as.character(df$Used_LLM_Frequency),
  Rarely = c("Never", "Less than once a month", "1–3 times per month"),
  Often  = c("Weekly", "Daily")
)

df$Used_LLM_Hours <- forcats::fct_collapse(
  as.character(df$Used_LLM_Hours),
  None = "0",
  Low  = c("1–5", "6–10"),
  High = c("11–20", ">20")
)
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
summary(df$Label)
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
# Convert To Longer Table
cols_to_long <- grep("^(Pre|Post|stage\\d+|follow)_", colnames(df), value = TRUE)

df_long <- df %>%
  pivot_longer(
    cols = all_of(cols_to_long),
    names_to = "fullvar",
    values_to = "Value"
  ) %>%
  mutate(
    Phase = str_extract(fullvar, "^(Pre|Post|stage\\d+|follow)"),
    tmp = str_remove(fullvar, "^(Pre|Post|stage\\d+|follow)_"),
    task = ifelse(str_detect(tmp, "^task\\d+"), str_extract(tmp, "^task\\d+"), NA),
    measure = ifelse(!is.na(task), str_remove(tmp, "^task\\d+_"), tmp),
    tmp = NULL,
    fullvar = NULL
  )

df_long$Phase <- factor(df_long$Phase, levels = c("follow", "Post", "stage3", "stage2", "stage1", "Pre"))
df_long$Task <- as.factor(df_long$task)

df_long <- df_long %>%
  dplyr::select(-task)

df_long$Label <- as.factor(df_long$Label)
df_long$ID <- as.factor(df_long$ID)

head(df_long)
```

## Pre-Survey Comparison By Label (Follow-Up Only)
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
# Descriptive Statistics By Label
varnames <- rename_vars[1:7]

label_summary <- lapply(varnames, function(var) {
  df %>%
    group_by(Label) %>%
    summarise(
      Mean = round(mean(.data[[var]], na.rm = TRUE), 2),
      SD = round(sd(.data[[var]], na.rm = TRUE), 2),
      n = sum(!is.na(.data[[var]]))
    ) %>%
    mutate(Variable = var) %>%
    relocate(Variable)
})

label_summary_table <- bind_rows(label_summary)
label_summary_table
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
# ANOVA By Label
anova_results <- lapply(varnames, function(var) {
  aov_res <- summary(aov(df[[var]] ~ df$Label))
  data.frame(
    Variable = var,
    F_value = round(aov_res[[1]][["F value"]][1], 2),
    p_value = round(aov_res[[1]][["Pr(>F)"]][1], 4)
  )
})

anova_results_table <- bind_rows(anova_results)
anova_results_table
```

## H1
### Descriptive
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
performance_long <- df_long %>%
  rename(Measure = measure) %>%
  filter(
    Measure == "accuracy",
    Task != "task0"
  )

head(performance_long)
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
performance_long$Label <- as.factor(performance_long$Label)
performance_long$Phase <- as.factor(performance_long$Phase)
performance_long$Task <- as.factor(performance_long$Task)

stage_summary <- performance_long %>%
  group_by(Phase, Label) %>%
  summarise(
    Mean = round(mean(Value, na.rm = TRUE), 2),
    SD = round(sd(Value, na.rm = TRUE), 2),
    N = n()
  )

head(stage_summary)
```

### LMM
#### Without Task
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
follow_up_stage <- c("stage1", "stage2", "stage3", "follow")

performance_long1 <- performance_long %>%
  filter(Phase %in% follow_up_stage)

performance_long1$Phase <- factor(performance_long1$Phase, levels = c("follow", "stage3", "stage2", "stage1"))

model <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = performance_long1
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients
print(model_summary)

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Label)
cat("\n===POST HOC LABEL===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
cat("\n===POST HOC PHASE X LABEL===\n")
print(posthoc_stage_label$contrasts)

posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
cat("\n===POST HOC LABEL X PHASE===\n")
print(posthoc_label_stage$contrasts)
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
# write.xlsx(
#   list(
#     Model_Summary = as.data.frame(model_summary),
#     ANOVA = as.data.frame(anova_results),
#     Eta_Squared = as.data.frame(eta_sq),
#     Posthoc_Stage = as.data.frame(posthoc_stage$contrasts),
#     Posthoc_Label = as.data.frame(posthoc_label$contrasts),
#     Posthoc_Stage_Label = as.data.frame(posthoc_stage_label$contrasts)
#   ),
#   file = "results/Follow-Up Activity/H1_Stage1_Longterm_Accuracy_Comparison_LMM.xlsx",
#   rowNames = TRUE
# )
```

#### With Task
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
follow_up_stage <- c("stage1", "stage2", "stage3", "follow")

performance_long1 <- performance_long %>%
  filter(Phase %in% follow_up_stage)

performance_long1$Phase <- factor(performance_long1$Phase, levels = c("follow", "stage3", "stage2", "stage1"))

model <- lmer(
  Value ~ Phase * Label * Task + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | ID:Task),
  data = performance_long1
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Task)
cat("\n===POST HOC Task===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Task)
cat("\n===POST HOC PHASE X Task===\n")
print(posthoc_stage_label$contrasts)

posthoc_stage_task_label <- emmeans(model, pairwise ~ Phase | Task | Label)
cat("\n===POST HOC PHASE X Task X Label===\n")
print(posthoc_stage_task_label$contrasts)
```

## H2
### Confidence
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
confidence_long <- df_long %>%
  filter(
    measure == "confidence",
    Task != "task0"
  )
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
follow_up_stage <- c("stage1", "stage2", "stage3", "follow")

confidence_long1 <- confidence_long %>%
  filter(Phase %in% follow_up_stage)

confidence_long1$Phase <- factor(confidence_long1$Phase, levels = c("follow", "stage3", "stage2", "stage1"))

model <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = confidence_long1
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Label)
cat("\n===POST HOC LABEL===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
cat("\n===POST HOC PHASE X LABEL===\n")
print(posthoc_stage_label$contrasts)

posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
cat("\n===POST HOC LABEL X STAGE===\n")
print(posthoc_label_stage$contrasts)
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
# write.xlsx(
#   list(
#     Model_Summary = as.data.frame(model_summary),
#     ANOVA = as.data.frame(anova_results),
#     Eta_Squared = as.data.frame(eta_sq),
#     Posthoc_Stage = as.data.frame(posthoc_stage$contrasts),
#     Posthoc_Label = as.data.frame(posthoc_label$contrasts),
#     Posthoc_Stage_Label = as.data.frame(posthoc_stage_label$contrasts)
#   ),
#   file = "results/Follow-Up Activity/H2_Longterm_Confidence_Change.xlsx"
# )
```

### Willingness
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
willingness_long <- df_long %>%
  filter(
    measure == "willing",
    Task != "task0"
  )
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
follow_up_stage <- c("stage2", "stage3")

willingness_long1 <- willingness_long %>%
  filter(Phase %in% follow_up_stage)

willingness_long1$Phase <- factor(willingness_long1$Phase, levels = c("stage3", "stage2"))

model <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = willingness_long1
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Label)
cat("\n===POST HOC LABEL===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
cat("\n===POST HOC PHASE X LABEL===\n")
print(posthoc_stage_label$contrasts)

posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
cat("\n===POST HOC LABEL X STAGE===\n")
print(posthoc_label_stage$contrasts)
```

### Usefulness
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
usefulness_long <- df_long %>%
  filter(
    measure == "useful",
    Task != "task0"
  )
```

``` {r, message=FALSE, warning=FALSE, echo=TRUE}
follow_up_stage <- c("stage2", "stage3")

usefulness_long1 <- usefulness_long %>%
  filter(Phase %in% follow_up_stage)

usefulness_long1$Phase <- factor(usefulness_long1$Phase, levels = c("stage3", "stage2"))

model <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = usefulness_long1
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Label)
cat("\n===POST HOC LABEL===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
cat("\n===POST HOC PHASE X LABEL===\n")
print(posthoc_stage_label$contrasts)

posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
cat("\n===POST HOC LABEL X STAGE===\n")
print(posthoc_label_stage$contrasts)
```

### Attitude Change Over Time
#### Pre, Followup
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
measures <- c("GLAT_Objective_AI_Literacy", "AILS_CCS_Subjective_AI_Literacy", "AI_Self_Efficacy")

change_stats <- list()
anova_results <- list()
eta_squared_results <- list()
posthoc_results_stage <- list()
posthoc_results_PL <- list()
posthoc_results_LP <- list()

for (msr in measures) {
  d_sub <- df_long %>%
    filter(measure == msr, Phase %in% c("Pre", "follow")) %>%
    dplyr::select(-Task)

  d_wide <- d_sub %>%
    dplyr::select(ID, Label, Phase, Value) %>%
    pivot_wider(names_from = Phase, values_from = Value) %>%
    mutate(change = follow - Pre)

  stat_tab <- d_wide %>%
    group_by(Label) %>%
    summarise(
      MeanChange = round(mean(change, na.rm = TRUE), 2),
      SD = round(sd(change, na.rm = TRUE), 2),
      N = n()
    ) %>%
    mutate(Measure = msr, .before = 1)

  change_stats[[msr]] <- stat_tab

  d_mod <- d_sub %>%
    filter(!is.na(Value))

  if (nrow(d_mod) > 0) {
    d_mod$Phase <- factor(d_mod$Phase, levels = c("follow", "Pre"))
    d_mod$Phase <- relevel(as.factor(d_mod$Phase), ref = "follow")

    model <- lmer(
      Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours + (1 | ID),
      data = d_mod
    )

    print(msr)

    aov_tab <- anova(model)
    cat("\n===ANOVA===\n")
    print(aov_tab)

    eta <- effectsize::eta_squared(model, partial = TRUE)
    cat("\n===Eta Squared===\n")
    print(eta)

    posthoc_stage <- emmeans(model, pairwise ~ Phase)
    cat("\n===Post-Hoc Phase===\n")
    print(posthoc_stage)

    posthoc_label <- emmeans(model, pairwise ~ Label)
    cat("\n===Post-Hoc Label===\n")
    print(posthoc_label)

    posthoc_PL <- emmeans(model, pairwise ~ Phase | Label)
    posthoc_LP <- emmeans(model, pairwise ~ Label | Phase)

    anova_results[[msr]] <- as.data.frame(aov_tab) %>%
      tibble::rownames_to_column("Effect") %>%
      mutate(Measure = msr, .before = 1)

    eta_squared_results[[msr]] <- as.data.frame(eta) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_stage[[msr]] <- as.data.frame(posthoc_stage$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_PL[[msr]] <- as.data.frame(posthoc_PL$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_LP[[msr]] <- as.data.frame(posthoc_LP$contrasts) %>%
      mutate(Measure = msr, .before = 1)
  }
}

# final_output_list <- list(
#   ChangeScore_Summary = bind_rows(change_stats),
#   ANOVA_Results = bind_rows(anova_results),
#   Eta_Squared_Results = bind_rows(eta_squared_results),
#   Posthoc_Stage_Results = bind_rows(posthoc_results_stage),
#   Posthoc_PL_Results = bind_rows(posthoc_results_PL),
#   Posthoc_LP_Results = bind_rows(posthoc_results_LP)
# )
#
# write.xlsx(
#   final_output_list,
#   file = "results/Follow-Up Activity/H2_Attitude_Change_Longterm_PF.xlsx",
#   overwrite = TRUE
# )
```

#### Pre, Post, Followup
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
measures <- c("AI_Trust", "AI_Usefulness", "AI_Affect", "Behavioral_Intention")

change_stats <- list()
anova_results <- list()
eta_squared_results <- list()
posthoc_results_stage <- list()
posthoc_results_PL <- list()
posthoc_results_LP <- list()

for (msr in measures) {
  d_sub <- df_long %>%
    filter(measure == msr, Phase %in% c("Pre", "Post", "follow")) %>%
    dplyr::select(-Task)

  d_wide <- d_sub %>%
    dplyr::select(ID, Label, Phase, Value) %>%
    pivot_wider(names_from = Phase, values_from = Value) %>%
    mutate(change = follow - Pre)

  stat_tab <- d_wide %>%
    group_by(Label) %>%
    summarise(
      MeanChange = round(mean(change, na.rm = TRUE), 2),
      SD = round(sd(change, na.rm = TRUE), 2),
      N = n()
    ) %>%
    mutate(Measure = msr, .before = 1)

  change_stats[[msr]] <- stat_tab

  d_mod <- d_sub %>%
    filter(!is.na(Value))

  if (nrow(d_mod) > 0) {
    d_mod$Phase <- factor(d_mod$Phase, levels = c("follow", "Post", "Pre"))
    d_mod$Phase <- relevel(as.factor(d_mod$Phase), ref = "follow")

    model <- lmer(
      Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours + (1 | ID),
      data = d_mod
    )

    cat("\n")
    print(msr)

    aov_tab <- anova(model)
    cat("\n===ANOVA===\n")
    print(aov_tab)

    eta <- effectsize::eta_squared(model, partial = TRUE)
    cat("\n===Eta Squared===\n")
    print(eta)

    posthoc_stage <- emmeans(model, pairwise ~ Phase)
    cat("\n===Post Hoc Phase===\n")
    print(posthoc_stage)

    posthoc_PL <- emmeans(model, pairwise ~ Phase | Label)
    posthoc_LP <- emmeans(model, pairwise ~ Label | Phase)

    anova_results[[msr]] <- as.data.frame(aov_tab) %>%
      tibble::rownames_to_column("Effect") %>%
      mutate(Measure = msr, .before = 1)

    eta_squared_results[[msr]] <- as.data.frame(eta) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_stage[[msr]] <- as.data.frame(posthoc_stage$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_PL[[msr]] <- as.data.frame(posthoc_PL$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_LP[[msr]] <- as.data.frame(posthoc_LP$contrasts) %>%
      mutate(Measure = msr, .before = 1)
  }
}

# final_output_list <- list(
#   ChangeScore_Summary = bind_rows(change_stats),
#   ANOVA_Results = bind_rows(anova_results),
#   Eta_Squared_Results = bind_rows(eta_squared_results),
#   Posthoc_Stage_Results = bind_rows(posthoc_results_stage),
#   Posthoc_PL_Results = bind_rows(posthoc_results_PL),
#   Posthoc_LP_Results = bind_rows(posthoc_results_LP)
# )
#
# write.xlsx(
#   final_output_list,
#   file = "results/Follow-Up Activity/H2_Attitude_Change_Longterm_PPF.xlsx",
#   overwrite = TRUE
# )
```

## H3
### Attitude Change Longterm Moderation
#### Pre, Followup
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
outcomes <- c(
  "GLAT_Objective_AI_Literacy",
  "AILS_CCS_Subjective_AI_Literacy",
  "AI_Self_Efficacy"
)

moderators <- c(
  "GLAT_Objective_AI_Literacy",
  "AILS_CCS_Subjective_AI_Literacy",
  "AI_Trust",
  "AI_Usefulness",
  "AI_Affect",
  "AI_Self_Efficacy",
  "Behavioral_Intention",
  "Stats_Background",
  "Used_LLM_Frequency",
  "Used_LLM_Hours"
)

categorical_mods <- c("Stats_Background", "Used_LLM_Frequency", "Used_LLM_Hours")

outcome_abbr <- c(
  "GLAT_Objective_AI_Literacy" = "ObjLit",
  "AILS_CCS_Subjective_AI_Literacy" = "CCSLit",
  "AI_Trust" = "Trust",
  "AI_Usefulness" = "Useful",
  "AI_Affect" = "Affect",
  "AI_Self_Efficacy" = "SelfEff",
  "Behavioral_Intention" = "BehInt"
)

moderator_abbr <- c(
  "GLAT_Objective_AI_Literacy" = "ObjLit",
  "AILS_CCS_Subjective_AI_Literacy" = "CCSLit",
  "AI_Trust" = "Trust",
  "AI_Usefulness" = "Useful",
  "AI_Affect" = "Affect",
  "AI_Self_Efficacy" = "SelfEff",
  "Behavioral_Intention" = "BehInt",
  "Stats_Background" = "StatsBG",
  "Used_LLM_Frequency" = "LLMFreq",
  "Used_LLM_Hours" = "LLMHr"
)

make_excel_sheetname <- function(x) {
  x <- gsub("[:/\\?\\*\\[\\] ]", "_", x)
  x <- substr(x, 1, 31)
  return(x)
}

result_list <- list()

for (outcome in outcomes) {
  for (mod in moderators) {
    df_sub <- df_long %>%
      filter(measure == outcome, Phase %in% c("Pre", "follow"))

    if (nrow(df_sub) > 0) {
      df_sub$Phase <- factor(df_sub$Phase, levels = c("Pre", "follow"))
      df_sub$Label <- as.factor(df_sub$Label)
      df_sub$ID <- as.factor(df_sub$ID)

      posthoc_list <- list()
      formula_str <- NA_character_

      if (mod == outcome) {
        baseline_df <- df_sub %>%
          filter(Phase == "Pre") %>%
          dplyr::select(ID, BaselineScore = Value)

        df_sub <- df_sub %>%
          left_join(baseline_df, by = "ID")

        df_sub$BaselineScore <- scale(df_sub$BaselineScore, scale = FALSE)

        formula_str <- "Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours + BaselineScore + (1|ID)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      } else if (mod %in% df_long$measure) {
        mod_df <- df_long %>%
          filter(Phase == "Pre", measure == mod) %>%
          dplyr::select(ID, ModeratorScore = Value)

        df_sub <- df_sub %>%
          left_join(mod_df, by = "ID")

        df_sub$ModeratorScore <- scale(df_sub$ModeratorScore, scale = FALSE)

        formula_str <- "Value ~ Phase * Label * ModeratorScore + Age + Gender + Field + Used_LLM_Hours + (1|ID)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      } else {
        df_sub$ModeratorScore <- df_sub[[mod]]

        formula_str <- "Value ~ Phase * Label * ModeratorScore + Age + Gender + Field + Used_LLM_Hours + (1|ID)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      }

      anova_res <- anova(model)

      ANOVA <- as.data.frame(anova_res)
      ANOVA$Variable <- rownames(ANOVA)
      ANOVA <- ANOVA[, c("Variable", setdiff(names(ANOVA), "Variable"))]

      eta_sq <- eta_squared(model, partial = TRUE)

      coef_tbl <- as.data.frame(summary(model)$coefficients)
      coef_tbl$Variable <- rownames(coef_tbl)
      coef_tbl <- coef_tbl[, c("Variable", setdiff(names(coef_tbl), "Variable"))]

      if ("Pr(>F)" %in% names(ANOVA)) {
        sig_terms <- rownames(ANOVA)[which(ANOVA$`Pr(>F)` < 0.05)]
      } else {
        sig_terms <- character(0)
      }

      for (term in sig_terms) {
        clean_term <- gsub("[:/\\\\?\\*\\[\\]]", "_", term)

        term_vars <- unlist(strsplit(term, ":"))
        left_facs <- setdiff(term_vars, c(mod, "ModeratorScore"))

        if (mod %in% categorical_mods && any(term_vars %in% c(mod, "ModeratorScore"))) {
          ph_em <- tryCatch(
            emmeans(model, pairwise ~ Label | ModeratorScore),
            error = function(e) NULL
          )

          if (!is.null(ph_em)) {
            posthoc_list[[clean_term]] <- as.data.frame(ph_em$contrasts)
          }
        } else if (!(mod %in% categorical_mods) && any(term_vars %in% c(mod, "ModeratorScore"))) {
          if (length(left_facs) == 0) {
            specs <- ~1
          } else {
            specs <- as.formula(paste0("~", paste(left_facs, collapse = "*")))
          }

          et <- tryCatch(
            emtrends(
              model,
              specs = specs,
              var = ifelse("ModeratorScore" %in% term_vars, "ModeratorScore", mod),
              infer = c(TRUE, TRUE)
            ),
            error = function(e) NULL
          )

          cat("\n")
          print(outcome)
          print(mod)
          print(et)

          if (!is.null(et)) {
            posthoc_list[[paste0(clean_term, "_trends")]] <- as.data.frame(summary(et, infer = c(TRUE, TRUE)))

            if (length(left_facs) > 0) {
              ph_pair <- tryCatch(as.data.frame(pairs(et)), error = function(e) NULL)
              if (!is.null(ph_pair)) {
                posthoc_list[[paste0(clean_term, "_trends_pairs")]] <- ph_pair
              }
            }
          }
        } else if (length(term_vars) > 0) {
          em_out <- tryCatch(emmeans(model, specs = term_vars), error = function(e) NULL)
          if (!is.null(em_out)) {
            posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
          }
        }
      }

      result_list[[paste0(outcome, "_by_", mod)]] <- list(
        Formula = formula_str,
        ANOVA = ANOVA,
        Eta_Squared = as.data.frame(eta_sq),
        Coef_Summary = coef_tbl,
        Posthoc = posthoc_list
      )
    }
  }
}

# flat_result_list <- list()
#
# for (name in names(result_list)) {
#   name_parts <- unlist(strsplit(name, "*by*"))
#   outcome <- ifelse(length(name_parts) >= 1, name_parts[1], name)
#   moderator <- ifelse(length(name_parts) >= 2, name_parts[2], "")
#
#   out_abbr <- ifelse(outcome %in% names(outcome_abbr), outcome_abbr[[outcome]], substr(outcome, 1, 8))
#   mod_abbr <- ifelse(moderator %in% names(moderator_abbr), moderator_abbr[[moderator]], substr(moderator, 1, 8))
#
#   prefix <- if (mod_abbr != "") paste(out_abbr, mod_abbr, sep = "_") else out_abbr
#
#   if (!is.null(result_list[[name]]$ANOVA)) {
#     flat_result_list[[make_excel_sheetname(paste0(prefix, "_ANOVA"))]] <- result_list[[name]]$ANOVA
#   }
#
#   if (!is.null(result_list[[name]]$Eta_Squared)) {
#     flat_result_list[[make_excel_sheetname(paste0(prefix, "_EtaSq"))]] <- result_list[[name]]$Eta_Squared
#   }
#
#   if (!is.null(result_list[[name]]$Coef_Summary)) {
#     flat_result_list[[make_excel_sheetname(paste0(prefix, "_Coef"))]] <- result_list[[name]]$Coef_Summary
#   }
#
#   if (!is.null(result_list[[name]]$Posthoc)) {
#     for (int_type in names(result_list[[name]]$Posthoc)) {
#       ph <- result_list[[name]]$Posthoc[[int_type]]
#       if (!is.null(ph) && is.data.frame(ph) && !is.na(nrow(ph)) && nrow(ph) > 0) {
#         flat_result_list[[make_excel_sheetname(
#           paste0(prefix, "*Posthoc*", substr(int_type, 1, 10))
#         )]] <- ph
#       }
#     }
#   }
# }
#
# names(flat_result_list) <- gsub(":", "_", names(flat_result_list))
#
# write.xlsx(
#   flat_result_list,
#   file = "results/Follow-Up Activity/H3_Attitude_Change_Longterm_Moderation_PF.xlsx"
# )
```

##### Export Results Summary
``` {r}
# export_sig_effects <- function(result_list, out_excel_path) {
#   if (!dir.exists(dirname(out_excel_path))) {
#     dir.create(dirname(out_excel_path), recursive = TRUE)
#   }
#
#   summary_sig_effects <- data.frame(
#     DV = character(),
#     Moderator = character(),
#     Term = character(),
#     NumDF = numeric(),
#     DenDF = numeric(),
#     F_value = numeric(),
#     p_value = numeric(),
#     eta_p = numeric(),
#     stringsAsFactors = FALSE
#   )
#
#   for (res_name in names(result_list)) {
#     split_name <- unlist(strsplit(res_name, "*by*"))
#     DV <- split_name[1]
#     Moderator <- split_name[2]
#
#
#     ANOVA <- result_list[[res_name]]$ANOVA
#     Eta <- result_list[[res_name]]$Eta_Squared
#
#     if (!is.null(ANOVA) && "Pr(>F)" %in% names(ANOVA) && "F value" %in% names(ANOVA)) {
#       sig_rows <- which(ANOVA$`Pr(>F)` <= 1)
#
#       if (length(sig_rows) > 0) {
#         for (i in sig_rows) {
#           this_term <- ANOVA$Variable[i]
#           Ndf <- ANOVA$NumDF[i]
#           Ddf <- ANOVA$DenDF[i]
#           Fval <- ANOVA$`F value`[i]
#           pval <- ANOVA$`Pr(>F)`[i]
#
#           eta_row <- NULL
#           if (!is.null(Eta) && "Parameter" %in% names(Eta)) {
#             eta_row <- Eta[Eta$Parameter == this_term, ]
#           }
#
#           eta_val <- NA
#           if (!is.null(eta_row) && nrow(eta_row) == 1) {
#             if ("Eta2_partial" %in% names(eta_row)) eta_val <- eta_row$Eta2_partial
#             if ("Eta2" %in% names(eta_row) && is.na(eta_val)) eta_val <- eta_row$Eta2
#           }
#
#           summary_sig_effects <- rbind(
#             summary_sig_effects,
#             data.frame(
#               DV = DV,
#               Moderator = Moderator,
#               Term = this_term,
#               NumDF = Ndf,
#               DenDF = Ddf,
#               F_value = Fval,
#               p_value = pval,
#               eta_p = eta_val
#             )
#           )
#         }
#       }
#     }
#   }
#
#   summary_sig_effects <- summary_sig_effects[
#     order(summary_sig_effects$DV, summary_sig_effects$Moderator, summary_sig_effects$p_value),
#   ]
#
#   write.xlsx(summary_sig_effects, file = out_excel_path, rowNames = FALSE)
#   cat(sprintf("Significant terms summary saved to %s\n", out_excel_path))
#   invisible(summary_sig_effects)
# }
#
# export_sig_effects(
#   result_list,
#   out_excel_path = "results/Follow-Up Activity/H3_Attitude_Longterm_Moderation_Summary_PF.xlsx"
# )
```

#### Pre, Post, Followup
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
outcomes <- c(
  "AI_Trust",
  "AI_Usefulness",
  "AI_Affect",
  "Behavioral_Intention"
)

moderators <- c(
  "GLAT_Objective_AI_Literacy",
  "AILS_CCS_Subjective_AI_Literacy",
  "AI_Trust",
  "AI_Usefulness",
  "AI_Affect",
  "AI_Self_Efficacy",
  "Behavioral_Intention",
  "Stats_Background",
  "Used_LLM_Frequency",
  "Used_LLM_Hours"
)

categorical_mods <- c("Stats_Background", "Used_LLM_Frequency", "Used_LLM_Hours")

outcome_abbr <- c(
  "GLAT_Objective_AI_Literacy" = "ObjLit",
  "AILS_CCS_Subjective_AI_Literacy" = "CCSLit",
  "AI_Trust" = "Trust",
  "AI_Usefulness" = "Useful",
  "AI_Affect" = "Affect",
  "AI_Self_Efficacy" = "SelfEff",
  "Behavioral_Intention" = "BehInt"
)

moderator_abbr <- c(
  "GLAT_Objective_AI_Literacy" = "ObjLit",
  "AILS_CCS_Subjective_AI_Literacy" = "CCSLit",
  "AI_Trust" = "Trust",
  "AI_Usefulness" = "Useful",
  "AI_Affect" = "Affect",
  "AI_Self_Efficacy" = "SelfEff",
  "Behavioral_Intention" = "BehInt",
  "Stats_Background" = "StatsBG",
  "Used_LLM_Frequency" = "LLMFreq",
  "Used_LLM_Hours" = "LLMHr"
)

make_excel_sheetname <- function(x) {
  x <- gsub("[:/\\?\\*\\[\\] ]", "_", x)
  x <- substr(x, 1, 31)
  return(x)
}

result_list <- list()

for (outcome in outcomes) {
  for (mod in moderators) {
    df_sub <- df_long %>%
      filter(measure == outcome, Phase %in% c("Pre", "Post", "follow"))

    if (nrow(df_sub) > 0) {
      df_sub$Phase <- factor(df_sub$Phase, levels = c("Pre", "Post", "follow"))
      df_sub$Label <- as.factor(df_sub$Label)
      df_sub$ID <- as.factor(df_sub$ID)

      posthoc_list <- list()
      formula_str <- NA_character_

      if (mod == outcome) {
        baseline_df <- df_sub %>%
          filter(Phase == "Pre") %>%
          dplyr::select(ID, BaselineScore = Value)

        df_sub <- df_sub %>%
          left_join(baseline_df, by = "ID")

        df_sub$BaselineScore <- scale(df_sub$BaselineScore, scale = FALSE)

        formula_str <- "Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours + BaselineScore + (1|ID)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      } else if (mod %in% df_long$measure) {
        mod_df <- df_long %>%
          filter(Phase == "Pre", measure == mod) %>%
          dplyr::select(ID, ModeratorScore = Value)

        df_sub <- df_sub %>%
          left_join(mod_df, by = "ID")

        df_sub$ModeratorScore <- scale(df_sub$ModeratorScore, scale = FALSE)

        formula_str <- "Value ~ Phase * Label * ModeratorScore + Age + Gender + Field + Used_LLM_Hours + (1|ID)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      } else {
        df_sub$ModeratorScore <- df_sub[[mod]]

        formula_str <- "Value ~ Phase * Label * ModeratorScore + Age + Gender + Field + Used_LLM_Hours + (1|ID)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      }

      anova_res <- anova(model)

      ANOVA <- as.data.frame(anova_res)
      ANOVA$Variable <- rownames(ANOVA)
      ANOVA <- ANOVA[, c("Variable", setdiff(names(ANOVA), "Variable"))]

      eta_sq <- effectsize::eta_squared(model, partial = TRUE)

      coef_tbl <- as.data.frame(summary(model)$coefficients)
      coef_tbl$Variable <- rownames(coef_tbl)
      coef_tbl <- coef_tbl[, c("Variable", setdiff(names(coef_tbl), "Variable"))]

      if ("Pr(>F)" %in% names(ANOVA)) {
        sig_terms <- rownames(ANOVA)[which(ANOVA$`Pr(>F)` < 0.05)]
      } else {
        sig_terms <- character(0)
      }

      for (term in sig_terms) {
        clean_term <- gsub("[:/\\\\?\\*\\[\\]]", "_", term)

        term_vars <- unlist(strsplit(term, ":"))
        left_facs <- setdiff(term_vars, c(mod, "ModeratorScore"))

        if (mod %in% categorical_mods && any(term_vars %in% c(mod, "ModeratorScore"))) {
          ph_em <- tryCatch(
            emmeans(model, pairwise ~ Label | ModeratorScore),
            error = function(e) NULL
          )

          if (!is.null(ph_em)) {
            posthoc_list[[clean_term]] <- as.data.frame(ph_em$contrasts)
          }
        } else if (!(mod %in% categorical_mods) && any(term_vars %in% c(mod, "ModeratorScore"))) {
          if (length(left_facs) == 0) {
            specs <- ~1
          } else {
            specs <- as.formula(paste0("~", paste(left_facs, collapse = "*")))
          }

          et <- tryCatch(
            emtrends(
              model,
              specs = specs,
              var = ifelse("ModeratorScore" %in% term_vars, "ModeratorScore", mod),
              infer = c(TRUE, TRUE)
            ),
            error = function(e) NULL
          )

          cat("\n===", outcome, "+", mod, "===\n")
          print(et)

          if (!is.null(et)) {
            posthoc_list[[paste0(clean_term, "_trends")]] <- as.data.frame(summary(et, infer = c(TRUE, TRUE)))

            if (length(left_facs) > 0) {
              ph_pair <- tryCatch(as.data.frame(pairs(et)), error = function(e) NULL)
              if (!is.null(ph_pair)) {
                posthoc_list[[paste0(clean_term, "_trends_pairs")]] <- ph_pair
              }
            }
          }
        } else if (length(term_vars) > 0) {
          em_out <- tryCatch(emmeans(model, specs = term_vars), error = function(e) NULL)
          if (!is.null(em_out)) {
            posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
          }
        }
      }

      result_list[[paste0(outcome, "_by_", mod)]] <- list(
        Formula = formula_str,
        ANOVA = ANOVA,
        Eta_Squared = as.data.frame(eta_sq),
        Coef_Summary = coef_tbl,
        Posthoc = posthoc_list
      )
    }
  }
}

# flat_result_list <- list()
#
# for (name in names(result_list)) {
#   name_parts <- unlist(strsplit(name, "*by*"))
#   outcome <- ifelse(length(name_parts) >= 1, name_parts[1], name)
#   moderator <- ifelse(length(name_parts) >= 2, name_parts[2], "")
#
#   out_abbr <- ifelse(outcome %in% names(outcome_abbr), outcome_abbr[[outcome]], substr(outcome, 1, 8))
#   mod_abbr <- ifelse(moderator %in% names(moderator_abbr), moderator_abbr[[moderator]], substr(moderator, 1, 8))
#
#   prefix <- if (mod_abbr != "") paste(out_abbr, mod_abbr, sep = "_") else out_abbr
#
#   if (!is.null(result_list[[name]]$ANOVA)) {
#     flat_result_list[[make_excel_sheetname(paste0(prefix, "_ANOVA"))]] <- result_list[[name]]$ANOVA
#   }
#
#   if (!is.null(result_list[[name]]$Eta_Squared)) {
#     flat_result_list[[make_excel_sheetname(paste0(prefix, "_EtaSq"))]] <- result_list[[name]]$Eta_Squared
#   }
#
#   if (!is.null(result_list[[name]]$Coef_Summary)) {
#     flat_result_list[[make_excel_sheetname(paste0(prefix, "_Coef"))]] <- result_list[[name]]$Coef_Summary
#   }
#
#   if (!is.null(result_list[[name]]$Posthoc)) {
#     for (int_type in names(result_list[[name]]$Posthoc)) {
#       ph <- result_list[[name]]$Posthoc[[int_type]]
#       if (!is.null(ph) && is.data.frame(ph) && !is.na(nrow(ph)) && nrow(ph) > 0) {
#         flat_result_list[[make_excel_sheetname(
#           paste0(prefix, "*Posthoc*", substr(int_type, 1, 10))
#         )]] <- ph
#       }
#     }
#   }
# }
#
# names(flat_result_list) <- gsub(":", "_", names(flat_result_list))
#
# write.xlsx(
#   flat_result_list,
#   file = "results/Follow-Up Activity/H3_Attitude_Change_Longterm_Moderation_PPF.xlsx"
# )
```

##### Export Restuls Summary
``` {r}
# export_sig_effects <- function(result_list, out_excel_path) {
#   if (!dir.exists(dirname(out_excel_path))) {
#     dir.create(dirname(out_excel_path), recursive = TRUE)
#   }
#
#   summary_sig_effects <- data.frame(
#     DV = character(),
#     Moderator = character(),
#     Term = character(),
#     NumDF = numeric(),
#     DenDF = numeric(),
#     F_value = numeric(),
#     p_value = numeric(),
#     eta_p = numeric(),
#     stringsAsFactors = FALSE
#   )
#
#   for (res_name in names(result_list)) {
#     split_name <- unlist(strsplit(res_name, "*by*"))
#     DV <- split_name[1]
#     Moderator <- split_name[2]
#
#     ANOVA <- result_list[[res_name]]$ANOVA
#     Eta <- result_list[[res_name]]$Eta_Squared
#
#     if (!is.null(ANOVA) && "Pr(>F)" %in% names(ANOVA) && "F value" %in% names(ANOVA)) {
#       sig_rows <- which(ANOVA$`Pr(>F)` <= 1)
#
#       if (length(sig_rows) > 0) {
#         for (i in sig_rows) {
#           this_term <- ANOVA$Variable[i]
#           Ndf <- ANOVA$NumDF[i]
#           Ddf <- ANOVA$DenDF[i]
#           Fval <- ANOVA$`F value`[i]
#           pval <- ANOVA$`Pr(>F)`[i]
#
#           eta_row <- NULL
#           if (!is.null(Eta) && "Parameter" %in% names(Eta)) {
#             eta_row <- Eta[Eta$Parameter == this_term, ]
#           }
#
#           eta_val <- NA
#           if (!is.null(eta_row) && nrow(eta_row) == 1) {
#             if ("Eta2_partial" %in% names(eta_row)) eta_val <- eta_row$Eta2_partial
#             if ("Eta2" %in% names(eta_row) && is.na(eta_val)) eta_val <- eta_row$Eta2
#           }
#
#           summary_sig_effects <- rbind(
#             summary_sig_effects,
#             data.frame(
#               DV = DV,
#               Moderator = Moderator,
#               Term = this_term,
#               NumDF = Ndf,
#               DenDF = Ddf,
#               F_value = Fval,
#               p_value = pval,
#               eta_p = eta_val
#             )
#           )
#         }
#       }
#     }
#   }
#
#   summary_sig_effects <- summary_sig_effects[
#     order(summary_sig_effects$DV, summary_sig_effects$Moderator, summary_sig_effects$p_value),
#   ]
#
#   write.xlsx(summary_sig_effects, file = out_excel_path, rowNames = FALSE)
#   cat(sprintf("Significant terms summary saved to %s\n", out_excel_path))
#   invisible(summary_sig_effects)
# }
#
# export_sig_effects(
#   result_list,
#   out_excel_path = "results/Follow-Up Activity/H3_Attitude_Longterm_Moderation_Summary_PPF.xlsx"
# )
```

### Continued Use Application
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
behavior_map <- c(
  follow_activity_1 = "applied_stat_concepts",
  follow_activity_2 = "used_llms_stat",
  follow_activity_3 = "used_llms_general",
  follow_activity_4 = "stayed_updated_ai"
)

result_list <- list()

for (v in names(behavior_map)) {
  df_bhv <- df %>%
    dplyr::select(ID, Label, !!rlang::sym(v)) %>%
    dplyr::rename(Value = !!rlang::sym(v)) %>%
    dplyr::filter(!is.na(Value))

  means <- df_bhv %>%
    group_by(Label) %>%
    summarise(
      Mean = round(mean(as.numeric(Value), na.rm = TRUE), 2),
      SD = round(sd(as.numeric(Value), na.rm = TRUE), 2),
      N = n()
    )

  aov_mod <- aov(Value ~ Label, data = df_bhv)
  anova_tab <- as.data.frame(summary(aov_mod)[[1]])
  posthoc_aov <- as.data.frame(emmeans(aov_mod, pairwise ~ Label)$contrasts)

  kw_mod <- rstatix::kruskal_test(Value ~ Label, data = df_bhv)
  dunn_mod <- rstatix::dunn_test(Value ~ Label, data = df_bhv, p.adjust.method = "bonferroni")

  df_bhv$Value_ord <- as.ordered(df_bhv$Value)
  ord_mod <- MASS::polr(Value_ord ~ Label, data = df_bhv, Hess = TRUE)
  ord_aov <- car::Anova(ord_mod)

  cat("\n===", v, "===\n")
  print(ord_aov)
  cat("\n")

  posthoc_ord <- as.data.frame(emmeans(ord_mod, pairwise ~ Label)$contrasts)

  nm <- behavior_map[[v]]

  result_list[[paste0(nm, "_summary")]] <- means
  result_list[[paste0(nm, "_anova")]] <- anova_tab
  result_list[[paste0(nm, "_ph_aov")]] <- posthoc_aov
  result_list[[paste0(nm, "_kruskal")]] <- as.data.frame(kw_mod)
  result_list[[paste0(nm, "_dunn")]] <- as.data.frame(dunn_mod)
  result_list[[paste0(nm, "_ordinal")]] <- as.data.frame(summary(ord_mod)$coefficients)
  result_list[[paste0(nm, "_ph_ord")]] <- posthoc_ord
}

# write.xlsx(
#   result_list,
#   file = "results/Follow-Up Activity/Continued_Use_Application.xlsx",
#   row.names = TRUE
# )
```
