---
title: "Study 2 Demographic Results (Follow-Up)"
author: "Spike"
date: "2025-07-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages
```{r, message=FALSE, warning=FALSE}
library(readxl)
library(janitor)
library(dplyr)
library(tidyr)
library(openxlsx)
```

## Load Data
```{r, message=FALSE, warning=FALSE}
df <- read_excel("data/Study_2_Followup_Data.xlsx")

df <- df %>%
  filter(stage1_task0_accuracy < 0.9) %>%
  mutate(Label = factor(Label, levels = c("AI", "AI Human", "Human")))
```

## Descriptives
### Label Distribution
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
label_table <- df %>%
  group_by(Label) %>%
  summarise(
    n = n(),
    .groups = "drop"
  ) %>%
  mutate(percent = round(100 * n / sum(n), 1))

label_table
```

### Gender Distribution
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
gender_table <- df %>%
  group_by(Label, Gender) %>%
  summarise(
    n = n(),
    .groups = "drop"
  ) %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

gender_table
```

### Age Distribution
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
age_table <- df %>%
  group_by(Label, Age) %>%
  summarise(
    n = n(),
    .groups = "drop"
  ) %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

age_table
```

### Identity Distribution
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
identity_table <- df %>%
  group_by(Label, Identity) %>%
  summarise(
    n = n(),
    .groups = "drop"
  ) %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

identity_table
```

### Field Distribution
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
field_table <- df %>%
  group_by(Label, Field) %>%
  summarise(
    n = n(),
    .groups = "drop"
  ) %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

field_table
```

### Stats Background Distribution
``` {r}
statsbackground_table <- df %>%
  group_by(Label, Stats_Background) %>%
  summarise(
    n = n(),
    .groups = "drop"
  ) %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

statsbackground_table
```

### LLM Use Frequency Distribution
``` {r}
llm_freq_table <- df %>%
  group_by(Label, Used_LLM_Frequency) %>%
  summarise(
    n = n(),
    .groups = "drop"
  ) %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

llm_freq_table
```

### LLM Use Hours Distribution
``` {r}
llm_hours_table <- df %>%
  group_by(Label, Used_LLM_Hours) %>%
  summarise(
    n = n(),
    .groups = "drop"
  ) %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

llm_hours_table
```te(percent = round(100 * n / sum(n), 1))
```

## Chi-square Tests
``` {r, message=FALSE, warning=FALSE, echo=TRUE}
label_chi <- chisq.test(table(df$Label))
gender_chi <- chisq.test(table(df$Label, df$Gender))
age_chi <- chisq.test(table(df$Label, df$Age))
identity_chi <- chisq.test(table(df$Label, df$Identity))
field_chi <- chisq.test(table(df$Label, df$Field))
background_chi <- chisq.test(table(df$Label, df$Stats_Background))
frequency_chi <- chisq.test(table(df$Label, df$Used_LLM_Frequency))
hours_chi <- chisq.test(table(df$Label, df$Used_LLM_Hours))

label_chi
gender_chi
age_chi
identity_chi
field_chi
background_chi
frequency_chi
hours_chi
```

## Export Results
``` {r}
# test_results <- data.frame(
#   Variable = c(
#     "Label", "Gender", "Age", "Identity", "Field",
#     "Stats_Background", "Used_Frequency", "Used_Hours"
#   ),
#   Test = rep("Chi-square", 8),
#   Statistic = c(
#     as.numeric(label_chi$statistic),
#     as.numeric(gender_chi$statistic),
#     as.numeric(age_chi$statistic),
#     as.numeric(identity_chi$statistic),
#     as.numeric(field_chi$statistic),
#     as.numeric(background_chi$statistic),
#     as.numeric(frequency_chi$statistic),
#     as.numeric(hours_chi$statistic)
#   ),
#   p_value = c(
#     label_chi$p.value,
#     gender_chi$p.value,
#     age_chi$p.value,
#     identity_chi$p.value,
#     field_chi$p.value,
#     background_chi$p.value,
#     frequency_chi$p.value,
#     hours_chi$p.value
#   )
# )
#
# all_tables <- list(
#   Label_Distribution    = label_table,
#   Gender_Distribution   = gender_table,
#   Age_Distribution      = age_table,
#   Identity_Distribution = identity_table,
#   Field_Distribution    = field_table,
#   Stats_Background      = statsbackground_table,
#   LLM_Use_Frequency     = llm_freq_table,
#   LLM_Use_Hours         = llm_hours_table,
#   Statistical_Tests     = test_results
# )
#
# write.xlsx(
#   all_tables,
#   file = "results/Baseline demographic_results/Demographic_Analysis_Results_Followup.xlsx"
# )
```