---
title: "Adjust P (Main) — Moderation Multiple-Comparison Correction"
author: "Siyuan Huang"
date: "2026-06-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here("Study_2_Main_Results"))

set.seed(42)
```

## Multiple-comparison correction for H3 moderation effects (Main initial-session sample)

This corrects p-values for the Study 2 **main (initial-session)** H3
**moderation** analyses — attitude-change moderation (Pre → Post) and within-task
performance / confidence / willingness / usefulness moderation (Stage 1–3) — under
one scheme so the two are comparable. Two points define the correction family:

1. **Only the focal moderation terms enter the family.** The hypothesis is
   *whether the moderator alters the change over `Phase`/`Stage` (and its
   dependence on `Label`)* — i.e. the interaction terms involving the moderator.
   Main effects and covariates are not tested and are excluded (including them
   inflated the family and made Holm far too conservative).
2. **`mod == outcome` baseline-adjusted models are dropped** (`BaselineScore`
   models are not moderation tests). For the within-task models this is a no-op
   (accuracy/confidence/willing/useful are never moderators).

A single rule spans both Term conventions — the attitude file's generic
`ModeratorScore` token (e.g. `Phase:ModeratorScore`) and the within-task file's
embedded moderator name with `Stage` (e.g. `Stage:Label:pre_AI_Usefulness`): a
focal term is any interaction (contains `:`) involving the moderator. Family =
focal terms, corrected **within each DV**. Holm (FWER) and BH (FDR) are both
reported; for an exploratory multi-moderator screen **BH/FDR is primary**, Holm a
conservative check.

```{r multiple-comparison-correction-for-h3-moderation-1, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
library(readxl)
library(openxlsx)

# Focal moderation terms = interaction terms involving the moderator. This rule
# handles both Term conventions in the Study 2 main results:
#   * attitude file: moderator appears as the generic token "ModeratorScore"
#   * within-task file: moderator appears as its actual name (row's `Moderator`)
# Main effects (the moderator alone, Phase/Stage, Label) and covariates have no
# ":" or do not involve the moderator, so they are excluded from the family.
adjust_moderation <- function(path_in, path_out, analysis_label) {
  mods <- read_xlsx(path_in)

  mods_focal <- mods %>%
    filter(DV != Moderator) %>%          # drop mod == outcome baseline models
    rowwise() %>%
    filter(
      grepl(":", Term) & (
        grepl("ModeratorScore", Term, fixed = TRUE) |
          grepl(Moderator, Term, fixed = TRUE)
      )
    ) %>%
    ungroup()

  mods_adj <- mods_focal %>%
    group_by(DV) %>%
    mutate(
      n_in_family = n(),
      p_holm = p.adjust(p_value, method = "holm"),
      p_BH   = p.adjust(p_value, method = "BH")
    ) %>%
    ungroup() %>%
    mutate(Analysis = analysis_label, .before = 1) %>%
    arrange(DV, p_value)

  if (!dir.exists(dirname(path_out))) {
    dir.create(dirname(path_out), recursive = TRUE)
  }
  write.xlsx(mods_adj, path_out, overwrite = TRUE)

  cat("\n===", analysis_label, "=== family sizes per DV:\n")
  print(mods_adj %>% distinct(DV, n_in_family))
  cat("\nSurviving BH < .05:\n")
  print(as.data.frame(mods_adj %>% filter(p_BH < 0.05)))
  cat("\nSurviving Holm < .05:\n")
  print(as.data.frame(mods_adj %>% filter(p_holm < 0.05)))

  mods_adj
}

# --- Attitude change moderation (Pre -> Post) -------------------------------
attitude <- adjust_moderation(
  "results/H3/H3_Attitude_Change_Moderation_Summary.xlsx",
  "results/H3/H3_Attitude_Change_Moderation_Padjust.xlsx",
  "Main | Attitude Change (Pre-Post)"
)
```

## Multiple-comparison correction for H3 within-task moderation (accuracy, confidence, willing, useful)

Same scheme for the within-task models (`Stage * Label * Moderator`, Stages
1–3). The focal family is the moderator interactions (`Stage:<mod>`,
`Label:<mod>`, `Stage:Label:<mod>`); the `DV != Moderator` filter is a no-op
and no baseline-adjusted models exist to drop. Family corrected **within each
DV**; Holm and BH reported, BH/FDR primary.

```{r multiple-comparison-correction-for-h3-within-1, message=FALSE, warning=FALSE, echo=TRUE}
within_task <- adjust_moderation(
  "results/H3/H3_Within_Task_Moderation_Summary.xlsx",
  "results/H3/H3_Within_Task_Moderation_Padjust.xlsx",
  "Main | Within-Task Performance, Confidence, Willingness, Usefulness (Stage1-3)"
)
```

## Reproducibility

```{r session-info}
sessionInfo()
```
