---
title: "Study 2 — Follow-Up (Completer-Only) Analyses"
author: "Siyuan Huang"
date: "2025-07-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

set.seed(42)
```

# Study 2 — Follow-Up (Completer-Only) Analyses

This document reports the Study 2 analyses restricted to the **follow-up
completer** sample: participants who completed both the initial and the
follow-up session. As in all Study 2 follow-up analyses, participants with a
Stage-1 baseline (task 0) accuracy of `>= 0.90` are excluded as a
ceiling-effect screen, yielding the analysis sample used throughout
(N = 84; AI / AI + Human / Human conditions).

Unless otherwise noted, all linear mixed models include Age, Gender, Field,
and weekly LLM-usage as covariates, with by-participant (and, for
task-level outcomes, by-task) random effects. The hypotheses are:
**H1** long-term task performance (accuracy), **H2** confidence,
willingness, usefulness, and attitude change over time, and **H3**
moderation of the long-term outcomes by individual-difference measures.

## Packages
```{r packages-1}
library(broom)
library(car)
library(DescTools)
library(dplyr)
library(DT)
library(effectsize)
library(emmeans)
library(ggplot2)
library(janitor)
library(lme4)
library(lmerTest)
library(lsr)
library(MASS)
library(openxlsx)
library(ordinal)
library(performance)
library(readxl)
library(stringr)
library(tidyr)
library(report)
library(interactions)

# Output directories: results are organised into per-hypothesis subfolders.
for (h in c("H1", "H2", "H3")) {
  dir.create(file.path("results/Follow-Up Activity", h), recursive = TRUE, showWarnings = FALSE)
}
```

## Data Preprocessing

The follow-up completer data are loaded, the ceiling-effect screen
(`stage1_task0_accuracy < 0.9`) is applied, background variables are
recoded, and the data are reshaped to long format for the mixed-model
analyses. The factor ordering AI < AI + Human < Human is used throughout.

```{r data-preprocessing-1}
df <- read_xlsx("data/Study_2_Followup_Data.xlsx")
```

```{r data-preprocessing-2}
# Define Variables and Factor Levels
rename_vars <- c(
  "Pre_GLAT_Objective_AI_Literacy",
  "Pre_AILS_CCS_Subjective_AI_Literacy",
  "Pre_AI_Trust",
  "Pre_AI_Usefulness",
  "Pre_AI_Affect",
  "Pre_AI_Self_Efficacy",
  "Pre_Behavioral_Intention",
  "stage1_task0_accuracy",
  "stage1_task1_accuracy",
  "stage1_task2_accuracy",
  "stage1_task3_accuracy",
  "stage2_task0_accuracy",
  "stage2_task1_accuracy",
  "stage2_task2_accuracy",
  "stage2_task3_accuracy",
  "stage3_task0_accuracy",
  "stage3_task1_accuracy",
  "stage3_task2_accuracy",
  "stage3_task3_accuracy",
  "stage1_task0_confidence",
  "stage1_task1_confidence",
  "stage1_task2_confidence",
  "stage1_task3_confidence",
  "stage2_task0_confidence",
  "stage2_task1_confidence",
  "stage2_task2_confidence",
  "stage2_task3_confidence",
  "stage3_task0_confidence",
  "stage3_task1_confidence",
  "stage3_task2_confidence",
  "stage3_task3_confidence",
  "stage2_task0_willing",
  "stage2_task1_willing",
  "stage2_task2_willing",
  "stage2_task3_willing",
  "stage3_task0_willing",
  "stage3_task1_willing",
  "stage3_task2_willing",
  "stage3_task3_willing",
  "stage2_task0_useful",
  "stage2_task1_useful",
  "stage2_task2_useful",
  "stage2_task3_useful",
  "stage3_task0_useful",
  "stage3_task1_useful",
  "stage3_task2_useful",
  "stage3_task3_useful",
  "Post_AI_Trust",
  "Post_AI_Usefulness",
  "Post_AI_Affect",
  "Post_Behavioral_Intention"
)

df$Label <- factor(df$Label, levels = c("AI", "AI Human", "Human"))
```

```{r data-preprocessing-3}
# Check Distribution
ggplot(df, aes(x = stage1_task0_accuracy)) +
  geom_histogram(binwidth = 0.05, fill = "skyblue", color = "black") +
  stat_bin(binwidth = 0.05, geom = "text", aes(label = ..count..), vjust = -0.3) +
  scale_x_continuous(
    breaks = seq(0, 1, by = 0.05),
    labels = sprintf("%.2f", seq(0, 1, by = 0.05))
  ) +
  labs(
    title = "Distribution of stage1_task0_accuracy",
    x = "stage1_task0_accuracy",
    y = "Frequency"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r data-preprocessing-4}
# Filter Out stage1_task0_accuracy >= 0.9
Count <- sum(df$stage1_task0_accuracy >= 0.9)
Count

df <- df %>%
  filter(stage1_task0_accuracy < 0.9)
```

```{r data-preprocessing-5}
# Recode Background and LLM Usage
df$Stats_Background <- cut(
  as.numeric(as.character(df$Stats_Background)),
  breaks = c(1, 3, 5, 8),
  labels = c("Low", "Medium", "High"),
  right = TRUE,
  include.lowest = TRUE
)

df$Used_LLM_Frequency <- forcats::fct_collapse(
  as.character(df$Used_LLM_Frequency),
  Rarely = c("Never", "Less than once a month", "1–3 times per month"),
  Often  = c("Weekly", "Daily")
)

df$Used_LLM_Hours <- forcats::fct_collapse(
  as.character(df$Used_LLM_Hours),
  None = "0",
  Low  = c("1–5", "6–10"),
  High = c("11–20", ">20")
)
```

```{r data-preprocessing-6}
summary(df$Label)
```

```{r data-preprocessing-7}
# Convert To Longer Table
cols_to_long <- grep("^(Pre|Post|stage\\d+|follow)_", colnames(df), value = TRUE)

df_long <- df %>%
  pivot_longer(
    cols = all_of(cols_to_long),
    names_to = "fullvar",
    values_to = "Value"
  ) %>%
  mutate(
    Phase = str_extract(fullvar, "^(Pre|Post|stage\\d+|follow)"),
    tmp = str_remove(fullvar, "^(Pre|Post|stage\\d+|follow)_"),
    task = ifelse(str_detect(tmp, "^task\\d+"), str_extract(tmp, "^task\\d+"), NA),
    measure = ifelse(!is.na(task), str_remove(tmp, "^task\\d+_"), tmp),
    tmp = NULL,
    fullvar = NULL
  )

df_long$Phase <- factor(df_long$Phase, levels = c("follow", "Post", "stage3", "stage2", "stage1", "Pre"))
df_long$Task <- as.factor(df_long$task)

df_long <- df_long %>%
  dplyr::select(-task)

df_long$Label <- as.factor(df_long$Label)
df_long$ID <- as.factor(df_long$ID)

head(df_long)
```

## Baseline Equivalence Across Conditions

Before testing the hypotheses, we verify that the three labelling
conditions did not differ at baseline on the seven pre-survey measures
(objective and subjective AI literacy, AI trust, usefulness, affect,
self-efficacy, and behavioural intention). Per-condition descriptive
statistics are followed by one-way ANOVAs.

```{r baseline-equivalence-across-conditions-1}
# Descriptive statistics by condition
varnames <- rename_vars[1:7]

label_summary <- lapply(varnames, function(var) {
  df %>%
    group_by(Label) %>%
    summarise(
      Mean = round(mean(.data[[var]], na.rm = TRUE), 2),
      SD = round(sd(.data[[var]], na.rm = TRUE), 2),
      n = sum(!is.na(.data[[var]]))
    ) %>%
    mutate(Variable = var) %>%
    relocate(Variable)
})

label_summary_table <- bind_rows(label_summary)
label_summary_table
```

```{r baseline-equivalence-across-conditions-2}
# ANOVA By Label
anova_results <- lapply(varnames, function(var) {
  aov_res <- summary(aov(df[[var]] ~ df$Label))
  data.frame(
    Variable = var,
    F_value = round(aov_res[[1]][["F value"]][1], 2),
    p_value = round(aov_res[[1]][["Pr(>F)"]][1], 4)
  )
})

anova_results_table <- bind_rows(anova_results)
anova_results_table
```

## H1: Long-Term Task Performance (Accuracy)

H1 tests whether task accuracy is retained at follow-up. Linear mixed
models compare accuracy across the four phases (Stage 1–3 and follow-up)
by labelling condition, adjusting for the dropout covariates.

### Descriptive Statistics
```{r descriptive-statistics-1}
performance_long <- df_long %>%
  rename(Measure = measure) %>%
  filter(
    Measure == "accuracy",
    Task != "task0"
  )

head(performance_long)
```

```{r descriptive-statistics-2}
performance_long$Label <- as.factor(performance_long$Label)
performance_long$Phase <- as.factor(performance_long$Phase)
performance_long$Task <- as.factor(performance_long$Task)

stage_summary <- performance_long %>%
  group_by(Phase, Label) %>%
  summarise(
    Mean = round(mean(Value, na.rm = TRUE), 2),
    SD = round(sd(Value, na.rm = TRUE), 2),
    N = n()
  )

head(stage_summary)
```

### Linear Mixed Models

Phase is the within-participant factor and Label the between-participant
factor; results are reported without and with the task factor.

#### Without Task
```{r without-task-1}
follow_up_stage <- c("stage1", "stage2", "stage3", "follow")

performance_long1 <- performance_long %>%
  filter(Phase %in% follow_up_stage)

performance_long1$Phase <- factor(performance_long1$Phase, levels = c("follow", "stage3", "stage2", "stage1"))

model <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = performance_long1
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients
print(model_summary)

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Label)
cat("\n===POST HOC LABEL===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
cat("\n===POST HOC PHASE X LABEL===\n")
print(posthoc_stage_label$contrasts)

posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
cat("\n===POST HOC LABEL X PHASE===\n")
print(posthoc_label_stage$contrasts)
```

```{r without-task-2}
write.xlsx(
  list(
    Model_Summary = as.data.frame(model_summary),
    ANOVA = as.data.frame(anova_results),
    Eta_Squared = as.data.frame(eta_sq),
    Posthoc_Stage = as.data.frame(posthoc_stage$contrasts),
    Posthoc_Label = as.data.frame(posthoc_label$contrasts),
    Posthoc_Stage_Label = as.data.frame(posthoc_stage_label$contrasts)
  ),
  file = "results/Follow-Up Activity/H1/H1_Stage1_Longterm_Accuracy_Comparison_LMM.xlsx",
  rowNames = TRUE
)
```

#### With Task
```{r with-task-1}
follow_up_stage <- c("stage1", "stage2", "stage3", "follow")

performance_long1 <- performance_long %>%
  filter(Phase %in% follow_up_stage)

performance_long1$Phase <- factor(performance_long1$Phase, levels = c("follow", "stage3", "stage2", "stage1"))

model <- lmer(
  Value ~ Phase * Label * Task + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | ID:Task),
  data = performance_long1
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Task)
cat("\n===POST HOC Task===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Task)
cat("\n===POST HOC PHASE X Task===\n")
print(posthoc_stage_label$contrasts)

posthoc_stage_task_label <- emmeans(model, pairwise ~ Phase | Task | Label)
cat("\n===POST HOC PHASE X Task X Label===\n")
print(posthoc_stage_task_label$contrasts)
```

### Robustness: Item-Level Binomial GLMM

The H1 models treat phase-level accuracy — a proportion of only 5–6 binary
items — as a Gaussian outcome, which can strain linear-model assumptions.
As a robustness check we refit the phase effect as an **item-level binomial
GLMM** (the response family used for the early/late analysis), modelling
each binary item response directly with the same fixed effects and
covariates and crossed participant, item, and task intercepts:

`correct ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours + (1 | ID) + (1 | Item) + (1 | Task)`

Item responses are read from `correction_raw_data.xlsx` for the same cohort
as the H1 model (follow-up completers passing the ceiling screen). With
only three task levels the `(1 | Task)` variance may sit near the boundary,
but this does not affect the Phase × Label inference. Matching the Gaussian
LMM confirms the conclusion is robust to the modelling choice.

#### Build Item-Level Dataset (Follow-Up Completer Cohort)
```{r itemlevel-data-fu}
# Ground-truth key for the 17 items (task 1: 6, task 2: 5, task 3: 6).
item_names <- c(paste0("t1_q", 1:6), paste0("t2_q", 1:5), paste0("t3_q", 1:6))
item_truth <- c(rep(FALSE, 6), rep(FALSE, 5), FALSE, TRUE, TRUE, TRUE, FALSE, TRUE)
names(item_truth) <- item_names

# Analytic cohort = the same follow-up completers used by the H1 model.
cohort_ids <- unique(as.character(df$ID))

# Per-participant covariates, recoded identically to the primary model.
demo <- df %>%
  mutate(ID = as.character(ID)) %>%
  dplyr::select(ID, Label, Age, Gender, Field, Used_LLM_Hours) %>%
  distinct()

# Item columns span the three learning stages plus the follow-up phase.
stage_cols  <- paste0(rep(c("stage1_", "stage2_", "stage3_"), each = length(item_names)), item_names)
follow_cols <- paste0("follow_up_", item_names)

item_long <- read_excel("data/correction_raw_data.xlsx") %>%
  mutate(ID = as.character(ID)) %>%
  filter(ID %in% cohort_ids) %>%
  dplyr::select(ID, all_of(stage_cols), all_of(follow_cols)) %>%
  pivot_longer(
    cols = c(all_of(stage_cols), all_of(follow_cols)),
    names_to = c("Phase", "Item"),
    names_pattern = "^(stage[123]|follow_up)_(t[123]_q\\d+)$",
    values_to = "Answer"
  ) %>%
  mutate(
    Phase = ifelse(Phase == "follow_up", "follow", Phase),
    Truth = item_truth[as.character(Item)],
    correct = as.integer(as.logical(Answer) == Truth),
    Task = factor(sub("_q\\d+$", "", Item), levels = c("t1", "t2", "t3")),
    Item = factor(Item, levels = item_names),
    # Match the primary model's factor ordering (reference = follow).
    Phase = factor(Phase, levels = c("follow", "stage3", "stage2", "stage1")),
    ID = as.character(ID)
  ) %>%
  filter(!is.na(correct)) %>%
  left_join(demo, by = "ID") %>%
  mutate(ID = factor(ID))

# Cohort check: should equal the H1 analytic n across all four phases.
cat("Item-level cohort n =", dplyr::n_distinct(item_long$ID),
    "| item responses =", nrow(item_long), "\n")
print(item_long %>% group_by(Phase) %>% summarise(n_resp = dplyr::n(), n_id = dplyr::n_distinct(ID)))
head(item_long)
```

#### Fit Item-Level Binomial GLMM
```{r itemlevel-model-fu}
itemlevel_model <- glmer(
  correct ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Item) + (1 | Task),
  data = item_long,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(itemlevel_model)
```

#### Odds Ratios, Type-III Tests, and Contrasts
```{r itemlevel-inference-fu}
# Odds ratios for fixed effects (Wald CIs).
itemlevel_or <- exp(cbind(
  OR = fixef(itemlevel_model),
  confint(itemlevel_model, parm = "beta_", method = "Wald")
))
itemlevel_or

# Type-III tests (matches the early/late analysis convention).
itemlevel_anova <- car::Anova(itemlevel_model, type = 3)
itemlevel_anova

# Phase contrasts overall and within each label, on the response scale.
itemlevel_emm_phase <- emmeans(itemlevel_model, pairwise ~ Phase, type = "response")
itemlevel_emm_phase_label <- emmeans(itemlevel_model, pairwise ~ Phase | Label, type = "response")
itemlevel_emm_phase$contrasts
itemlevel_emm_phase_label$contrasts
```

#### Export Item-Level Robustness Results
```{r itemlevel-export-fu}
write.xlsx(
  list(
    Fixed_Effects = as.data.frame(summary(itemlevel_model)$coefficients),
    Odds_Ratios = as.data.frame(itemlevel_or),
    Type3_ANOVA = as.data.frame(itemlevel_anova),
    Posthoc_Phase = as.data.frame(itemlevel_emm_phase$contrasts),
    Posthoc_Phase_by_Label = as.data.frame(itemlevel_emm_phase_label$contrasts)
  ),
  file = "results/Follow-Up Activity/H1/H1_Performance_ItemLevel_Binomial_GLMM.xlsx",
  rowNames = TRUE
)
```

### H1 Sensitivity: Manipulation Passers Only

Because source attribution is the manipulation, we refit the primary H1
model (without the task factor) on participants who correctly recalled
their assigned label. Recall (`Recalled_Label`) is taken from this
analysis's data file, where every participant in the cohort has a response.
If the Phase × Label pattern holds, the conclusion is not driven by
participants who misremembered their condition.

#### Restrict to Passers
```{r passers-data-fu}
# Recall lookup from the analysis data file, recoded to match the Label factor
# ("AI", "AI Human", "Human").
recall_lk <- df %>%
  transmute(
    ID = as.character(ID),
    Recalled_Label = dplyr::recode(Recalled_Label, "AI + Human" = "AI Human")
  )

# Passer = recalled label matches assigned label.
passer_ids <- df %>%
  mutate(ID = as.character(ID)) %>%
  dplyr::select(ID, Label) %>%
  left_join(recall_lk, by = "ID") %>%
  filter(as.character(Label) == as.character(Recalled_Label)) %>%
  pull(ID) %>%
  unique()

# Rebuild the H1 (without-task) modelling data, then restrict to passers.
performance_pass <- performance_long %>%
  filter(Phase %in% c("stage1", "stage2", "stage3", "follow")) %>%
  filter(as.character(ID) %in% passer_ids) %>%
  droplevels()
performance_pass$Phase <- factor(performance_pass$Phase,
                                 levels = c("follow", "stage3", "stage2", "stage1"))

# Denominator = participants in the H1 (without-task) modelling data.
h1_n <- performance_long %>%
  filter(Phase %in% c("stage1", "stage2", "stage3", "follow")) %>%
  pull(ID) %>% as.character() %>% dplyr::n_distinct()
cat("Passers retained:", dplyr::n_distinct(performance_pass$ID), "of", h1_n, "participants\n")
print(performance_pass %>% group_by(Phase, Label) %>%
  summarise(Mean = round(mean(Value, na.rm = TRUE), 2),
            SD = round(sd(Value, na.rm = TRUE), 2),
            N = sum(!is.na(Value)), .groups = "drop"))
```

#### Mixed Model (Without Task, Passers Only)
```{r passers-model-fu}
model_pass <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = performance_pass
)

model_pass_summary <- summary(model_pass)$coefficients
anova_pass <- anova(model_pass)
eta_pass <- effectsize::eta_squared(model_pass, partial = TRUE)

model_pass_summary
anova_pass
eta_pass
```

#### Post-hoc Comparisons (Passers Only)
```{r passers-posthoc-fu}
posthoc_phase_pass <- emmeans(model_pass, pairwise ~ Phase)
posthoc_label_pass <- emmeans(model_pass, pairwise ~ Label)
posthoc_phase_label_pass <- emmeans(model_pass, pairwise ~ Phase | Label)
posthoc_label_phase_pass <- emmeans(model_pass, pairwise ~ Label | Phase)

cat("===Phase===\n");        print(posthoc_phase_pass$contrasts)
cat("\n===Label===\n");      print(posthoc_label_pass$contrasts)
cat("\n===Phase:Label===\n");print(posthoc_phase_label_pass$contrasts)
cat("\n===Label:Phase===\n");print(posthoc_label_phase_pass$contrasts)

cat("\n===Cohen's d: Phase===\n")
print(eff_size(posthoc_phase_pass, sigma = sigma(model_pass), edf = df.residual(model_pass)))
```

#### Export Results (Passers Only)
```{r passers-export-fu}
report(anova_pass)

write.xlsx(
  list(
    Model_Summary = as.data.frame(model_pass_summary),
    ANOVA = as.data.frame(anova_pass),
    Eta_Squared = as.data.frame(eta_pass),
    Posthoc_Phase = as.data.frame(posthoc_phase_pass$contrasts),
    Posthoc_Label = as.data.frame(posthoc_label_pass$contrasts),
    Posthoc_Phase_Label = as.data.frame(posthoc_phase_label_pass$contrasts),
    Posthoc_Label_Phase = as.data.frame(posthoc_label_phase_pass$contrasts)
  ),
  file = "results/Follow-Up Activity/H1/H1_Performance_PassersOnly_LMM.xlsx",
  rowNames = TRUE
)
```

### H1 Sensitivity: Perceived Label (As-Recalled Condition)

Complementary to the passers-only analysis, this keeps the **full sample**
but replaces the assigned `Label` with the **perceived label** each
participant recalled — the more proximal cause if the manipulation operates
through what participants *believe* they received. Passers enter under their
assigned label, non-passers under the one they believed. The primary H1
structure (without the task factor) and covariates are otherwise unchanged.

#### Attach Perceived Label
```{r perceived-data-fu}
perceived_lk <- recall_lk %>%
  transmute(ID = as.character(ID),
            PerceivedLabel = factor(Recalled_Label, levels = c("AI", "AI Human", "Human")))

performance_perc <- performance_long %>%
  filter(Phase %in% c("stage1", "stage2", "stage3", "follow")) %>%
  mutate(ID = as.character(ID)) %>%
  left_join(perceived_lk, by = "ID") %>%
  filter(!is.na(PerceivedLabel)) %>%
  mutate(ID = factor(ID)) %>%
  droplevels()
performance_perc$Phase <- factor(performance_perc$Phase,
                                 levels = c("follow", "stage3", "stage2", "stage1"))

cat("Participants with a recalled label:", dplyr::n_distinct(performance_perc$ID),
    "of", h1_n, "\n")
print(performance_perc %>% group_by(Phase, PerceivedLabel) %>%
  summarise(Mean = round(mean(Value, na.rm = TRUE), 2),
            SD = round(sd(Value, na.rm = TRUE), 2),
            N = sum(!is.na(Value)), .groups = "drop"))
```

#### Mixed Model (Without Task, Perceived Label)
```{r perceived-model-fu}
model_perc <- lmer(
  Value ~ Phase * PerceivedLabel + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = performance_perc
)

model_perc_summary <- summary(model_perc)$coefficients
anova_perc <- anova(model_perc)
eta_perc <- effectsize::eta_squared(model_perc, partial = TRUE)

model_perc_summary
anova_perc
eta_perc
```

#### Post-hoc Comparisons (Perceived Label)
```{r perceived-posthoc-fu}
posthoc_phase_perc <- emmeans(model_perc, pairwise ~ Phase)
posthoc_label_perc <- emmeans(model_perc, pairwise ~ PerceivedLabel)
posthoc_phase_label_perc <- emmeans(model_perc, pairwise ~ Phase | PerceivedLabel)
posthoc_label_phase_perc <- emmeans(model_perc, pairwise ~ PerceivedLabel | Phase)

cat("===Phase===\n");        print(posthoc_phase_perc$contrasts)
cat("\n===Perceived Label===\n");      print(posthoc_label_perc$contrasts)
cat("\n===Phase:Perceived Label===\n");print(posthoc_phase_label_perc$contrasts)
cat("\n===Perceived Label:Phase===\n");print(posthoc_label_phase_perc$contrasts)

cat("\n===Cohen's d: Phase===\n")
print(eff_size(posthoc_phase_perc, sigma = sigma(model_perc), edf = df.residual(model_perc)))
```

#### Export Results (Perceived Label)
```{r perceived-export-fu}
report(anova_perc)

write.xlsx(
  list(
    Model_Summary = as.data.frame(model_perc_summary),
    ANOVA = as.data.frame(anova_perc),
    Eta_Squared = as.data.frame(eta_perc),
    Posthoc_Phase = as.data.frame(posthoc_phase_perc$contrasts),
    Posthoc_Label = as.data.frame(posthoc_label_perc$contrasts),
    Posthoc_Phase_Label = as.data.frame(posthoc_phase_label_perc$contrasts),
    Posthoc_Label_Phase = as.data.frame(posthoc_label_phase_perc$contrasts)
  ),
  file = "results/Follow-Up Activity/H1/H1_Performance_PerceivedLabel_LMM.xlsx",
  rowNames = TRUE
)
```

## H2: Confidence, Willingness, Usefulness, and Attitude Change

H2 examines self-reported confidence, willingness to use AI, perceived
usefulness, and change over time in AI attitudes, using the same
mixed-model specification as H1.

### Confidence
```{r confidence-1}
confidence_long <- df_long %>%
  filter(
    measure == "confidence",
    Task != "task0"
  )
```

```{r confidence-2}
follow_up_stage <- c("stage1", "stage2", "stage3", "follow")

confidence_long1 <- confidence_long %>%
  filter(Phase %in% follow_up_stage)

confidence_long1$Phase <- factor(confidence_long1$Phase, levels = c("follow", "stage3", "stage2", "stage1"))

model <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = confidence_long1
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Label)
cat("\n===POST HOC LABEL===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
cat("\n===POST HOC PHASE X LABEL===\n")
print(posthoc_stage_label$contrasts)

posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
cat("\n===POST HOC LABEL X STAGE===\n")
print(posthoc_label_stage$contrasts)
```

```{r confidence-3}
write.xlsx(
  list(
    Model_Summary = as.data.frame(model_summary),
    ANOVA = as.data.frame(anova_results),
    Eta_Squared = as.data.frame(eta_sq),
    Posthoc_Stage = as.data.frame(posthoc_stage$contrasts),
    Posthoc_Label = as.data.frame(posthoc_label$contrasts),
    Posthoc_Stage_Label = as.data.frame(posthoc_stage_label$contrasts)
  ),
  file = "results/Follow-Up Activity/H2/H2_Longterm_Confidence_Change.xlsx"
)
```

### Willingness
```{r willingness-1}
willingness_long <- df_long %>%
  filter(
    measure == "willing",
    Task != "task0"
  )
```

```{r willingness-2}
follow_up_stage <- c("stage2", "stage3")

willingness_long1 <- willingness_long %>%
  filter(Phase %in% follow_up_stage)

willingness_long1$Phase <- factor(willingness_long1$Phase, levels = c("stage3", "stage2"))

model <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = willingness_long1
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Label)
cat("\n===POST HOC LABEL===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
cat("\n===POST HOC PHASE X LABEL===\n")
print(posthoc_stage_label$contrasts)

posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
cat("\n===POST HOC LABEL X STAGE===\n")
print(posthoc_label_stage$contrasts)
```

### Usefulness
```{r usefulness-1}
usefulness_long <- df_long %>%
  filter(
    measure == "useful",
    Task != "task0"
  )
```

```{r usefulness-2}
follow_up_stage <- c("stage2", "stage3")

usefulness_long1 <- usefulness_long %>%
  filter(Phase %in% follow_up_stage)

usefulness_long1$Phase <- factor(usefulness_long1$Phase, levels = c("stage3", "stage2"))

model <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = usefulness_long1
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Label)
cat("\n===POST HOC LABEL===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
cat("\n===POST HOC PHASE X LABEL===\n")
print(posthoc_stage_label$contrasts)

posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
cat("\n===POST HOC LABEL X STAGE===\n")
print(posthoc_label_stage$contrasts)
```

### Attitude Change Over Time

Change in AI attitudes is modelled across the available measurement
phases: Pre vs. follow-up for the literacy and self-efficacy measures,
and Pre vs. Post vs. follow-up for trust, usefulness, affect, and
behavioural intention.

#### Pre and Follow-Up
```{r pre-and-follow-up-1}
measures <- c("GLAT_Objective_AI_Literacy", "AILS_CCS_Subjective_AI_Literacy", "AI_Self_Efficacy")

change_stats <- list()
anova_results <- list()
eta_squared_results <- list()
posthoc_results_stage <- list()
posthoc_results_PL <- list()
posthoc_results_LP <- list()

for (msr in measures) {
  d_sub <- df_long %>%
    filter(measure == msr, Phase %in% c("Pre", "follow")) %>%
    dplyr::select(-Task)

  d_wide <- d_sub %>%
    dplyr::select(ID, Label, Phase, Value) %>%
    pivot_wider(names_from = Phase, values_from = Value) %>%
    mutate(change = follow - Pre)

  stat_tab <- d_wide %>%
    group_by(Label) %>%
    summarise(
      MeanChange = round(mean(change, na.rm = TRUE), 2),
      SD = round(sd(change, na.rm = TRUE), 2),
      N = n()
    ) %>%
    mutate(Measure = msr, .before = 1)

  change_stats[[msr]] <- stat_tab

  d_mod <- d_sub %>%
    filter(!is.na(Value))

  if (nrow(d_mod) > 0) {
    d_mod$Phase <- factor(d_mod$Phase, levels = c("follow", "Pre"))
    d_mod$Phase <- relevel(as.factor(d_mod$Phase), ref = "follow")

    model <- lmer(
      Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours + (1 | ID),
      data = d_mod
    )

    print(msr)

    aov_tab <- anova(model)
    cat("\n===ANOVA===\n")
    print(aov_tab)

    eta <- effectsize::eta_squared(model, partial = TRUE)
    cat("\n===Eta Squared===\n")
    print(eta)

    posthoc_stage <- emmeans(model, pairwise ~ Phase)
    cat("\n===Post-Hoc Phase===\n")
    print(posthoc_stage)

    posthoc_label <- emmeans(model, pairwise ~ Label)
    cat("\n===Post-Hoc Label===\n")
    print(posthoc_label)

    posthoc_PL <- emmeans(model, pairwise ~ Phase | Label)
    posthoc_LP <- emmeans(model, pairwise ~ Label | Phase)

    anova_results[[msr]] <- as.data.frame(aov_tab) %>%
      tibble::rownames_to_column("Effect") %>%
      mutate(Measure = msr, .before = 1)

    eta_squared_results[[msr]] <- as.data.frame(eta) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_stage[[msr]] <- as.data.frame(posthoc_stage$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_PL[[msr]] <- as.data.frame(posthoc_PL$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_LP[[msr]] <- as.data.frame(posthoc_LP$contrasts) %>%
      mutate(Measure = msr, .before = 1)
  }
}

final_output_list <- list(
  ChangeScore_Summary = bind_rows(change_stats),
  ANOVA_Results = bind_rows(anova_results),
  Eta_Squared_Results = bind_rows(eta_squared_results),
  Posthoc_Stage_Results = bind_rows(posthoc_results_stage),
  Posthoc_PL_Results = bind_rows(posthoc_results_PL),
  Posthoc_LP_Results = bind_rows(posthoc_results_LP)
)

write.xlsx(
  final_output_list,
  file = "results/Follow-Up Activity/H2/H2_Attitude_Change_Longterm_PF.xlsx",
  overwrite = TRUE
)
```

#### Pre, Post, Followup
```{r pre-post-followup-1}
measures <- c("AI_Trust", "AI_Usefulness", "AI_Affect", "Behavioral_Intention")

change_stats <- list()
anova_results <- list()
eta_squared_results <- list()
posthoc_results_stage <- list()
posthoc_results_PL <- list()
posthoc_results_LP <- list()

for (msr in measures) {
  d_sub <- df_long %>%
    filter(measure == msr, Phase %in% c("Pre", "Post", "follow")) %>%
    dplyr::select(-Task)

  d_wide <- d_sub %>%
    dplyr::select(ID, Label, Phase, Value) %>%
    pivot_wider(names_from = Phase, values_from = Value) %>%
    mutate(change = follow - Pre)

  stat_tab <- d_wide %>%
    group_by(Label) %>%
    summarise(
      MeanChange = round(mean(change, na.rm = TRUE), 2),
      SD = round(sd(change, na.rm = TRUE), 2),
      N = n()
    ) %>%
    mutate(Measure = msr, .before = 1)

  change_stats[[msr]] <- stat_tab

  d_mod <- d_sub %>%
    filter(!is.na(Value))

  if (nrow(d_mod) > 0) {
    d_mod$Phase <- factor(d_mod$Phase, levels = c("follow", "Post", "Pre"))
    d_mod$Phase <- relevel(as.factor(d_mod$Phase), ref = "follow")

    model <- lmer(
      Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours + (1 | ID),
      data = d_mod
    )

    cat("\n")
    print(msr)

    aov_tab <- anova(model)
    cat("\n===ANOVA===\n")
    print(aov_tab)

    eta <- effectsize::eta_squared(model, partial = TRUE)
    cat("\n===Eta Squared===\n")
    print(eta)

    posthoc_stage <- emmeans(model, pairwise ~ Phase)
    cat("\n===Post Hoc Phase===\n")
    print(posthoc_stage)

    posthoc_PL <- emmeans(model, pairwise ~ Phase | Label)
    posthoc_LP <- emmeans(model, pairwise ~ Label | Phase)

    anova_results[[msr]] <- as.data.frame(aov_tab) %>%
      tibble::rownames_to_column("Effect") %>%
      mutate(Measure = msr, .before = 1)

    eta_squared_results[[msr]] <- as.data.frame(eta) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_stage[[msr]] <- as.data.frame(posthoc_stage$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_PL[[msr]] <- as.data.frame(posthoc_PL$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_LP[[msr]] <- as.data.frame(posthoc_LP$contrasts) %>%
      mutate(Measure = msr, .before = 1)
  }
}

final_output_list <- list(
  ChangeScore_Summary = bind_rows(change_stats),
  ANOVA_Results = bind_rows(anova_results),
  Eta_Squared_Results = bind_rows(eta_squared_results),
  Posthoc_Stage_Results = bind_rows(posthoc_results_stage),
  Posthoc_PL_Results = bind_rows(posthoc_results_PL),
  Posthoc_LP_Results = bind_rows(posthoc_results_LP)
)

write.xlsx(
  final_output_list,
  file = "results/Follow-Up Activity/H2/H2_Attitude_Change_Longterm_PPF.xlsx",
  overwrite = TRUE
)
```

## H3: Moderation of Long-Term Outcomes

H3 screens whether individual-difference measures (objective/subjective
literacy, AI attitudes, statistics background, and LLM usage) moderate
the long-term effects on attitudes and on performance/confidence. Each
outcome × moderator model is fitted; multiplicity is addressed separately
in the p-value adjudication document, and significant terms are
summarised per outcome.

### Attitude Change Long-Term Moderation
#### Pre, Followup
```{r pre-followup-1}
outcomes <- c(
  "GLAT_Objective_AI_Literacy",
  "AILS_CCS_Subjective_AI_Literacy",
  "AI_Self_Efficacy"
)

moderators <- c(
  "GLAT_Objective_AI_Literacy",
  "AILS_CCS_Subjective_AI_Literacy",
  "AI_Trust",
  "AI_Usefulness",
  "AI_Affect",
  "AI_Self_Efficacy",
  "Behavioral_Intention",
  "Stats_Background",
  "Used_LLM_Frequency",
  "Used_LLM_Hours"
)

categorical_mods <- c("Stats_Background", "Used_LLM_Frequency", "Used_LLM_Hours")

outcome_abbr <- c(
  "GLAT_Objective_AI_Literacy" = "ObjLit",
  "AILS_CCS_Subjective_AI_Literacy" = "CCSLit",
  "AI_Trust" = "Trust",
  "AI_Usefulness" = "Useful",
  "AI_Affect" = "Affect",
  "AI_Self_Efficacy" = "SelfEff",
  "Behavioral_Intention" = "BehInt"
)

moderator_abbr <- c(
  "GLAT_Objective_AI_Literacy" = "ObjLit",
  "AILS_CCS_Subjective_AI_Literacy" = "CCSLit",
  "AI_Trust" = "Trust",
  "AI_Usefulness" = "Useful",
  "AI_Affect" = "Affect",
  "AI_Self_Efficacy" = "SelfEff",
  "Behavioral_Intention" = "BehInt",
  "Stats_Background" = "StatsBG",
  "Used_LLM_Frequency" = "LLMFreq",
  "Used_LLM_Hours" = "LLMHr"
)

make_excel_sheetname <- function(x) {
  x <- gsub("[:/\\?\\*\\[\\] ]", "_", x)
  x <- substr(x, 1, 31)
  return(x)
}

result_list <- list()

for (outcome in outcomes) {
  for (mod in moderators) {
    df_sub <- df_long %>%
      filter(measure == outcome, Phase %in% c("Pre", "follow"))

    if (nrow(df_sub) > 0) {
      df_sub$Phase <- factor(df_sub$Phase, levels = c("Pre", "follow"))
      df_sub$Label <- as.factor(df_sub$Label)
      df_sub$ID <- as.factor(df_sub$ID)

      posthoc_list <- list()
      formula_str <- NA_character_

      if (mod == outcome) {
        baseline_df <- df_sub %>%
          filter(Phase == "Pre") %>%
          dplyr::select(ID, BaselineScore = Value)

        df_sub <- df_sub %>%
          left_join(baseline_df, by = "ID")

        df_sub$BaselineScore <- scale(df_sub$BaselineScore, scale = FALSE)

        formula_str <- "Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours + BaselineScore + (1|ID)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      } else if (mod %in% df_long$measure) {
        mod_df <- df_long %>%
          filter(Phase == "Pre", measure == mod) %>%
          dplyr::select(ID, ModeratorScore = Value)

        df_sub <- df_sub %>%
          left_join(mod_df, by = "ID")

        df_sub$ModeratorScore <- scale(df_sub$ModeratorScore, scale = FALSE)

        formula_str <- "Value ~ Phase * Label * ModeratorScore + Age + Gender + Field + Used_LLM_Hours + (1|ID)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      } else {
        df_sub$ModeratorScore <- df_sub[[mod]]

        formula_str <- "Value ~ Phase * Label * ModeratorScore + Age + Gender + Field + Used_LLM_Hours + (1|ID)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      }

      anova_res <- anova(model)

      ANOVA <- as.data.frame(anova_res)
      ANOVA$Variable <- rownames(ANOVA)
      ANOVA <- ANOVA[, c("Variable", setdiff(names(ANOVA), "Variable"))]

      eta_sq <- eta_squared(model, partial = TRUE)

      coef_tbl <- as.data.frame(summary(model)$coefficients)
      coef_tbl$Variable <- rownames(coef_tbl)
      coef_tbl <- coef_tbl[, c("Variable", setdiff(names(coef_tbl), "Variable"))]

      if ("Pr(>F)" %in% names(ANOVA)) {
        sig_terms <- rownames(ANOVA)[which(ANOVA$`Pr(>F)` < 0.05)]
      } else {
        sig_terms <- character(0)
      }

      for (term in sig_terms) {
        clean_term <- gsub("[:/\\\\?\\*\\[\\]]", "_", term)

        term_vars <- unlist(strsplit(term, ":"))
        left_facs <- setdiff(term_vars, c(mod, "ModeratorScore"))

        if (mod %in% categorical_mods && any(term_vars %in% c(mod, "ModeratorScore"))) {
          ph_em <- tryCatch(
            emmeans(model, pairwise ~ Label | ModeratorScore),
            error = function(e) NULL
          )

          if (!is.null(ph_em)) {
            posthoc_list[[clean_term]] <- as.data.frame(ph_em$contrasts)
          }
        } else if (!(mod %in% categorical_mods) && any(term_vars %in% c(mod, "ModeratorScore"))) {
          if (length(left_facs) == 0) {
            specs <- ~1
          } else {
            specs <- as.formula(paste0("~", paste(left_facs, collapse = "*")))
          }

          et <- tryCatch(
            emtrends(
              model,
              specs = specs,
              var = ifelse("ModeratorScore" %in% term_vars, "ModeratorScore", mod),
              infer = c(TRUE, TRUE)
            ),
            error = function(e) NULL
          )

          cat("\n")
          print(outcome)
          print(mod)
          print(et)

          if (!is.null(et)) {
            posthoc_list[[paste0(clean_term, "_trends")]] <- as.data.frame(summary(et, infer = c(TRUE, TRUE)))

            if (length(left_facs) > 0) {
              ph_pair <- tryCatch(as.data.frame(pairs(et)), error = function(e) NULL)
              if (!is.null(ph_pair)) {
                posthoc_list[[paste0(clean_term, "_trends_pairs")]] <- ph_pair
              }
            }
          }
        } else if (length(term_vars) > 0) {
          em_out <- tryCatch(emmeans(model, specs = term_vars), error = function(e) NULL)
          if (!is.null(em_out)) {
            posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
          }
        }
      }

      result_list[[paste0(outcome, "_by_", mod)]] <- list(
        Formula = formula_str,
        ANOVA = ANOVA,
        Eta_Squared = as.data.frame(eta_sq),
        Coef_Summary = coef_tbl,
        Posthoc = posthoc_list
      )
    }
  }
}

flat_result_list <- list()

for (name in names(result_list)) {
  name_parts <- unlist(strsplit(name, "_by_", fixed = TRUE))
  outcome <- ifelse(length(name_parts) >= 1, name_parts[1], name)
  moderator <- ifelse(length(name_parts) >= 2, name_parts[2], "")

  out_abbr <- ifelse(outcome %in% names(outcome_abbr), outcome_abbr[[outcome]], substr(outcome, 1, 8))
  mod_abbr <- ifelse(moderator %in% names(moderator_abbr), moderator_abbr[[moderator]], substr(moderator, 1, 8))

  prefix <- if (mod_abbr != "") paste(out_abbr, mod_abbr, sep = "_") else out_abbr

  if (!is.null(result_list[[name]]$ANOVA)) {
    flat_result_list[[make_excel_sheetname(paste0(prefix, "_ANOVA"))]] <- result_list[[name]]$ANOVA
  }

  if (!is.null(result_list[[name]]$Eta_Squared)) {
    flat_result_list[[make_excel_sheetname(paste0(prefix, "_EtaSq"))]] <- result_list[[name]]$Eta_Squared
  }

  if (!is.null(result_list[[name]]$Coef_Summary)) {
    flat_result_list[[make_excel_sheetname(paste0(prefix, "_Coef"))]] <- result_list[[name]]$Coef_Summary
  }

  if (!is.null(result_list[[name]]$Posthoc)) {
    for (int_type in names(result_list[[name]]$Posthoc)) {
      ph <- result_list[[name]]$Posthoc[[int_type]]
      if (!is.null(ph) && is.data.frame(ph) && !is.na(nrow(ph)) && nrow(ph) > 0) {
        flat_result_list[[make_excel_sheetname(
          paste0(prefix, "*Posthoc*", substr(int_type, 1, 10))
        )]] <- ph
      }
    }
  }
}

names(flat_result_list) <- gsub(":", "_", names(flat_result_list))

if (!dir.exists("results/Follow-Up Activity")) dir.create("results/Follow-Up Activity", recursive = TRUE)

write.xlsx(
  flat_result_list,
  file = "results/Follow-Up Activity/H3/H3_Attitude_Change_Longterm_Moderation_PF.xlsx"
)
```

##### Export Results Summary
```{r export-results-summary-1}
export_sig_effects <- function(result_list, out_excel_path) {
  if (!dir.exists(dirname(out_excel_path))) {
    dir.create(dirname(out_excel_path), recursive = TRUE)
  }

  summary_sig_effects <- data.frame(
    DV = character(),
    Moderator = character(),
    Term = character(),
    NumDF = numeric(),
    DenDF = numeric(),
    F_value = numeric(),
    p_value = numeric(),
    eta_p = numeric(),
    stringsAsFactors = FALSE
  )

  for (res_name in names(result_list)) {
    split_name <- unlist(strsplit(res_name, "_by_", fixed = TRUE))
    DV <- split_name[1]
    Moderator <- split_name[2]


    ANOVA <- result_list[[res_name]]$ANOVA
    Eta <- result_list[[res_name]]$Eta_Squared

    if (!is.null(ANOVA) && "Pr(>F)" %in% names(ANOVA) && "F value" %in% names(ANOVA)) {
      sig_rows <- which(ANOVA$`Pr(>F)` <= 1)

      if (length(sig_rows) > 0) {
        for (i in sig_rows) {
          this_term <- ANOVA$Variable[i]
          Ndf <- ANOVA$NumDF[i]
          Ddf <- ANOVA$DenDF[i]
          Fval <- ANOVA$`F value`[i]
          pval <- ANOVA$`Pr(>F)`[i]

          eta_row <- NULL
          if (!is.null(Eta) && "Parameter" %in% names(Eta)) {
            eta_row <- Eta[Eta$Parameter == this_term, ]
          }

          eta_val <- NA
          if (!is.null(eta_row) && nrow(eta_row) == 1) {
            if ("Eta2_partial" %in% names(eta_row)) eta_val <- eta_row$Eta2_partial
            if ("Eta2" %in% names(eta_row) && is.na(eta_val)) eta_val <- eta_row$Eta2
          }

          summary_sig_effects <- rbind(
            summary_sig_effects,
            data.frame(
              DV = DV,
              Moderator = Moderator,
              Term = this_term,
              NumDF = Ndf,
              DenDF = Ddf,
              F_value = Fval,
              p_value = pval,
              eta_p = eta_val
            )
          )
        }
      }
    }
  }

  summary_sig_effects <- summary_sig_effects[
    order(summary_sig_effects$DV, summary_sig_effects$Moderator, summary_sig_effects$p_value),
  ]

  write.xlsx(summary_sig_effects, file = out_excel_path, rowNames = FALSE)
  cat(sprintf("Significant terms summary saved to %s\n", out_excel_path))
  invisible(summary_sig_effects)
}

export_sig_effects(
  result_list,
  out_excel_path = "results/Follow-Up Activity/H3/H3_Attitude_Longterm_Moderation_Summary_PF.xlsx"
)
```

#### Pre, Post, Followup
```{r pre-post-followup-2}
outcomes <- c(
  "AI_Trust",
  "AI_Usefulness",
  "AI_Affect",
  "Behavioral_Intention"
)

moderators <- c(
  "GLAT_Objective_AI_Literacy",
  "AILS_CCS_Subjective_AI_Literacy",
  "AI_Trust",
  "AI_Usefulness",
  "AI_Affect",
  "AI_Self_Efficacy",
  "Behavioral_Intention",
  "Stats_Background",
  "Used_LLM_Frequency",
  "Used_LLM_Hours"
)

categorical_mods <- c("Stats_Background", "Used_LLM_Frequency", "Used_LLM_Hours")

outcome_abbr <- c(
  "GLAT_Objective_AI_Literacy" = "ObjLit",
  "AILS_CCS_Subjective_AI_Literacy" = "CCSLit",
  "AI_Trust" = "Trust",
  "AI_Usefulness" = "Useful",
  "AI_Affect" = "Affect",
  "AI_Self_Efficacy" = "SelfEff",
  "Behavioral_Intention" = "BehInt"
)

moderator_abbr <- c(
  "GLAT_Objective_AI_Literacy" = "ObjLit",
  "AILS_CCS_Subjective_AI_Literacy" = "CCSLit",
  "AI_Trust" = "Trust",
  "AI_Usefulness" = "Useful",
  "AI_Affect" = "Affect",
  "AI_Self_Efficacy" = "SelfEff",
  "Behavioral_Intention" = "BehInt",
  "Stats_Background" = "StatsBG",
  "Used_LLM_Frequency" = "LLMFreq",
  "Used_LLM_Hours" = "LLMHr"
)

make_excel_sheetname <- function(x) {
  x <- gsub("[:/\\?\\*\\[\\] ]", "_", x)
  x <- substr(x, 1, 31)
  return(x)
}

result_list <- list()

for (outcome in outcomes) {
  for (mod in moderators) {
    df_sub <- df_long %>%
      filter(measure == outcome, Phase %in% c("Pre", "Post", "follow"))

    if (nrow(df_sub) > 0) {
      df_sub$Phase <- factor(df_sub$Phase, levels = c("Pre", "Post", "follow"))
      df_sub$Label <- as.factor(df_sub$Label)
      df_sub$ID <- as.factor(df_sub$ID)

      posthoc_list <- list()
      formula_str <- NA_character_

      if (mod == outcome) {
        baseline_df <- df_sub %>%
          filter(Phase == "Pre") %>%
          dplyr::select(ID, BaselineScore = Value)

        df_sub <- df_sub %>%
          left_join(baseline_df, by = "ID")

        df_sub$BaselineScore <- scale(df_sub$BaselineScore, scale = FALSE)

        formula_str <- "Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours + BaselineScore + (1|ID)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      } else if (mod %in% df_long$measure) {
        mod_df <- df_long %>%
          filter(Phase == "Pre", measure == mod) %>%
          dplyr::select(ID, ModeratorScore = Value)

        df_sub <- df_sub %>%
          left_join(mod_df, by = "ID")

        df_sub$ModeratorScore <- scale(df_sub$ModeratorScore, scale = FALSE)

        formula_str <- "Value ~ Phase * Label * ModeratorScore + Age + Gender + Field + Used_LLM_Hours + (1|ID)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      } else {
        df_sub$ModeratorScore <- df_sub[[mod]]

        formula_str <- "Value ~ Phase * Label * ModeratorScore + Age + Gender + Field + Used_LLM_Hours + (1|ID)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      }

      anova_res <- anova(model)

      ANOVA <- as.data.frame(anova_res)
      ANOVA$Variable <- rownames(ANOVA)
      ANOVA <- ANOVA[, c("Variable", setdiff(names(ANOVA), "Variable"))]

      eta_sq <- effectsize::eta_squared(model, partial = TRUE)

      coef_tbl <- as.data.frame(summary(model)$coefficients)
      coef_tbl$Variable <- rownames(coef_tbl)
      coef_tbl <- coef_tbl[, c("Variable", setdiff(names(coef_tbl), "Variable"))]

      if ("Pr(>F)" %in% names(ANOVA)) {
        sig_terms <- rownames(ANOVA)[which(ANOVA$`Pr(>F)` < 0.05)]
      } else {
        sig_terms <- character(0)
      }

      for (term in sig_terms) {
        clean_term <- gsub("[:/\\\\?\\*\\[\\]]", "_", term)

        term_vars <- unlist(strsplit(term, ":"))
        left_facs <- setdiff(term_vars, c(mod, "ModeratorScore"))

        if (mod %in% categorical_mods && any(term_vars %in% c(mod, "ModeratorScore"))) {
          ph_em <- tryCatch(
            emmeans(model, pairwise ~ Label | ModeratorScore),
            error = function(e) NULL
          )

          if (!is.null(ph_em)) {
            posthoc_list[[clean_term]] <- as.data.frame(ph_em$contrasts)
          }
        } else if (!(mod %in% categorical_mods) && any(term_vars %in% c(mod, "ModeratorScore"))) {
          if (length(left_facs) == 0) {
            specs <- ~1
          } else {
            specs <- as.formula(paste0("~", paste(left_facs, collapse = "*")))
          }

          et <- tryCatch(
            emtrends(
              model,
              specs = specs,
              var = ifelse("ModeratorScore" %in% term_vars, "ModeratorScore", mod),
              infer = c(TRUE, TRUE)
            ),
            error = function(e) NULL
          )

          cat("\n===", outcome, "+", mod, "===\n")
          print(et)

          if (!is.null(et)) {
            posthoc_list[[paste0(clean_term, "_trends")]] <- as.data.frame(summary(et, infer = c(TRUE, TRUE)))

            if (length(left_facs) > 0) {
              ph_pair <- tryCatch(as.data.frame(pairs(et)), error = function(e) NULL)
              if (!is.null(ph_pair)) {
                posthoc_list[[paste0(clean_term, "_trends_pairs")]] <- ph_pair
              }
            }
          }
        } else if (length(term_vars) > 0) {
          em_out <- tryCatch(emmeans(model, specs = term_vars), error = function(e) NULL)
          if (!is.null(em_out)) {
            posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
          }
        }
      }

      result_list[[paste0(outcome, "_by_", mod)]] <- list(
        Formula = formula_str,
        ANOVA = ANOVA,
        Eta_Squared = as.data.frame(eta_sq),
        Coef_Summary = coef_tbl,
        Posthoc = posthoc_list
      )
    }
  }
}

flat_result_list <- list()

for (name in names(result_list)) {
  name_parts <- unlist(strsplit(name, "_by_", fixed = TRUE))
  outcome <- ifelse(length(name_parts) >= 1, name_parts[1], name)
  moderator <- ifelse(length(name_parts) >= 2, name_parts[2], "")

  out_abbr <- ifelse(outcome %in% names(outcome_abbr), outcome_abbr[[outcome]], substr(outcome, 1, 8))
  mod_abbr <- ifelse(moderator %in% names(moderator_abbr), moderator_abbr[[moderator]], substr(moderator, 1, 8))

  prefix <- if (mod_abbr != "") paste(out_abbr, mod_abbr, sep = "_") else out_abbr

  if (!is.null(result_list[[name]]$ANOVA)) {
    flat_result_list[[make_excel_sheetname(paste0(prefix, "_ANOVA"))]] <- result_list[[name]]$ANOVA
  }

  if (!is.null(result_list[[name]]$Eta_Squared)) {
    flat_result_list[[make_excel_sheetname(paste0(prefix, "_EtaSq"))]] <- result_list[[name]]$Eta_Squared
  }

  if (!is.null(result_list[[name]]$Coef_Summary)) {
    flat_result_list[[make_excel_sheetname(paste0(prefix, "_Coef"))]] <- result_list[[name]]$Coef_Summary
  }

  if (!is.null(result_list[[name]]$Posthoc)) {
    for (int_type in names(result_list[[name]]$Posthoc)) {
      ph <- result_list[[name]]$Posthoc[[int_type]]
      if (!is.null(ph) && is.data.frame(ph) && !is.na(nrow(ph)) && nrow(ph) > 0) {
        flat_result_list[[make_excel_sheetname(
          paste0(prefix, "*Posthoc*", substr(int_type, 1, 10))
        )]] <- ph
      }
    }
  }
}

names(flat_result_list) <- gsub(":", "_", names(flat_result_list))

if (!dir.exists("results/Follow-Up Activity")) dir.create("results/Follow-Up Activity", recursive = TRUE)

write.xlsx(
  flat_result_list,
  file = "results/Follow-Up Activity/H3/H3_Attitude_Change_Longterm_Moderation_PPF.xlsx"
)
```

##### Export Results Summary
```{r export-results-summary-2}
export_sig_effects <- function(result_list, out_excel_path) {
  if (!dir.exists(dirname(out_excel_path))) {
    dir.create(dirname(out_excel_path), recursive = TRUE)
  }

  summary_sig_effects <- data.frame(
    DV = character(),
    Moderator = character(),
    Term = character(),
    NumDF = numeric(),
    DenDF = numeric(),
    F_value = numeric(),
    p_value = numeric(),
    eta_p = numeric(),
    stringsAsFactors = FALSE
  )

  for (res_name in names(result_list)) {
    split_name <- unlist(strsplit(res_name, "_by_", fixed = TRUE))
    DV <- split_name[1]
    Moderator <- split_name[2]

    ANOVA <- result_list[[res_name]]$ANOVA
    Eta <- result_list[[res_name]]$Eta_Squared

    if (!is.null(ANOVA) && "Pr(>F)" %in% names(ANOVA) && "F value" %in% names(ANOVA)) {
      sig_rows <- which(ANOVA$`Pr(>F)` <= 1)

      if (length(sig_rows) > 0) {
        for (i in sig_rows) {
          this_term <- ANOVA$Variable[i]
          Ndf <- ANOVA$NumDF[i]
          Ddf <- ANOVA$DenDF[i]
          Fval <- ANOVA$`F value`[i]
          pval <- ANOVA$`Pr(>F)`[i]

          eta_row <- NULL
          if (!is.null(Eta) && "Parameter" %in% names(Eta)) {
            eta_row <- Eta[Eta$Parameter == this_term, ]
          }

          eta_val <- NA
          if (!is.null(eta_row) && nrow(eta_row) == 1) {
            if ("Eta2_partial" %in% names(eta_row)) eta_val <- eta_row$Eta2_partial
            if ("Eta2" %in% names(eta_row) && is.na(eta_val)) eta_val <- eta_row$Eta2
          }

          summary_sig_effects <- rbind(
            summary_sig_effects,
            data.frame(
              DV = DV,
              Moderator = Moderator,
              Term = this_term,
              NumDF = Ndf,
              DenDF = Ddf,
              F_value = Fval,
              p_value = pval,
              eta_p = eta_val
            )
          )
        }
      }
    }
  }

  summary_sig_effects <- summary_sig_effects[
    order(summary_sig_effects$DV, summary_sig_effects$Moderator, summary_sig_effects$p_value),
  ]

  write.xlsx(summary_sig_effects, file = out_excel_path, rowNames = FALSE)
  cat(sprintf("Significant terms summary saved to %s\n", out_excel_path))
  invisible(summary_sig_effects)
}

export_sig_effects(
  result_list,
  out_excel_path = "results/Follow-Up Activity/H3/H3_Attitude_Longterm_Moderation_Summary_PPF.xlsx"
)
```

### Performance & Confidence Longterm Moderation
#### Stage1, Stage2, Stage3, Followup
```{r stage1-stage2-stage3-followup-1}
outcomes <- c("accuracy", "confidence")

moderators <- c(
  "GLAT_Objective_AI_Literacy",
  "AILS_CCS_Subjective_AI_Literacy",
  "AI_Trust",
  "AI_Usefulness",
  "AI_Affect",
  "AI_Self_Efficacy",
  "Behavioral_Intention",
  "Stats_Background",
  "Used_LLM_Frequency",
  "Used_LLM_Hours"
)

categorical_mods <- c("Stats_Background", "Used_LLM_Frequency", "Used_LLM_Hours")

outcome_abbr <- c(
  "accuracy" = "Acc",
  "confidence" = "Conf"
)

moderator_abbr <- c(
  "GLAT_Objective_AI_Literacy" = "ObjLit",
  "AILS_CCS_Subjective_AI_Literacy" = "CCSLit",
  "AI_Trust" = "Trust",
  "AI_Usefulness" = "Useful",
  "AI_Affect" = "Affect",
  "AI_Self_Efficacy" = "SelfEff",
  "Behavioral_Intention" = "BehInt",
  "Stats_Background" = "StatsBG",
  "Used_LLM_Frequency" = "LLMFreq",
  "Used_LLM_Hours" = "LLMHr"
)

make_excel_sheetname <- function(x) {
  x <- gsub("[:/\\?\\*\\[\\] ]", "_", x)
  x <- substr(x, 1, 31)
  return(x)
}

follow_up_stage <- c("stage1", "stage2", "stage3", "follow")

result_list <- list()

for (outcome in outcomes) {
  for (mod in moderators) {
    df_sub <- df_long %>%
      filter(
        measure == outcome,
        Task != "task0",
        Phase %in% follow_up_stage
      )

    if (nrow(df_sub) > 0) {
      df_sub$Phase <- factor(df_sub$Phase, levels = c("follow", "stage3", "stage2", "stage1"))
      df_sub$Label <- as.factor(df_sub$Label)
      df_sub$Task <- as.factor(df_sub$Task)
      df_sub$ID <- as.factor(df_sub$ID)

      posthoc_list <- list()
      formula_str <- NA_character_

      if (mod %in% df_long$measure) {
        mod_df <- df_long %>%
          filter(Phase == "Pre", measure == mod) %>%
          dplyr::select(ID, ModeratorScore = Value)

        df_sub <- df_sub %>%
          left_join(mod_df, by = "ID")

        df_sub$ModeratorScore <- scale(df_sub$ModeratorScore, scale = FALSE)

        formula_str <- "Value ~ Phase * Label * ModeratorScore + Age + Gender + Field + Used_LLM_Hours + (1|ID) + (1|Task) + (1|ID:Task)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      } else {
        df_sub$ModeratorScore <- df_sub[[mod]]

        formula_str <- "Value ~ Phase * Label * ModeratorScore + Age + Gender + Field + Used_LLM_Hours + (1|ID) + (1|Task) + (1|ID:Task)"
        model <- lmer(as.formula(formula_str), data = df_sub)
      }

      anova_res <- anova(model)

      ANOVA <- as.data.frame(anova_res)
      ANOVA$Variable <- rownames(ANOVA)
      ANOVA <- ANOVA[, c("Variable", setdiff(names(ANOVA), "Variable"))]

      eta_sq <- effectsize::eta_squared(model, partial = TRUE)

      coef_tbl <- as.data.frame(summary(model)$coefficients)
      coef_tbl$Variable <- rownames(coef_tbl)
      coef_tbl <- coef_tbl[, c("Variable", setdiff(names(coef_tbl), "Variable"))]

      if ("Pr(>F)" %in% names(ANOVA)) {
        sig_terms <- rownames(ANOVA)[which(ANOVA$`Pr(>F)` < 0.05)]
      } else {
        sig_terms <- character(0)
      }

      for (term in sig_terms) {
        clean_term <- gsub("[:/\\\\?\\*\\[\\]]", "_", term)

        term_vars <- unlist(strsplit(term, ":"))
        left_facs <- setdiff(term_vars, c(mod, "ModeratorScore"))

        if (mod %in% categorical_mods && any(term_vars %in% c(mod, "ModeratorScore"))) {
          ph_em <- tryCatch(
            emmeans(model, pairwise ~ Label | ModeratorScore),
            error = function(e) NULL
          )

          if (!is.null(ph_em)) {
            posthoc_list[[clean_term]] <- as.data.frame(ph_em$contrasts)
          }
        } else if (!(mod %in% categorical_mods) && any(term_vars %in% c(mod, "ModeratorScore"))) {
          if (length(left_facs) == 0) {
            specs <- ~1
          } else {
            specs <- as.formula(paste0("~", paste(left_facs, collapse = "*")))
          }

          et <- tryCatch(
            emtrends(
              model,
              specs = specs,
              var = ifelse("ModeratorScore" %in% term_vars, "ModeratorScore", mod),
              infer = c(TRUE, TRUE)
            ),
            error = function(e) NULL
          )

          cat("\n===", outcome, "+", mod, "===\n")
          print(et)

          if (!is.null(et)) {
            posthoc_list[[paste0(clean_term, "_trends")]] <- as.data.frame(summary(et, infer = c(TRUE, TRUE)))

            if (length(left_facs) > 0) {
              ph_pair <- tryCatch(as.data.frame(pairs(et)), error = function(e) NULL)
              if (!is.null(ph_pair)) {
                posthoc_list[[paste0(clean_term, "_trends_pairs")]] <- ph_pair
              }
            }
          }
        } else if (length(term_vars) > 0) {
          em_out <- tryCatch(emmeans(model, specs = term_vars), error = function(e) NULL)
          if (!is.null(em_out)) {
            posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
          }
        }
      }

      result_list[[paste0(outcome, "_by_", mod)]] <- list(
        Formula = formula_str,
        ANOVA = ANOVA,
        Eta_Squared = as.data.frame(eta_sq),
        Coef_Summary = coef_tbl,
        Posthoc = posthoc_list
      )
    }
  }
}

flat_result_list <- list()

for (name in names(result_list)) {
  name_parts <- unlist(strsplit(name, "_by_", fixed = TRUE))
  outcome <- ifelse(length(name_parts) >= 1, name_parts[1], name)
  moderator <- ifelse(length(name_parts) >= 2, name_parts[2], "")

  out_abbr <- ifelse(outcome %in% names(outcome_abbr), outcome_abbr[[outcome]], substr(outcome, 1, 8))
  mod_abbr <- ifelse(moderator %in% names(moderator_abbr), moderator_abbr[[moderator]], substr(moderator, 1, 8))

  prefix <- if (mod_abbr != "") paste(out_abbr, mod_abbr, sep = "_") else out_abbr

  if (!is.null(result_list[[name]]$ANOVA)) {
    flat_result_list[[make_excel_sheetname(paste0(prefix, "_ANOVA"))]] <- result_list[[name]]$ANOVA
  }

  if (!is.null(result_list[[name]]$Eta_Squared)) {
    flat_result_list[[make_excel_sheetname(paste0(prefix, "_EtaSq"))]] <- result_list[[name]]$Eta_Squared
  }

  if (!is.null(result_list[[name]]$Coef_Summary)) {
    flat_result_list[[make_excel_sheetname(paste0(prefix, "_Coef"))]] <- result_list[[name]]$Coef_Summary
  }

  if (!is.null(result_list[[name]]$Posthoc)) {
    for (int_type in names(result_list[[name]]$Posthoc)) {
      ph <- result_list[[name]]$Posthoc[[int_type]]
      if (!is.null(ph) && is.data.frame(ph) && !is.na(nrow(ph)) && nrow(ph) > 0) {
        flat_result_list[[make_excel_sheetname(
          paste0(prefix, "*Posthoc*", substr(int_type, 1, 10))
        )]] <- ph
      }
    }
  }
}

names(flat_result_list) <- gsub(":", "_", names(flat_result_list))

if (!dir.exists("results/Follow-Up Activity")) dir.create("results/Follow-Up Activity", recursive = TRUE)

write.xlsx(
  flat_result_list,
  file = "results/Follow-Up Activity/H3/H3_Performance_Confidence_Longterm_Moderation.xlsx"
)
```

##### Export Results Summary
```{r export-results-summary-3}
export_sig_effects <- function(result_list, out_excel_path) {
  if (!dir.exists(dirname(out_excel_path))) {
    dir.create(dirname(out_excel_path), recursive = TRUE)
  }

  summary_sig_effects <- data.frame(
    DV = character(),
    Moderator = character(),
    Term = character(),
    NumDF = numeric(),
    DenDF = numeric(),
    F_value = numeric(),
    p_value = numeric(),
    eta_p = numeric(),
    stringsAsFactors = FALSE
  )

  for (res_name in names(result_list)) {
    split_name <- unlist(strsplit(res_name, "_by_", fixed = TRUE))
    DV <- split_name[1]
    Moderator <- split_name[2]

    ANOVA <- result_list[[res_name]]$ANOVA
    Eta <- result_list[[res_name]]$Eta_Squared

    if (!is.null(ANOVA) && "Pr(>F)" %in% names(ANOVA) && "F value" %in% names(ANOVA)) {
      sig_rows <- which(ANOVA$`Pr(>F)` <= 1)

      if (length(sig_rows) > 0) {
        for (i in sig_rows) {
          this_term <- ANOVA$Variable[i]
          Ndf <- ANOVA$NumDF[i]
          Ddf <- ANOVA$DenDF[i]
          Fval <- ANOVA$`F value`[i]
          pval <- ANOVA$`Pr(>F)`[i]

          eta_row <- NULL
          if (!is.null(Eta) && "Parameter" %in% names(Eta)) {
            eta_row <- Eta[Eta$Parameter == this_term, ]
          }

          eta_val <- NA
          if (!is.null(eta_row) && nrow(eta_row) == 1) {
            if ("Eta2_partial" %in% names(eta_row)) eta_val <- eta_row$Eta2_partial
            if ("Eta2" %in% names(eta_row) && is.na(eta_val)) eta_val <- eta_row$Eta2
          }

          summary_sig_effects <- rbind(
            summary_sig_effects,
            data.frame(
              DV = DV,
              Moderator = Moderator,
              Term = this_term,
              NumDF = Ndf,
              DenDF = Ddf,
              F_value = Fval,
              p_value = pval,
              eta_p = eta_val
            )
          )
        }
      }
    }
  }

  summary_sig_effects <- summary_sig_effects[
    order(summary_sig_effects$DV, summary_sig_effects$Moderator, summary_sig_effects$p_value),
  ]

  write.xlsx(summary_sig_effects, file = out_excel_path, rowNames = FALSE)
  cat(sprintf("Significant terms summary saved to %s\n", out_excel_path))
  invisible(summary_sig_effects)
}

export_sig_effects(
  result_list,
  out_excel_path = "results/Follow-Up Activity/H3/H3_Performance_Confidence_Longterm_Moderation_Summary.xlsx"
)
```

### Continued Use Application
```{r continued-use-application-1}
behavior_map <- c(
  follow_activity_1 = "applied_stat_concepts",
  follow_activity_2 = "used_llms_stat",
  follow_activity_3 = "used_llms_general",
  follow_activity_4 = "stayed_updated_ai"
)

result_list <- list()

for (v in names(behavior_map)) {
  df_bhv <- df %>%
    dplyr::select(ID, Label, !!rlang::sym(v)) %>%
    dplyr::rename(Value = !!rlang::sym(v)) %>%
    dplyr::filter(!is.na(Value))

  means <- df_bhv %>%
    group_by(Label) %>%
    summarise(
      Mean = round(mean(as.numeric(Value), na.rm = TRUE), 2),
      SD = round(sd(as.numeric(Value), na.rm = TRUE), 2),
      N = n()
    )

  aov_mod <- aov(Value ~ Label, data = df_bhv)
  anova_tab <- as.data.frame(summary(aov_mod)[[1]])
  posthoc_aov <- as.data.frame(emmeans(aov_mod, pairwise ~ Label)$contrasts)

  kw_mod <- rstatix::kruskal_test(Value ~ Label, data = df_bhv)
  dunn_mod <- rstatix::dunn_test(Value ~ Label, data = df_bhv, p.adjust.method = "bonferroni")

  df_bhv$Value_ord <- as.ordered(df_bhv$Value)
  ord_mod <- MASS::polr(Value_ord ~ Label, data = df_bhv, Hess = TRUE)
  ord_aov <- car::Anova(ord_mod)

  cat("\n===", v, "===\n")
  print(ord_aov)
  cat("\n")

  posthoc_ord <- as.data.frame(emmeans(ord_mod, pairwise ~ Label)$contrasts)

  nm <- behavior_map[[v]]

  result_list[[paste0(nm, "_summary")]] <- means
  result_list[[paste0(nm, "_anova")]] <- anova_tab
  result_list[[paste0(nm, "_ph_aov")]] <- posthoc_aov
  result_list[[paste0(nm, "_kruskal")]] <- as.data.frame(kw_mod)
  result_list[[paste0(nm, "_dunn")]] <- as.data.frame(dunn_mod)
  result_list[[paste0(nm, "_ordinal")]] <- as.data.frame(summary(ord_mod)$coefficients)
  result_list[[paste0(nm, "_ph_ord")]] <- posthoc_ord
}

write.xlsx(
  result_list,
  file = "results/Follow-Up Activity/H2/Continued_Use_Application.xlsx",
  row.names = TRUE
)
```

## Sensitivity Check

To check the robustness of the initial-session findings, we also ran a
sensitivity analysis including only participants who completed both the
initial-session and the follow-up session. In this analysis, we added
significant predictors of dropout as covariates to adjust for attrition bias.
These models therefore restrict the phases to the initial session
(`stage1`, `stage2`, `stage3`; the follow-up phase is excluded) on the
follow-up completer sample, and use the same covariate set as the MAR
specification: `Value ~ Phase * Label + Age + Gender + Field +
Used_LLM_Hours + (1 | ID) + (1 | Task) + (1 | ID:Task)`.

### H1 (Accuracy)
```{r h1-accuracy-1}
initial_stage <- c("stage1", "stage2", "stage3")

performance_sens <- performance_long %>%
  filter(Phase %in% initial_stage)

performance_sens$Phase <- factor(performance_sens$Phase, levels = c("stage3", "stage2", "stage1"))
performance_sens$Label <- as.factor(performance_sens$Label)
performance_sens$Task <- as.factor(performance_sens$Task)

model <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = performance_sens
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients
print(model_summary)

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Label)
cat("\n===POST HOC LABEL===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
cat("\n===POST HOC PHASE X LABEL===\n")
print(posthoc_stage_label$contrasts)

posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
cat("\n===POST HOC LABEL X PHASE===\n")
print(posthoc_label_stage$contrasts)
```

### H2 (Confidence)
```{r h2-confidence-1}
initial_stage <- c("stage1", "stage2", "stage3")

confidence_sens <- confidence_long %>%
  filter(Phase %in% initial_stage)

confidence_sens$Phase <- factor(confidence_sens$Phase, levels = c("stage3", "stage2", "stage1"))
confidence_sens$Label <- as.factor(confidence_sens$Label)
confidence_sens$Task <- as.factor(confidence_sens$Task)

model <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = confidence_sens
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients
print(model_summary)

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Label)
cat("\n===POST HOC LABEL===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
cat("\n===POST HOC PHASE X LABEL===\n")
print(posthoc_stage_label$contrasts)

posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
cat("\n===POST HOC LABEL X PHASE===\n")
print(posthoc_label_stage$contrasts)
```

### Willingness
```{r willingness-3}
# Willingness is measured at stage2 and stage3 only (initial session).
initial_stage <- c("stage2", "stage3")

willingness_sens <- willingness_long %>%
  filter(Phase %in% initial_stage)

willingness_sens$Phase <- factor(willingness_sens$Phase, levels = c("stage3", "stage2"))
willingness_sens$Label <- as.factor(willingness_sens$Label)
willingness_sens$Task <- as.factor(willingness_sens$Task)

model <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = willingness_sens
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients
print(model_summary)

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Label)
cat("\n===POST HOC LABEL===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
cat("\n===POST HOC PHASE X LABEL===\n")
print(posthoc_stage_label$contrasts)

posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
cat("\n===POST HOC LABEL X PHASE===\n")
print(posthoc_label_stage$contrasts)
```

### Usefulness
```{r usefulness-3}
# Usefulness is measured at stage2 and stage3 only (initial session).
initial_stage <- c("stage2", "stage3")

usefulness_sens <- usefulness_long %>%
  filter(Phase %in% initial_stage)

usefulness_sens$Phase <- factor(usefulness_sens$Phase, levels = c("stage3", "stage2"))
usefulness_sens$Label <- as.factor(usefulness_sens$Label)
usefulness_sens$Task <- as.factor(usefulness_sens$Task)

model <- lmer(
  Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours +
    (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = usefulness_sens
)

cat("===LMM MODEL SUM===\n")
model_summary <- summary(model)$coefficients
print(model_summary)

anova_results <- anova(model)
cat("\n===ANOVA===\n")
print(anova_results)

eta_sq <- effectsize::eta_squared(model, partial = TRUE)
cat("\n===ETA SQUARED===\n")
print(eta_sq)

posthoc_stage <- emmeans(model, pairwise ~ Phase)
cat("\n===POST HOC STAGE===\n")
print(posthoc_stage$contrasts)

posthoc_label <- emmeans(model, pairwise ~ Label)
cat("\n===POST HOC LABEL===\n")
print(posthoc_label$contrasts)

posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
cat("\n===POST HOC PHASE X LABEL===\n")
print(posthoc_stage_label$contrasts)

posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
cat("\n===POST HOC LABEL X PHASE===\n")
print(posthoc_label_stage$contrasts)
```

### Attitude Change Over Time (Pre, Post)
```{r attitude-change-over-time-pre-post-1}
# Initial-session attitude change = Pre -> Post (follow-up phase excluded).
measures <- c("AI_Trust", "AI_Usefulness", "AI_Affect", "Behavioral_Intention")

change_stats <- list()
anova_results <- list()
eta_squared_results <- list()
posthoc_results_stage <- list()
posthoc_results_PL <- list()
posthoc_results_LP <- list()

for (msr in measures) {
  d_sub <- df_long %>%
    filter(measure == msr, Phase %in% c("Pre", "Post")) %>%
    dplyr::select(-Task)

  d_wide <- d_sub %>%
    dplyr::select(ID, Label, Phase, Value) %>%
    pivot_wider(names_from = Phase, values_from = Value) %>%
    mutate(change = Post - Pre)

  stat_tab <- d_wide %>%
    group_by(Label) %>%
    summarise(
      MeanChange = round(mean(change, na.rm = TRUE), 2),
      SD = round(sd(change, na.rm = TRUE), 2),
      N = n()
    ) %>%
    mutate(Measure = msr, .before = 1)

  change_stats[[msr]] <- stat_tab

  d_mod <- d_sub %>%
    filter(!is.na(Value))

  if (nrow(d_mod) > 0) {
    d_mod$Phase <- factor(d_mod$Phase, levels = c("Post", "Pre"))
    d_mod$Phase <- relevel(as.factor(d_mod$Phase), ref = "Post")

    model <- lmer(
      Value ~ Phase * Label + Age + Gender + Field + Used_LLM_Hours + (1 | ID),
      data = d_mod
    )

    cat("\n")
    print(msr)

    aov_tab <- anova(model)
    cat("\n===ANOVA===\n")
    print(aov_tab)

    eta <- effectsize::eta_squared(model, partial = TRUE)
    cat("\n===Eta Squared===\n")
    print(eta)

    posthoc_stage <- emmeans(model, pairwise ~ Phase)
    cat("\n===Post Hoc Phase===\n")
    print(posthoc_stage)

    posthoc_PL <- emmeans(model, pairwise ~ Phase | Label)
    posthoc_LP <- emmeans(model, pairwise ~ Label | Phase)

    anova_results[[msr]] <- as.data.frame(aov_tab) %>%
      tibble::rownames_to_column("Effect") %>%
      mutate(Measure = msr, .before = 1)

    eta_squared_results[[msr]] <- as.data.frame(eta) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_stage[[msr]] <- as.data.frame(posthoc_stage$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_PL[[msr]] <- as.data.frame(posthoc_PL$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_LP[[msr]] <- as.data.frame(posthoc_LP$contrasts) %>%
      mutate(Measure = msr, .before = 1)
  }
}
```

## Reproducibility

```{r session-info}
sessionInfo()
```
