---
title: "Study 2 — Follow-Up (Completer) Sample: Demographic Characteristics"
author: "Siyuan Huang"
date: "2025-07-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

set.seed(42)
```

# Overview

This document reports the demographic composition of the Study 2 **follow-up
completer** sample and tests whether the three labelling conditions (AI,
AI + Human, Human) were balanced on background characteristics.

The analysis sample comprises participants who completed **both** the
initial and the follow-up session, after excluding participants with a
Stage-1 baseline (task 0) accuracy of `>= 0.90` (a ceiling-effect screen
applied identically across all Study 2 follow-up analyses). For each
demographic variable we report the per-condition distribution and a
chi-square test of independence against condition.

## Packages

```{r packages}
library(readxl)
library(janitor)
library(dplyr)
library(tidyr)
library(openxlsx)
```

## Load and Filter Data

The ceiling-effect screen (`stage1_task0_accuracy < 0.9`) defines the
analysis sample; `Label` is ordered AI < AI + Human < Human throughout.

```{r load-data}
df <- read_excel("data/Study_2_Followup_Data.xlsx")

df <- df %>%
  filter(stage1_task0_accuracy < 0.9) %>%
  mutate(Label = factor(Label, levels = c("AI", "AI Human", "Human")))
```

## Descriptive Distributions by Condition

Each table gives the count and within-condition percentage for one
demographic variable.

### Condition (Label) Distribution

```{r dist-label}
label_table <- df %>%
  group_by(Label) %>%
  summarise(n = n(), .groups = "drop") %>%
  mutate(percent = round(100 * n / sum(n), 1))

label_table
```

### Gender

```{r dist-gender}
gender_table <- df %>%
  group_by(Label, Gender) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

gender_table
```

### Age

```{r dist-age}
age_table <- df %>%
  group_by(Label, Age) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

age_table
```

### Identity

```{r dist-identity}
identity_table <- df %>%
  group_by(Label, Identity) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

identity_table
```

### Field of Study

```{r dist-field}
field_table <- df %>%
  group_by(Label, Field) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

field_table
```

### Statistics Background

```{r dist-stats-background}
statsbackground_table <- df %>%
  group_by(Label, Stats_Background) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

statsbackground_table
```

### LLM Use Frequency

```{r dist-llm-frequency}
llm_freq_table <- df %>%
  group_by(Label, Used_LLM_Frequency) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

llm_freq_table
```

### LLM Use Hours

```{r dist-llm-hours}
llm_hours_table <- df %>%
  group_by(Label, Used_LLM_Hours) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(Label) %>%
  mutate(percent = round(100 * n / sum(n), 1)) %>%
  ungroup()

llm_hours_table
```

## Chi-Square Tests of Independence

Each test evaluates whether the demographic variable is independent of the
labelling condition; a non-significant result indicates the conditions were
balanced on that characteristic.

```{r chi-square-tests}
label_chi      <- chisq.test(table(df$Label))
gender_chi     <- chisq.test(table(df$Label, df$Gender))
age_chi        <- chisq.test(table(df$Label, df$Age))
identity_chi   <- chisq.test(table(df$Label, df$Identity))
field_chi      <- chisq.test(table(df$Label, df$Field))
background_chi <- chisq.test(table(df$Label, df$Stats_Background))
frequency_chi  <- chisq.test(table(df$Label, df$Used_LLM_Frequency))
hours_chi      <- chisq.test(table(df$Label, df$Used_LLM_Hours))

label_chi
gender_chi
age_chi
identity_chi
field_chi
background_chi
frequency_chi
hours_chi
```

## Export Results

```{r export-results}
test_results <- data.frame(
  Variable = c(
    "Label", "Gender", "Age", "Identity", "Field",
    "Stats_Background", "Used_Frequency", "Used_Hours"
  ),
  Test = rep("Chi-square", 8),
  Statistic = c(
    as.numeric(label_chi$statistic),
    as.numeric(gender_chi$statistic),
    as.numeric(age_chi$statistic),
    as.numeric(identity_chi$statistic),
    as.numeric(field_chi$statistic),
    as.numeric(background_chi$statistic),
    as.numeric(frequency_chi$statistic),
    as.numeric(hours_chi$statistic)
  ),
  p_value = c(
    label_chi$p.value,
    gender_chi$p.value,
    age_chi$p.value,
    identity_chi$p.value,
    field_chi$p.value,
    background_chi$p.value,
    frequency_chi$p.value,
    hours_chi$p.value
  )
)

all_tables <- list(
  Label_Distribution    = label_table,
  Gender_Distribution   = gender_table,
  Age_Distribution      = age_table,
  Identity_Distribution = identity_table,
  Field_Distribution    = field_table,
  Stats_Background      = statsbackground_table,
  LLM_Use_Frequency     = llm_freq_table,
  LLM_Use_Hours         = llm_hours_table,
  Statistical_Tests     = test_results
)

write.xlsx(
  all_tables,
  file = "results/Follow-Up Activity/Baseline/Demographic_Results_Followup_Only.xlsx"
)
```

## Reproducibility

```{r session-info}
sessionInfo()
```
