---
title: "Study 2 — Early- vs. Late-Corrected Items at Follow-Up"
author: "Siyuan Huang"
date: "2025-08-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

set.seed(42)
```

# Study 2 — Early- vs. Late-Corrected Items at Follow-Up

This is a standalone item-level analysis asking whether items a
participant first answered incorrectly at Stage 1 and then corrected
**early** (by Stage 2) versus **late** (only by Stage 3) differ in their
probability of remaining correct at follow-up.

The **main analysis** is a logistic mixed-effects model of follow-up
correctness that **controls for item difficulty** (plus participant
baseline accuracy and task), with crossed participant and item random
effects. The supplementary and sensitivity analyses that follow probe its
robustness (model without the difficulty covariate, label main effects,
the difficulty composition of the early/late groups, the early-corrected
subset, manipulation passers, and the perceived label).

The sample is the follow-up responders (≥ 1 follow-up answer). It is **not**
subject to the Stage-1 ceiling screen used elsewhere, because this analysis
is item-conditional: an item enters only if it was wrong at Stage 1,
corrected by Stage 2 or 3, and answered at follow-up.

## Packages
```{r packages}
library(readxl)
library(dplyr)
library(tidyr)
library(stringr)
library(lme4)
library(broom.mixed)
library(emmeans)
```

## Load Data and Preprocessing

The raw item-level data are loaded and restricted to follow-up
responders. Item responses are scored against the ground truth, reshaped
to long format, and the correction-timing analysis dataset is built by
keeping items that were wrong at Stage 1, subsequently corrected (by
Stage 2 or Stage 3), and answered at follow-up. `CorrectionTiming`
classifies each such item as **Early** (corrected by Stage 2) or
**Late** (corrected only by Stage 3).

```{r load-data}
dat <- readxl::read_excel("data/correction_raw_data.xlsx") %>%
  mutate(ID = factor(ID))
```

```{r build-analysis}
items <- c(paste0("t1_q", 1:6), paste0("t2_q", 1:5), paste0("t3_q", 1:6))

truth <- c(rep(FALSE, 6), rep(FALSE, 5), FALSE, TRUE, TRUE, TRUE, FALSE, TRUE)
names(truth) <- items

s1 <- paste0("stage1_", items)
s2 <- paste0("stage2_", items)
s3 <- paste0("stage3_", items)
fu <- paste0("follow_up_", items)

# Filter Participants With Follow-up Responses
dat <- dat %>%
  filter(rowSums(across(all_of(fu), ~ !is.na(.))) > 0)

# Coerce Answer Types
dat <- dat %>%
  mutate(
    across(all_of(fu), ~ ifelse(is.na(.), NA, . == 1)),
    across(all_of(c(s1, s2, s3)), as.logical)
  )

# Long Format, Attach Truth, Compute Correctness
long <- dat %>%
  pivot_longer(
    cols = matches("^(stage1|stage2|stage3|follow_up)_t[123]_q\\d+$"),
    names_to = c("Stage", "Item"),
    names_pattern = "^(stage1|stage2|stage3|follow_up)_(t\\d_q\\d+)$",
    values_to = "Ans"
  ) %>%
  mutate(
    Item = factor(Item, levels = items),
    Task = factor(sub("_q\\d+$", "", as.character(Item)), levels = c("t1", "t2", "t3"))
  )

truth_df <- tibble(Item = factor(items, levels = items), Truth = truth)

wide <- long %>%
  left_join(truth_df, by = "Item") %>%
  pivot_wider(names_from = Stage, values_from = Ans) %>%
  mutate(
    S1c = stage1 == Truth,
    S2c = stage2 == Truth,
    S3c = stage3 == Truth,
    FUc = if_else(is.na(follow_up), NA, follow_up == Truth)
  )

# Build Analysis Dataset: Early vs Late Correction
# Items wrong at Stage 1, eventually corrected, and answered at follow-up.
# Among these:
#   Early = corrected by Stage 2
#   Late  = not by Stage 2 but corrected by Stage 3
analysis <- wide %>%
  filter(S1c == FALSE, (S2c | S3c), !is.na(FUc)) %>%
  mutate(
    CorrectionTiming = factor(
      case_when(
        S2c == TRUE ~ "Early",
        S2c == FALSE & S3c == TRUE ~ "Late"
      ),
      levels = c("Early", "Late")
    ),
    Item = factor(Item),
    ID = factor(ID)
  )
```

## Item-Difficulty Proxy

The main model controls for item difficulty. Difficulty is each item's
Stage-1 accuracy across the **full sample** (pre-treatment, item-level).
The full sample (including those who answered correctly) must be used,
otherwise post-treatment selection leaks back into the difficulty measure
itself. Larger `difficulty_c` = easier item.

```{r item-difficulty}
item_difficulty <- wide %>%
  filter(!is.na(S1c)) %>%
  group_by(Item) %>%
  summarise(p_correct_s1 = mean(S1c), .groups = "drop") %>%
  mutate(difficulty_c = as.numeric(scale(p_correct_s1, center = TRUE, scale = FALSE)))
# larger difficulty_c = easier item

print(item_difficulty)
```

# Main Analysis: Follow-Up Model Controlling for Difficulty

This is the primary analysis. Among items answered incorrectly at Stage 1
and subsequently corrected, we distinguish **early-corrected** items
(corrected by Stage 2, under the explanation alone) from **late-corrected**
items (corrected only after Stage 3 answer disclosure), and model follow-up
correctness with a logistic mixed-effects model that controls for item
difficulty, participant baseline accuracy (`overall_accuracy_stage1`), and
task, with crossed participant and item random effects. The focal term is
the `CorrectionTiming × Label` interaction.

Because this decomposition conditions on a post-treatment outcome (whether
and when an item was corrected), it is treated as exploratory and
descriptive; the supplementary and sensitivity analyses below probe its
robustness.

### Follow-Up Accuracy by Early/Late Correction
```{r main-descriptives}
desc <- analysis %>%
  group_by(Label, CorrectionTiming) %>%
  summarise(
    n = n(),
    mean_FU_correct = mean(FUc),
    .groups = "drop"
  ) %>%
  arrange(Label, CorrectionTiming)

print(desc)
```

### Difficulty-Controlled Logistic Mixed Model
```{r main-data}
# Attach the item-difficulty proxy to the early/late analysis dataset.
analysis_diff <- analysis %>%
  left_join(item_difficulty, by = "Item")
```

```{r main-model}
fit_main <- glmer(
  FUc ~ CorrectionTiming * Label + Task + difficulty_c + overall_accuracy_stage1 + (1 | ID) + (1 | Item),
  data = analysis_diff,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(fit_main)
```

### Odds Ratios (Fixed Effects)
```{r main-or}
or_tab <- broom.mixed::tidy(
  fit_main,
  effects = "fixed",
  conf.int = TRUE,
  exponentiate = TRUE
)

print(or_tab)
```

### Inference and Post-hoc
```{r main-inference}
aov <- car::Anova(fit_main, type = 3)
aov

parameters::model_parameters(fit_main, exponentiate = TRUE)

emmeans(fit_main, pairwise ~ CorrectionTiming)
```

#### Condition-Specific Contrasts
```{r main-contrasts-by-label}
emmeans::emmeans(fit_main, pairwise ~ CorrectionTiming | Label)$contrasts
emmeans::emmeans(fit_main, pairwise ~ CorrectionTiming | Label, type = "response")$contrasts
```

# Supplementary & Sensitivity Analyses

The analyses below probe the robustness of the main result: the same model
without the difficulty covariate (S1); label main effects among corrected
items (S2); whether the early/late groups differ in difficulty composition
(S3); the early-corrected subset on its own (S4–S5); and two manipulation
robustness checks (S6–S7).

## S1 — Without Difficulty Covariate

The main model, refit **without** the item-difficulty covariate (the
earlier specification). Comparing S1 with the main model shows how
controlling for difficulty changes the early/late pattern.

```{r s1-nodiff-model}
fit_nodiff <- glmer(
  FUc ~ CorrectionTiming * Label + Task + overall_accuracy_stage1 + (1 | ID) + (1 | Item),
  data = analysis,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(fit_nodiff)
```

```{r s1-nodiff-or}
broom.mixed::tidy(fit_nodiff, effects = "fixed", conf.int = TRUE, exponentiate = TRUE)
```

```{r s1-nodiff-inference}
car::Anova(fit_nodiff, type = 3)

parameters::model_parameters(fit_nodiff, exponentiate = TRUE)

emmeans(fit_nodiff, pairwise ~ CorrectionTiming)
emmeans::emmeans(fit_nodiff, pairwise ~ CorrectionTiming | Label, type = "response")$contrasts
```

## S2 — Label Main Effect on Corrected Items

Conditioning on items wrong at Stage 1 and subsequently corrected (by
Stage 2 or Stage 3), collapsing early/late, test the **label** main effect
on follow-up correctness. Reported with and without the item-difficulty
covariate.

```{r s2-data}
analysis_corrected <- wide %>%
  filter(S1c == FALSE, (S2c | S3c), !is.na(FUc)) %>%
  mutate(
    Item = factor(Item),
    ID = factor(ID)
  )
```

### S2a — Without Difficulty
```{r s2-model-nodiff}
fit_label <- glmer(
  FUc ~ Label + Task + overall_accuracy_stage1 + (1 | ID) + (1 | Item),
  data = analysis_corrected,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(fit_label)

car::Anova(fit_label, type = 3)

parameters::model_parameters(fit_label, exponentiate = TRUE)

emmeans(fit_label, pairwise ~ Label)
```

### S2b — Controlling for Difficulty
```{r s2-model-diff}
analysis_corrected_diff <- analysis_corrected %>%
  left_join(item_difficulty, by = "Item")

fit_label_diff <- glmer(
  FUc ~ Label + Task + overall_accuracy_stage1 + difficulty_c + (1 | ID) + (1 | Item),
  data = analysis_corrected_diff,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(fit_label_diff)

car::Anova(fit_label_diff, type = 3)

parameters::model_parameters(fit_label_diff, exponentiate = TRUE)

emmeans(fit_label_diff, pairwise ~ Label)
```

## S3 — Selection Test: Difficulty Composition of Early vs. Late

Here the outcome is *whether an item is corrected early or late* (not
accuracy), predicted from pre-treatment item difficulty. If difficulty
predicts the grouping, and does so differently by label, the early/late
groups differ in difficulty composition in a label-induced way — motivating
the difficulty control in the main model.

Variable mapping (against the original pseudocode): `d` → `wide`,
`item` → `Item`, `correct_s1` → `S1c`, `early_correct` → `EarlyCorrected`,
`label` → `Label`, `participant` → `ID`.

### S3a — Early/Late Analysis Subset
Items wrong at Stage 1 and eventually corrected (where `EarlyCorrected`
is defined), with the difficulty proxy attached.

```{r s3-corrected-subset}
d_corrected <- wide %>%
  filter(S1c == FALSE, (S2c | S3c)) %>%
  mutate(
    EarlyCorrected = as.integer(S2c == TRUE),
    Item = factor(Item),
    ID = factor(ID)
  ) %>%
  left_join(item_difficulty, by = "Item")
```

### S3b — Difficulty Main Effect
Are easier items more likely to fall into the early group?

```{r s3-difficulty-main}
sel1 <- glmer(
  EarlyCorrected ~ difficulty_c + (1 | ID) + (1 | Item),
  data = d_corrected, family = binomial,
  control = glmerControl(optimizer = "bobyqa")
)
summary(sel1)
```

### S3c — Difficulty × Label
Does the degree to which items are sorted into "early" by difficulty
differ across labels? This directly tests whether items early-correctable
under one label differ systematically from those early-correctable under
another.

```{r s3-difficulty-label}
sel2 <- glmer(
  EarlyCorrected ~ difficulty_c * Label + (1 | ID) + (1 | Item),
  data = d_corrected, family = binomial,
  control = glmerControl(optimizer = "bobyqa")
)
summary(sel2)

car::Anova(sel2, type = 3)
emmeans(sel2, pairwise ~ Label)

anova(sel1, sel2)
```

### S3d — Difficulty as the Outcome (Linear Model)
Cross-check by modelling difficulty itself as the outcome of
early-correction status and label.

```{r s3-difficulty-lm}
sel3 <- lmer(
  difficulty_c ~ EarlyCorrected * Label + (1 | ID),
  data = d_corrected
)
summary(sel3)

car::Anova(sel3, type = 3)
emmeans(sel3, pairwise ~ EarlyCorrected | Label)
```

### S3e — Descriptive Balance Table
A descriptive balance table of difficulty by label and correction timing,
included for completeness.

```{r s3-balance-table}
d_corrected %>%
  group_by(Label, EarlyCorrected) %>%
  summarise(
    n = n(),
    mean_difficulty = mean(difficulty_c),
    sd_difficulty = sd(difficulty_c),
    .groups = "drop"
  ) %>%
  arrange(Label, desc(EarlyCorrected)) %>%
  print(n = 50)
```

## S4 — Early-Corrected Subset Only

Keep only items wrong at Stage 1 and correct at Stage 2 (i.e. Early
Corrected). Within this "early-corrected" subset, test whether follow-up
accuracy differs across labels.

### S4a — Build the Early-Corrected Subset
```{r s4-early-subset}
analysis_early <- wide %>%
  filter(S1c == FALSE, S2c == TRUE, !is.na(FUc)) %>%
  mutate(
    Item = factor(Item),
    ID = factor(ID)
  )
```

### S4b — Descriptives: Follow-Up Accuracy by Label
```{r s4-early-accuracy-by-label}
analysis_early %>%
  group_by(Label) %>%
  summarise(
    n = n(),
    mean_FU_correct = mean(FUc),
    .groups = "drop"
  ) %>%
  arrange(Label) %>%
  print()
```

### S4b-2 — Participant Counts by Label
```{r s4-early-participant-counts}
analysis_early %>%
  group_by(Label) %>%
  summarise(
    n_participants = n_distinct(ID),
    n_obs = n(),
    .groups = "drop"
  ) %>%
  arrange(Label) %>%
  print()
```

### S4c — Logistic Mixed Model
```{r s4-early-model}
fit_early <- glmer(
  FUc ~ Label + Task + overall_accuracy_stage1 + (1 | ID) + (1 | Item),
  data = analysis_early,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(fit_early)
```

### S4d — Odds Ratios (Fixed Effects)
```{r s4-early-or}
or_tab_early <- broom.mixed::tidy(
  fit_early,
  effects = "fixed",
  conf.int = TRUE,
  exponentiate = TRUE
)

print(or_tab_early)
```

### S4e — Inference and Post-hoc
```{r s4-early-inference}
aov_early <- car::Anova(fit_early, type = 3)
aov_early

parameters::model_parameters(fit_early, exponentiate = TRUE)

emmeans(fit_early, pairwise ~ Label)
emmeans(fit_early, pairwise ~ Label, type = "response")$contrasts
```

## S5 — Early-Corrected Subset Only + Item Difficulty

The same subset as S4 (wrong at Stage 1, correct at Stage 2), adding the
item-level difficulty proxy `difficulty_c` (Stage-1 full-sample accuracy,
centered; larger = easier). The goal is to see whether the label
difference in follow-up accuracy changes once item difficulty is
controlled for.

### S5a — Attach the Difficulty Variable
```{r s5-early-diff-attach}
analysis_early_diff <- analysis_early %>%
  left_join(item_difficulty, by = "Item")
```

### S5b — Logistic Mixed Model
```{r s5-early-diff-model}
fit_early_diff <- glmer(
  FUc ~ Label * difficulty_c + Task + overall_accuracy_stage1 + (1 | ID) + (1 | Item),
  data = analysis_early_diff,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(fit_early_diff)
```

### S5c — Odds Ratios (Fixed Effects)
```{r s5-early-diff-or}
or_tab_early_diff <- broom.mixed::tidy(
  fit_early_diff,
  effects = "fixed",
  conf.int = TRUE,
  exponentiate = TRUE
)

print(or_tab_early_diff)
```

### S5d — Inference and Post-hoc
```{r s5-early-diff-inference}
aov_early_diff <- car::Anova(fit_early_diff, type = 3)
aov_early_diff

parameters::model_parameters(fit_early_diff, exponentiate = TRUE)

emmeans(fit_early_diff, pairwise ~ Label)
emmeans(fit_early_diff, pairwise ~ Label, type = "response")$contrasts
```

## S6 — Manipulation Passers Only

As a check against participants for whom the manipulation may have failed,
the main model is refit on those who **passed the source-recall check**
(correctly recalled their assigned label; `Recalled_Label` from the main
Study 2 data, recoded to match). Two models are reported, identical to the
main structure and differing only in whether `difficulty_c` is included.

### S6a — Identify Passers and Restrict the Sample
```{r s6-passers-build}
recall <- readxl::read_excel("data/manipulation_recall.xlsx") %>%
  mutate(
    ID = as.character(ID),
    Recalled_Label = dplyr::recode(Recalled_Label, "AI + Human" = "AI Human")
  )

passer_ids <- analysis %>%
  distinct(ID, Label) %>%
  mutate(ID = as.character(ID)) %>%
  left_join(recall, by = "ID") %>%
  filter(as.character(Label) == as.character(Recalled_Label)) %>%
  pull(ID)

analysis_pass <- analysis %>%
  filter(as.character(ID) %in% passer_ids) %>%
  droplevels()

cat("Passers:", length(passer_ids),
    "of", n_distinct(analysis$ID), "participants;",
    nrow(analysis_pass), "of", nrow(analysis), "item observations\n")
```

### S6b — Main Structure (No Difficulty Covariate)
```{r s6-passers-model-nodiff}
fit_pass <- glmer(
  FUc ~ CorrectionTiming * Label + Task + overall_accuracy_stage1 + (1 | ID) + (1 | Item),
  data = analysis_pass,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(fit_pass)

broom.mixed::tidy(fit_pass, effects = "fixed", conf.int = TRUE, exponentiate = TRUE)

car::Anova(fit_pass, type = 3)

emmeans(fit_pass, pairwise ~ CorrectionTiming | Label, type = "response")$contrasts
```

### S6c — Main Structure + Item Difficulty
```{r s6-passers-model-diff}
analysis_pass_diff <- analysis_pass %>%
  left_join(item_difficulty, by = "Item")

fit_pass_diff <- glmer(
  FUc ~ CorrectionTiming * Label + Task + difficulty_c + overall_accuracy_stage1 + (1 | ID),
  data = analysis_pass_diff,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(fit_pass_diff)

broom.mixed::tidy(fit_pass_diff, effects = "fixed", conf.int = TRUE, exponentiate = TRUE)

car::Anova(fit_pass_diff, type = 3)

emmeans(fit_pass_diff, pairwise ~ CorrectionTiming | Label, type = "response")$contrasts
```

## S7 — Perceived Label (As-Recalled Condition)

Complementary to the passers-only check, this keeps the **full sample** but
replaces the assigned `Label` with the **perceived label** each participant
recalled (`Recalled_Label`) — the more proximal cause if the manipulation
operates through what participants *believe* they received. Passers enter
under their assigned label, non-passers under the one they believed. Two
models are reported, differing only in whether `difficulty_c` is included.

### S7a — Attach Perceived Label
```{r s7-perceived-build}
perceived_lk <- recall %>%
  transmute(ID = as.character(ID),
            PerceivedLabel = factor(Recalled_Label, levels = c("AI", "AI Human", "Human")))

analysis_perc <- analysis %>%
  mutate(ID = as.character(ID)) %>%
  left_join(perceived_lk, by = "ID") %>%
  filter(!is.na(PerceivedLabel)) %>%
  mutate(ID = factor(ID)) %>%
  droplevels()

cat("Participants with a recalled label:", n_distinct(analysis_perc$ID),
    "of", n_distinct(analysis$ID), ";",
    nrow(analysis_perc), "of", nrow(analysis), "item observations\n")
```

### S7b — Main Structure (No Difficulty Covariate)
```{r s7-perceived-model-nodiff}
fit_perc <- glmer(
  FUc ~ CorrectionTiming * PerceivedLabel + Task + overall_accuracy_stage1 + (1 | ID) + (1 | Item),
  data = analysis_perc,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(fit_perc)

broom.mixed::tidy(fit_perc, effects = "fixed", conf.int = TRUE, exponentiate = TRUE)

car::Anova(fit_perc, type = 3)

emmeans(fit_perc, pairwise ~ CorrectionTiming | PerceivedLabel, type = "response")$contrasts
```

### S7c — Main Structure + Item Difficulty
```{r s7-perceived-model-diff}
analysis_perc_diff <- analysis_perc %>%
  left_join(item_difficulty, by = "Item")

fit_perc_diff <- glmer(
  FUc ~ CorrectionTiming * PerceivedLabel + Task + difficulty_c + overall_accuracy_stage1 + (1 | ID) + (1 | Item),
  data = analysis_perc_diff,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(fit_perc_diff)

broom.mixed::tidy(fit_perc_diff, effects = "fixed", conf.int = TRUE, exponentiate = TRUE)

car::Anova(fit_perc_diff, type = 3)

emmeans(fit_perc_diff, pairwise ~ CorrectionTiming | PerceivedLabel, type = "response")$contrasts
```

## Reproducibility

```{r session-info}
sessionInfo()
```
