---
title: "Study 2 Results"
author: "Spike Huang"
date: "2025-07-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Study 2 Results
## Load Packages
```{r packages, message=FALSE, warning=FALSE}
library(broom)
library(car)
library(DescTools)
library(dplyr)
library(DT)
library(effectsize)
library(emmeans)
library(ggplot2)
library(janitor)
library(lme4)
library(lmerTest)
library(lsr)
library(MASS)
library(openxlsx)
library(ordinal)
library(performance)
library(readxl)
library(stringr)
library(tidyr)
library(report)
library(interactions)
library(forcats)
library(tibble)
```

## Data Processing
### Load Data
```{r, message=FALSE, warning=FALSE}
df <- read_excel("data/Study_2_Main_Results_Data.xlsx")
head(df)

# Set Label Factor
df <- df %>%
  mutate(Label = factor(Label, levels = c("AI", "AI Human", "Human")))
```

``` {r, message=FALSE, warning=FALSE}
# Create a named vector to define the new column names
# The format is: "new_name" = "old_name"
rename_vars <- c(
  "Pre_GLAT_Objective_AI_Literacy",
  "Pre_AILS_CCS_Subjective_AI_Literacy",
  "Pre_AI_Trust",
  "Pre_AI_Usefulness",
  "Pre_AI_Affect",
  "Pre_AI_Self_Efficacy",
  "Pre_Behavioral_Intention",
  "stage1_task0_accuracy",
  "stage1_task1_accuracy",
  "stage1_task2_accuracy",
  "stage1_task3_accuracy",
  "stage2_task0_accuracy",
  "stage2_task1_accuracy",
  "stage2_task2_accuracy",
  "stage2_task3_accuracy",
  "stage3_task0_accuracy",
  "stage3_task1_accuracy",
  "stage3_task2_accuracy",
  "stage3_task3_accuracy",
  "stage1_task0_confidence",
  "stage1_task1_confidence",
  "stage1_task2_confidence",
  "stage1_task3_confidence",
  "stage2_task0_confidence",
  "stage2_task1_confidence",
  "stage2_task2_confidence",
  "stage2_task3_confidence",
  "stage3_task0_confidence",
  "stage3_task1_confidence",
  "stage3_task2_confidence",
  "stage3_task3_confidence",
  "stage2_task0_willing",
  "stage2_task1_willing",
  "stage2_task2_willing",
  "stage2_task3_willing",
  "stage3_task0_willing",
  "stage3_task1_willing",
  "stage3_task2_willing",
  "stage3_task3_willing",
  "stage2_task0_useful",
  "stage2_task1_useful",
  "stage2_task2_useful",
  "stage2_task3_useful",
  "stage3_task0_useful",
  "stage3_task1_useful",
  "stage3_task2_useful",
  "stage3_task3_useful",
  "Post_AI_Trust",
  "Post_AI_Usefulness",
  "Post_AI_Affect",
  "Post_Behavioral_Intention"
)

# Convert the 'Label' column into a factor data type
df$Label <- factor(df$Label, levels = c("AI", "AI Human", "Human"))
```

### Stage 1 Task 0 Accuracy Distribution
``` {r, message=FALSE, warning=FALSE}
ggplot(df, aes(x = stage1_task0_accuracy)) +
  geom_histogram(binwidth = 0.05, fill = "skyblue", color = "black") +
  stat_bin(
    binwidth = 0.05,
    geom = "text",
    aes(label = ..count..),
    vjust = -0.3
  ) +
  scale_x_continuous(
    breaks = seq(0, 1, by = 0.05),
    labels = sprintf("%.2f", seq(0, 1, by = 0.05))
  ) +
  labs(
    title = "Distribution of stage1_task0_accuracy",
    x = "stage1_task0_accuracy",
    y = "Frequency"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Filter Stage 1 Task 0 Accuracy
``` {r, message=FALSE, warning=FALSE}
df_over90 <- df %>% filter(stage1_task0_accuracy >= 0.9)

sum(df$stage1_task0_accuracy >= 0.9)

df <- df %>% filter(stage1_task0_accuracy < 0.9)
```

### Recode Background Variables
``` {r, message=FALSE, warning=FALSE}
df <- df %>%
  mutate(
    Stats_Background = cut(
      as.numeric(as.character(Stats_Background)),
      breaks = c(1, 3, 5, 8),
      labels = c("Low", "Medium", "High"),
      right = TRUE,
      include.lowest = TRUE
    ),
    Used_LLM_Frequency = forcats::fct_collapse(
      as.character(Used_LLM_Frequency),
      Rarely = c("Never", "Less than once a month", "1–3 times per month"),
      Often = c("Weekly", "Daily")
    ),
    Used_LLM_Hours = forcats::fct_collapse(
      as.character(Used_LLM_Hours),
      None = "0",
      Low = c("1–5", "6–10"),
      High = c("11–20", ">20")
    )
  )
```

### Convert to Long Format
``` {r, message=FALSE, warning=FALSE}
cols_to_long <- grep("^(Pre|Post|stage\\d+)_", colnames(df), value = TRUE)

df_long <- df %>%
  pivot_longer(
    cols = all_of(cols_to_long),
    names_to = "fullvar",
    values_to = "Value"
  ) %>%
  mutate(
    Phase = str_extract(fullvar, "^(Pre|Post|stage\\d+)"),
    tmp = str_remove(fullvar, "^(Pre|Post|stage\\d+)_"),
    task = ifelse(str_detect(tmp, "^task\\d+"), str_extract(tmp, "^task\\d+"), NA),
    measure = ifelse(!is.na(task), str_remove(tmp, "^task\\d+_"), tmp),
    tmp = NULL,
    fullvar = NULL
  )

head(df_long)
```

## Baseline Summary by Label
``` {r, message=FALSE, warning=FALSE}
varnames <- c(
  "Pre_GLAT_Objective_AI_Literacy",
  "Pre_AILS_CCS_Subjective_AI_Literacy",
  "Pre_AI_Trust",
  "Pre_AI_Usefulness",
  "Pre_AI_Affect",
  "Pre_AI_Self_Efficacy",
  "Pre_Behavioral_Intention"
)

label_summary_table <- bind_rows(lapply(varnames, function(v) {
  df %>%
    group_by(Label) %>%
    summarise(
      Mean = round(mean(.data[[v]], na.rm = TRUE), 2),
      SD = round(sd(.data[[v]], na.rm = TRUE), 2),
      n = sum(!is.na(.data[[v]])),
      .groups = "drop"
    ) %>%
    mutate(Variable = v) %>%
    relocate(Variable)
}))

label_summary_table
```

### Baseline ANOVA by Label
``` {r, message=FALSE, warning=FALSE}
anova_results_table <- bind_rows(lapply(varnames, function(v) {
  aov_res <- summary(aov(df[[v]] ~ df$Label))
  data.frame(
    Variable = v,
    F_value = round(aov_res[[1]][["F value"]][1], 2),
    p_value = round(aov_res[[1]][["Pr(>F)"]][1], 4)
  )
}))

anova_results_table
```

### Export Baseline Results
``` {r, message=FALSE, warning=FALSE}
# all_results <- list(
# Label_Summary = label_summary_table,
# ANOVA_Results = anova_results_table
# )
#
# write.xlsx(
# all_results,
# file = "results/Baseline demographic_results/Baseline_Charateristics_By_Label.xlsx"
# )
```

## H1
### Data Filter
``` {r, message=FALSE, warning=FALSE}
performance_long <- df_long %>%
  rename(
    Task = task,
    Measure = measure
  ) %>%
  filter(
    Measure == "accuracy",
    Task != "task0"
  )

head(performance_long)
```

### Descriptive Summary
``` {r, message=FALSE, warning=FALSE}
stage_summary <- performance_long %>%
  group_by(Phase, Label) %>%
  summarise(
    Mean = round(mean(Value, na.rm = TRUE), 2),
    SD = round(sd(Value, na.rm = TRUE), 2),
    N = n(),
    .groups = "drop"
  )

stage_summary
```

### Mixed Model (Without Task)
``` {r, message=FALSE, warning=FALSE}
performance_long <- performance_long %>%
  mutate(
    Label = factor(Label),
    Phase = factor(Phase, levels = c("stage3", "stage2", "stage1")),
    Task = factor(Task),
    Stats_Background = factor(Stats_Background)
  )

model <- lmer(
  Value ~ Phase * Label + (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = performance_long
)

model_summary <- summary(model)$coefficients
anova_results <- anova(model)
eta_sq <- effectsize::eta_squared(model, partial = TRUE)

model_summary
anova_results
eta_sq
```

#### Post-hoc Comparisons
``` {r, message=FALSE, warning=FALSE}
posthoc_stage <- emmeans(model, pairwise ~ Phase)
posthoc_label <- emmeans(model, pairwise ~ Label)
posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)

cat("===Stage===\n")
posthoc_stage$contrasts
cat("\n===Label===\n")
posthoc_label$contrasts
cat("\n===Stage:Labe===\n")
posthoc_stage_label$contrasts
# summary(posthoc_stage_label$contrasts, infer = TRUE)
cat("\n===Label:Stage===\n")
posthoc_label_stage$contrasts
```

#### Effect Sizes for Contrasts
``` {r, message=FALSE, warning=FALSE}
eff_size(
  posthoc_stage_label,
  sigma = sigma(model),
  edf = df.residual(model)
)
```

#### Report and Export Results
``` {r, message=FALSE, warning=FALSE}
report(anova_results)

# write.xlsx(
#   list(
#     Model_Summary = as.data.frame(model_summary),
#     ANOVA = as.data.frame(anova_results),
#     Eta_Squared = as.data.frame(eta_sq),
#     Posthoc_Stage = as.data.frame(posthoc_stage$contrasts),
#     Posthoc_Label = as.data.frame(posthoc_label$contrasts),
#     Posthoc_Stage_Label = as.data.frame(posthoc_stage_label$contrasts),
#     Posthoc_Label_Stage = as.data.frame(posthoc_label_stage$contrasts)
#   ),
#   file = "results/H1 learning_progression_results/H1_Performance_Comparison_LMM.xlsx",
#   rowNames = TRUE
# )
```

### Mixed Model (With Task)
``` {r, message=FALSE, warning=FALSE}
model_task <- lmer(
  Value ~ Phase * Label * Task + (1 | ID) + (1 | ID:Task),
  data = performance_long
)

model_task_summary <- summary(model_task)$coefficients
anova_task <- anova(model_task)
eta_task <- effectsize::eta_squared(model_task, partial = TRUE)

model_task_summary
anova_task
eta_task
```

#### Post-hoc With Task
``` {r, message=FALSE, warning=FALSE}
# posthoc_stage_task <- emmeans(model_task, pairwise ~ Phase)
# posthoc_task <- emmeans(model_task, pairwise ~ Task)
# posthoc_label_task <- emmeans(model_task, pairwise ~ Label)
#
# posthoc_stage_by_label_task <- emmeans(model_task, pairwise ~ Phase | Label)
# posthoc_label_by_phase_task <- emmeans(model_task, pairwise ~ Label | Phase)
# posthoc_stage_by_task_task <- emmeans(model_task, pairwise ~ Phase | Task)
# posthoc_3way_task <- emmeans(model_task, pairwise ~ Phase | Task | Label)
#
# posthoc_stage_task$contrasts
# posthoc_task$contrasts
# posthoc_label_task$contrasts
# posthoc_stage_by_label_task$contrasts
# posthoc_label_by_phase_task$contrasts
# posthoc_stage_by_task_task$contrasts
# posthoc_3way_task$contrasts
```

#### Export With Task
``` {r, message=FALSE, warning=FALSE}
# write.xlsx(
#   list(
#     Model_Summary = as.data.frame(model_task_summary),
#     ANOVA = as.data.frame(anova_task),
#     Eta_Squared = as.data.frame(eta_task),
#     Posthoc_Stage = as.data.frame(posthoc_stage_task$contrasts),
#     Posthoc_Task = as.data.frame(posthoc_task$contrasts),
#     Posthoc_Label = as.data.frame(posthoc_label_task$contrasts),
#     Posthoc_Stage_Label = as.data.frame(posthoc_stage_by_label_task$contrasts),
#     Posthoc_Label_Stage = as.data.frame(posthoc_label_by_phase_task$contrasts),
#     Posthoc_Stage_Task = as.data.frame(posthoc_stage_by_task_task$contrasts),
#     Posthoc_3way = as.data.frame(posthoc_3way_task$contrasts)
#   ),
#   file = "results/H1 learning_progression_results/H1_Performance_Comparison_LMM_Task.xlsx",
#   rowNames = TRUE
# )
```

## H2
### Confidence, Willingness, and Usefulness
#### Recode for Modeling
``` {r, message=FALSE, warning=FALSE}
df_long <- df_long %>%
  dplyr::mutate(
    Phase = factor(Phase, levels = c("Post", "stage3", "stage2", "stage1", "Pre")),
    Task = factor(task),
    Label = factor(Label),
    ID = factor(ID)
  ) %>%
  dplyr::select(-task)
```

#### Fit Models
``` {r, message=FALSE, warning=FALSE}
measures <- c("confidence", "willing", "useful")
result_list <- list()

for (var in measures) {
  cat(paste0("\n===", var, "===\n"))

  df_sub <- df_long %>%
    filter(
      measure == var,
      Task != "task0"
    )

  model <- lmer(
    Value ~ Phase * Label + (1 | ID) + (1 | Task) + (1 | ID:Task),
    data = df_sub
  )

  anova_res <- anova(model)
  print(anova_res)
  ANOVA <- as.data.frame(anova_res) %>%
    tibble::rownames_to_column("Variable")

  eta_sq <- effectsize::eta_squared(model, partial = TRUE)
  print(eta_sq)

  coef_tbl <- as.data.frame(summary(model)$coefficients) %>%
    tibble::rownames_to_column("Variable")

  posthoc_stage <- emmeans(model, pairwise ~ Phase)
  posthoc_label <- emmeans(model, pairwise ~ Label)

  posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
  effsize_pl <- eff_size(
    posthoc_stage_label,
    sigma = sigma(model),
    edf = df.residual(model)
  )

  posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)

  means_by_label <- df_sub %>%
    group_by(Label) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  means_by_stage <- df_sub %>%
    group_by(Phase) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  means_by_task <- df_sub %>%
    group_by(Task) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  means_by_label_stage <- df_sub %>%
    group_by(Phase, Label) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  means_by_stage_task <- df_sub %>%
    group_by(Phase, Task) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  means_by_task_label <- df_sub %>%
    group_by(Task, Label) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  means_by_stage_task_label <- df_sub %>%
    group_by(Phase, Task, Label) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  result_list[[var]] <- list(
    Model_Summary = coef_tbl,
    ANOVA = ANOVA,
    Eta_Squared = as.data.frame(eta_sq),
    M_Label = means_by_label,
    M_Stage = means_by_stage,
    M_Task = means_by_task,
    M_Label_Stage = means_by_label_stage,
    M_Stage_Task = means_by_stage_task,
    M_Task_Label = means_by_task_label,
    M_Stage_Task_Label = means_by_stage_task_label,
    Posthoc_Stage = as.data.frame(posthoc_stage$contrasts),
    Posthoc_Label = as.data.frame(posthoc_label$contrasts),
    Posthoc_Stage_Label = as.data.frame(posthoc_stage_label$contrasts),
    Posthoc_Label_Stage = as.data.frame(posthoc_label_stage$contrasts)
  )
}
```

#### Export Results
``` {r, message=FALSE, warning=FALSE}
# flat_result_list <- list()
#
# for (name in names(result_list)) {
#   for (subname in names(result_list[[name]])) {
#     tab <- result_list[[name]][[subname]]
#     if (is.data.frame(tab)) {
#       sheet_name <- paste(name, subname, sep = "_")
#       flat_result_list[[sheet_name]] <- tab
#     }
#   }
# }
#
# write.xlsx(
#   flat_result_list,
#   file = "results/H2 attitude_intention_behavior_results/H2_Within_Task_Attitude_Perceptions.xlsx"
# )
```

### Attitude Change Over Time
``` {r, message=FALSE, warning=FALSE}
measures <- c("AI_Trust", "AI_Usefulness", "AI_Affect", "Behavioral_Intention")

change_stats <- list()
anova_results <- list()
eta_squared_results <- list()
posthoc_results <- list()
posthoc_results_PL <- list()
posthoc_results_LP <- list()
```

#### Compute Change Scores, Fit Mixed Models
``` {r, message=FALSE, warning=FALSE}
for (msr in measures) {
  cat(paste0("\n===", msr, "===\n"))

  d_sub <- df_long %>%
    filter(measure == msr, Phase %in% c("Pre", "Post"))

  stat_tab_0 <- d_sub %>%
    dplyr::select(ID, Label, Phase, Value, measure) %>%
    group_by(Label, Phase, measure) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = n(),
      .groups = "drop"
    )

  d_wide <- d_sub %>%
    dplyr::select(ID, Label, Phase, Value) %>%
    pivot_wider(names_from = Phase, values_from = Value) %>%
    mutate(change = Post - Pre)

  stat_tab <- d_wide %>%
    group_by(Label) %>%
    summarise(
      MeanChange = round(mean(change, na.rm = TRUE), 2),
      SD = round(sd(change, na.rm = TRUE), 2),
      N = n(),
      .groups = "drop"
    ) %>%
    mutate(Measure = msr) %>%
    relocate(Measure)

  change_stats[[msr]] <- stat_tab

  d_mod <- d_sub %>%
    filter(!is.na(Value)) %>%
    mutate(
      Phase = factor(Phase, levels = c("Post", "Pre")),
      Phase = relevel(as.factor(Phase), ref = "Post")
    )

  if (nrow(d_mod) > 0) {
    model <- lmer(Value ~ Phase * Label + (1 | ID), data = d_mod)

    aov_tab <- anova(model)
    print(aov_tab)

    eta <- eta_squared(model, partial = TRUE)
    print(eta)
    cat("\n")

    posthoc <- emmeans(model, pairwise ~ Phase)
    posthoc_PL <- emmeans(model, pairwise ~ Phase | Label)
    posthoc_LP <- emmeans(model, pairwise ~ Label | Phase)

    anova_results[[msr]] <- as.data.frame(aov_tab) %>%
      tibble::rownames_to_column("Effect") %>%
      mutate(Measure = msr, .before = 1)

    eta_squared_results[[msr]] <- as.data.frame(eta) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results[[msr]] <- as.data.frame(posthoc$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_PL[[msr]] <- as.data.frame(posthoc_PL$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_LP[[msr]] <- as.data.frame(posthoc_LP$contrasts) %>%
      mutate(Measure = msr, .before = 1)
  }
}
```

#### Export Results
``` {r, message=FALSE, warning=FALSE}
# final_output_list <- list(
#   ChangeScore_Summary   = bind_rows(change_stats),
#   ANOVA_Results         = bind_rows(anova_results),
#   Eta_Squared_Results   = bind_rows(eta_squared_results),
#   Posthoc_Results       = bind_rows(posthoc_results),
#   Posthoc_PL_Results    = bind_rows(posthoc_results_PL),
#   Posthoc_LP_Results    = bind_rows(posthoc_results_LP)
# )
#
# write.xlsx(
#   final_output_list,
#   file = "results/H2 attitude_intention_behavior_results/H2_Attitude_Change_Immediate_Results.xlsx",
#   overwrite = TRUE
# )
```

### Post-Survey Experience & Sign-Up
#### Perceived Learning
``` {r, message=FALSE, warning=FALSE}
anova_learning <- aov(Stats_Improvement ~ Label, data = df)

means_learning <- df %>%
  group_by(Label) %>%
  summarise(
    Mean = round(mean(Stats_Improvement, na.rm = TRUE), 2),
    SD = round(sd(Stats_Improvement, na.rm = TRUE), 2),
    N = n(),
    .groups = "drop"
  )

eta2 <- etaSquared(anova_learning, type = 2)

posthoc_learning <- as.data.frame(
  emmeans(anova_learning, pairwise ~ Label)$contrasts
)

print(anova_learning)
print(eta2)
print(posthoc_learning)
```

#### Satisfaction
``` {r, message=FALSE, warning=FALSE}
df$Satisfaction <- as.ordered(df$Satisfaction)
satis_model <- MASS::polr(Satisfaction ~ Label, data = df, Hess = TRUE)

summary(satis_model)

satis_aov <- Anova(satis_model)
print(satis_aov)

emmeans_satis <- emmeans(satis_model, pairwise ~ Label)
posthoc_satis <- as.data.frame(emmeans_satis$contrasts)

means_satis <- df %>%
  group_by(Label) %>%
  summarise(
    Mean = round(mean(as.numeric(Satisfaction), na.rm = TRUE), 2),
    SD = round(sd(as.numeric(Satisfaction), na.rm = TRUE), 2),
    Median = median(as.numeric(Satisfaction), na.rm = TRUE),
    N = n(),
    .groups = "drop"
  )
```

#### Sign-Up Behavior
``` {r, message=FALSE, warning=FALSE}
logit_model <- glm(Sign_Up ~ Label, data = df, family = binomial)

summary(logit_model)

odds_ci <- exp(cbind(OR = coef(logit_model), confint(logit_model)))

table_signup <- table(df$Label, df$Sign_Up)
chisq_test <- chisq.test(table_signup)

print(chisq_test)

cramers_v <- sqrt(
  chisq_test$statistic / (sum(table_signup) * (min(dim(table_signup)) - 1))
)
```

#### Export Results
``` {r, message=FALSE, warning=FALSE}
# write.xlsx(
#   list(
#     Learning_ANOVA        = as.data.frame(summary(anova_learning)[[1]]),
#     Learning_Means        = means_learning,
#     Learning_Eta2         = as.data.frame(eta2),
#     Learning_Posthoc      = posthoc_learning,
#     Satisfaction_Means    = means_satis,
#     Satisfaction_Model    = tidy(satis_model),
#     Satisfaction_Posthoc  = posthoc_satis,
#     SignUp_Table          = as.data.frame(table_signup),
#     SignUp_Logit_Summary  = tidy(logit_model),
#     SignUp_Odds_CI        = as.data.frame(odds_ci),
#     SignUp_ChiSq          = tidy(chisq_test),
#     SignUp_CramersV       = data.frame(CramersV = as.numeric(cramers_v))
#   ),
#   file = "results/Post Survey Experience/Post_Survey_Experience.xlsx",
#   rowNames = TRUE
# )
```

## H3
### Acc, Conf, Will, and Use Moderation Effect
``` {r, message=FALSE, warning=FALSE}
moderators_raw <- c(
  "GLAT_Objective_AI_Literacy",
  "AILS_CCS_Subjective_AI_Literacy",
  "AI_Trust",
  "AI_Usefulness",
  "AI_Affect",
  "AI_Self_Efficacy",
  "Behavioral_Intention"
)

outcomes <- c("accuracy", "confidence", "willing", "useful")

df_mods <- df_long %>%
  filter(tolower(Phase) == "pre", measure %in% moderators_raw) %>%
  dplyr::select(ID, measure, Value) %>%
  pivot_wider(names_from = measure, names_prefix = "pre_", values_from = Value)

df_wide <- df_long %>%
  filter(measure %in% outcomes) %>%
  left_join(df_mods, by = "ID") %>%
  mutate(
    Stage = as.factor(Phase),
    Task  = as.factor(Task),
    Label = as.factor(Label),
    ID    = as.factor(ID)
  ) %>%
  dplyr::select(-Phase)
```

``` {r, message=FALSE, warning=FALSE}
moderators <- c(
  "pre_GLAT_Objective_AI_Literacy",
  "pre_AILS_CCS_Subjective_AI_Literacy",
  "pre_AI_Trust",
  "pre_AI_Usefulness",
  "pre_AI_Affect",
  "pre_AI_Self_Efficacy",
  "pre_Behavioral_Intention",
  "Stats_Background",
  "Used_LLM_Frequency",
  "Used_LLM_Hours"
)

categorical_mods <- c("Stats_Background", "Used_LLM_Frequency", "Used_LLM_Hours")

result_list <- list()
```

#### Fit Mixed Models + ANOVA + Eta + Coefs + Post-hoc (Conditional)
``` {r, message=FALSE, warning=FALSE}
for (outcome in outcomes) {
  for (mod in moderators) {
    if (grepl("^pre_", mod)) {
      df_wide[[mod]] <- scale(df_wide[[mod]], scale = FALSE)
    }

    df_task0 <- df_wide %>%
      filter(
        measure == outcome,
        Task != "task0",
        !is.na(.data[[mod]])
      )

    if (nrow(df_task0) == 0) next

    formula0 <- as.formula(
      paste0("Value ~ Stage * Label * ", mod, " + (1|ID) + (1|Task) + (1|ID:Task)")
    )

    model0 <- lmer(formula0, data = df_task0)

    anova0 <- anova(model0)
    cat(paste0("\n===", outcome, "+", mod, "===\n"))
    print(anova0)
    ANOVA <- as.data.frame(anova0)
    ANOVA$Variable <- rownames(ANOVA)
    ANOVA <- ANOVA[, c("Variable", setdiff(names(ANOVA), "Variable"))]

    eta0 <- as.data.frame(eta_squared(model0, partial = TRUE))

    coef_tbl <- as.data.frame(summary(model0)$coefficients)
    coef_tbl$Variable <- rownames(coef_tbl)
    coef_tbl <- coef_tbl[, c("Variable", setdiff(names(coef_tbl), "Variable"))]

    posthoc_list <- list()

    sig_terms <- rownames(ANOVA)[which(ANOVA$`Pr(>F)` < 0.05)]

    for (term in sig_terms) {
      clean_term <- gsub("[:/\\?\\*\\[\\]]", "_", term)
      term_vars <- unlist(strsplit(term, ":"))

      if (mod %in% categorical_mods && any(term_vars %in% c(mod, "ModeratorScore", mod))) {
        by_vars <- setdiff(term_vars, c(mod, "ModeratorScore"))
        specs <- c(mod, by_vars)

        em_out <- tryCatch(
          emmeans(model0, specs = specs),
          error = function(e) NULL
        )

        if (!is.null(em_out)) {
          posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
        }
      } else if (!(mod %in% categorical_mods) && any(term_vars %in% c(mod, "ModeratorScore", mod))) {
        other_facs <- setdiff(term_vars, c(mod, "ModeratorScore"))

        if (length(other_facs) == 0) {
          specs <- ~1
        } else {
          specs <- as.formula(paste0("~", paste(other_facs, collapse = "*")))
        }

        et <- tryCatch(
          emtrends(
            model0,
            specs = specs,
            var = ifelse("ModeratorScore" %in% term_vars, "ModeratorScore", mod),
            infer = c(TRUE, TRUE)
          ),
          error = function(e) NULL
        )

        if (!is.null(et)) {
          posthoc_list[[paste0(clean_term, "_trends")]] <-
            as.data.frame(summary(et, infer = c(TRUE, TRUE)))

          if (length(other_facs) > 0) {
            ph_pair <- tryCatch(as.data.frame(pairs(et)), error = function(e) NULL)
            if (!is.null(ph_pair)) {
              posthoc_list[[paste0(clean_term, "_trends_pairs")]] <- ph_pair
            }
          }
        }
      } else if (length(term_vars) > 0) {
        em_out <- tryCatch(
          emmeans(model0, specs = term_vars),
          error = function(e) NULL
        )

        if (!is.null(em_out)) {
          posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
        }
      }
    }

    result_list[[paste0(outcome, "_by_", mod)]] <- list(
      Formula      = as.character(formula0),
      ANOVA        = ANOVA,
      Eta_Squared  = eta0,
      Coef_Summary = coef_tbl,
      Posthoc      = posthoc_list
    )
  }
}
```

#### Export Results
``` {r, message=FALSE, warning=FALSE}
# mod_abbr <- c(
#   "pre_GLAT_Objective_AI_Literacy"       = "GLAT",
#   "pre_AILS_CCS_Subjective_AI_Literacy"  = "AILSCCS",
#   "pre_AI_Trust"                         = "Trust",
#   "pre_AI_Usefulness"                    = "Useful",
#   "pre_AI_Affect"                        = "Affect",
#   "pre_AI_Self_Efficacy"                 = "SelfEff",
#   "pre_Behavioral_Intention"             = "BehInt",
#   "Stats_Background"                     = "StatsBG",
#   "Used_LLM_Frequency"                   = "LLMFreq",
#   "Used_LLM_Hours"                       = "LLMHr"
# )
#
# flat_result_list <- list()
#
# for (nm in names(result_list)) {
#   key_base <- strsplit(nm, "_")[[1]]
#   outcome_letter <- substr(key_base[1], 1, 1)
#
#   moderator <- paste(key_base[4:length(key_base)], collapse = "_")
#   mod_short <- ifelse(
#     moderator %in% names(mod_abbr),
#     mod_abbr[[moderator]],
#     substr(moderator, 1, 8)
#   )
#
#   prefix <- paste(outcome_letter, mod_short, sep = "_")
#
#   flat_result_list[[paste0(prefix, "_ANOVA")]] <- result_list[[nm]]$ANOVA
#   flat_result_list[[paste0(prefix, "_EtaSq")]] <- result_list[[nm]]$Eta_Squared
#   flat_result_list[[paste0(prefix, "_Coef")]] <- result_list[[nm]]$Coef_Summary
#
#   if (!is.null(result_list[[nm]]$Posthoc)) {
#     for (int_type in names(result_list[[nm]]$Posthoc)) {
#       ph <- result_list[[nm]]$Posthoc[[int_type]]
#       if (!is.null(ph) && is.data.frame(ph) && nrow(ph) > 0) {
#         flat_result_list[[paste0(prefix, "*PH*", substr(int_type, 1, 8))]] <- ph
#       }
#     }
#   }
# }
#
# names(flat_result_list) <- gsub(":", "_", names(flat_result_list))
#
# write.xlsx(
#   flat_result_list,
#   file = "results/H3 moderation_effects/H3_Within_Task_Moderation_ALL_Posthoc.xlsx"
# )
```

#### Export Significant Effects Summary
``` {r, message=FALSE, warning=FALSE}
export_sig_effects <- function(
  result_list,
  out_excel_path
) {
  if (!dir.exists(dirname(out_excel_path))) {
    dir.create(dirname(out_excel_path), recursive = TRUE)
  }

  summary_sig_effects <- data.frame(
    DV = character(),
    Moderator = character(),
    Term = character(),
    NumDF = numeric(),
    DenDF = numeric(),
    F_value = numeric(),
    p_value = numeric(),
    eta_p = numeric(),
    stringsAsFactors = FALSE
  )

  for (res_name in names(result_list)) {
    split_name <- unlist(strsplit(res_name, "_by_"))
    DV <- split_name[1]
    Moderator <- split_name[2]

    ANOVA <- result_list[[res_name]]$ANOVA
    Eta <- result_list[[res_name]]$Eta_Squared

    if (is.null(ANOVA)) next
    if (!all(c("Pr(>F)", "F value") %in% names(ANOVA))) next

    sig_rows <- which(ANOVA$`Pr(>F)` > 0)
    if (length(sig_rows) == 0) next

    for (i in sig_rows) {
      this_term <- ANOVA$Variable[i]
      Ndf <- ANOVA$NumDF[i]
      Ddf <- ANOVA$DenDF[i]
      Fval <- ANOVA$`F value`[i]
      pval <- ANOVA$`Pr(>F)`[i]

      eta_val <- NA
      if (!is.null(Eta) && "Parameter" %in% names(Eta)) {
        eta_row <- Eta[Eta$Parameter == this_term, , drop = FALSE]
        if (nrow(eta_row) == 1) {
          if ("Eta2_partial" %in% names(eta_row)) eta_val <- eta_row$Eta2_partial
          if ("Eta2" %in% names(eta_row) && is.na(eta_val)) eta_val <- eta_row$Eta2
        }
      }

      summary_sig_effects <- rbind(
        summary_sig_effects,
        data.frame(
          DV = DV,
          Moderator = Moderator,
          Term = this_term,
          NumDF = Ndf,
          DenDF = Ddf,
          F_value = Fval,
          p_value = pval,
          eta_p = eta_val,
          stringsAsFactors = FALSE
        )
      )
    }
  }

  summary_sig_effects <- summary_sig_effects %>%
    arrange(DV, Moderator, p_value)

  write.xlsx(summary_sig_effects, file = out_excel_path, rowNames = FALSE)

  cat(sprintf("Significant terms summary saved to %s\n", out_excel_path))

  invisible(summary_sig_effects)
}
```

``` {r, message=FALSE, warning=FALSE}
export_sig_effects(
  result_list,
  out_excel_path = "results/H3 moderation_effects/H3_Within_Task_Moderation_Summary.xlsx"
)
```

### Attitude Change Immediate Moderation
``` {r, message=FALSE, warning=FALSE}
outcomes <- c("AI_Trust", "AI_Usefulness", "AI_Affect", "Behavioral_Intention")

moderators <- c(
  "GLAT_Objective_AI_Literacy",
  "AILS_CCS_Subjective_AI_Literacy",
  "AI_Trust",
  "AI_Usefulness",
  "AI_Affect",
  "AI_Self_Efficacy",
  "Behavioral_Intention",
  "Stats_Background",
  "Used_LLM_Frequency",
  "Used_LLM_Hours"
)

categorical_mods <- c("Stats_Background", "Used_LLM_Frequency", "Used_LLM_Hours")

result_list <- list()
```

#### Fit Models for Attitude Change (Pre/Post) with Moderation + Post-hoc
``` {r, message=FALSE, warning=FALSE}
for (outcome in outcomes) {
  for (mod in moderators) {
    df_sub <- df_long %>%
      filter(measure == outcome, Phase %in% c("Pre", "Post"))

    if (nrow(df_sub) == 0) next

    df_sub <- df_sub %>%
      mutate(
        Phase = factor(Phase, levels = c("Pre", "Post")),
        Label = as.factor(Label),
        ID    = as.factor(ID)
      )

    posthoc_list <- list()

    if (mod == outcome) {
      baseline_df <- df_sub %>%
        filter(Phase == "Pre") %>%
        dplyr::select(ID, BaselineScore = Value)

      df_sub <- df_sub %>%
        left_join(baseline_df, by = "ID") %>%
        mutate(BaselineScore = scale(BaselineScore, scale = FALSE))

      formula_str <- "Value ~ Phase * Label + BaselineScore + (1|ID)"
      model <- lmer(as.formula(formula_str), data = df_sub)
    } else if (mod %in% df_long$measure) {
      mod_df <- df_long %>%
        filter(Phase == "Pre", measure == mod) %>%
        dplyr::select(ID, ModeratorScore = Value)

      df_sub <- df_sub %>%
        left_join(mod_df, by = "ID") %>%
        mutate(ModeratorScore = scale(ModeratorScore, scale = FALSE))

      formula_str <- "Value ~ Phase * Label * ModeratorScore + (1|ID)"
      model <- lmer(as.formula(formula_str), data = df_sub)
    } else {
      df_sub <- df_sub %>%
        mutate(ModeratorScore = .data[[mod]])

      formula_str <- "Value ~ Phase * Label * ModeratorScore + (1|ID)"
      model <- lmer(as.formula(formula_str), data = df_sub)
    }

    anova_res <- anova(model)
    cat(paste0("\n===", outcome, "+", mod, "===\n"))
    print(anova_res)
    ANOVA <- as.data.frame(anova_res)
    ANOVA$Variable <- rownames(ANOVA)
    ANOVA <- ANOVA[, c("Variable", setdiff(names(ANOVA), "Variable"))]

    eta_sq <- effectsize::eta_squared(model, partial = TRUE)

    coef_tbl <- as.data.frame(summary(model)$coefficients)
    coef_tbl$Variable <- rownames(coef_tbl)
    coef_tbl <- coef_tbl[, c("Variable", setdiff(names(coef_tbl), "Variable"))]

    sig_terms <- rownames(ANOVA)[which(ANOVA$`Pr(>F)` < 0.05)]

    for (term in sig_terms) {
      clean_term <- gsub("[:/\\?\\*\\[\\]]", "_", term)
      term_vars <- unlist(strsplit(term, ":"))
      left_facs <- setdiff(term_vars, c(mod, "ModeratorScore"))

      if (mod %in% categorical_mods && any(term_vars %in% c(mod, "ModeratorScore", mod))) {
        ph_em <- tryCatch(
          emmeans(model, pairwise ~ Label | ModeratorScore),
          error = function(e) NULL
        )

        if (!is.null(ph_em)) {
          posthoc_list[[clean_term]] <- as.data.frame(ph_em$contrasts)
        }
      } else if (!(mod %in% categorical_mods) && any(term_vars %in% c(mod, "ModeratorScore", mod))) {
        if (length(left_facs) == 0) {
          specs <- ~1
        } else {
          specs <- as.formula(paste0("~", paste(left_facs, collapse = "*")))
        }

        et <- tryCatch(
          emtrends(
            model,
            specs = specs,
            var = ifelse("ModeratorScore" %in% term_vars, "ModeratorScore", mod),
            infer = c(TRUE, TRUE)
          ),
          error = function(e) NULL
        )

        if (!is.null(et)) {
          posthoc_list[[paste0(clean_term, "_trends")]] <-
            as.data.frame(summary(et, infer = c(TRUE, TRUE)))

          if (length(left_facs) > 0) {
            ph_pair <- tryCatch(as.data.frame(pairs(et)), error = function(e) NULL)
            if (!is.null(ph_pair)) {
              posthoc_list[[paste0(clean_term, "_trends_pairs")]] <- ph_pair
            }
          }
        }
      } else if (length(term_vars) > 1) {
        em_formula <- as.formula(paste0("~", paste(term_vars, collapse = " * ")))
        em_out <- tryCatch(emmeans(model, em_formula), error = function(e) NULL)

        if (!is.null(em_out)) {
          posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
        }
      } else if (length(term_vars) == 1) {
        em_formula <- as.formula(paste0("~", term))
        em_out <- tryCatch(emmeans(model, em_formula), error = function(e) NULL)

        if (!is.null(em_out)) {
          posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
        }
      }
    }

    result_list[[paste0(outcome, "_by_", mod)]] <- list(
      Formula      = formula_str,
      ANOVA        = ANOVA,
      Eta_Squared  = as.data.frame(eta_sq),
      Coef_Summary = coef_tbl,
      Posthoc      = posthoc_list
    )
  }
}
```

####  Export Results
``` {r, message=FALSE, warning=FALSE}
# clean_sheet <- function(x) gsub("[:/\?\*[\] ]", "_", substr(x, 1, 31))
#
# mod_abbr <- c(
#   "GLAT_Objective_AI_Literacy"          = "GLAT",
#   "AILS_CCS_Subjective_AI_Literacy"     = "AILSCCS",
#   "AI_Trust"                            = "Trust",
#   "AI_Usefulness"                       = "Useful",
#   "AI_Affect"                           = "Affect",
#   "AI_Self_Efficacy"                    = "SelfEff",
#   "Behavioral_Intention"                = "BehInt",
#   "Stats_Background"                    = "StatsBG",
#   "Used_LLM_Frequency"                  = "LLMFreq",
#   "Used_LLM_Hours"                      = "LLMHr"
# )
#
# flat_result_list <- list()
#
# for (nm in names(result_list)) {
#   key_base <- strsplit(nm, "_")[[1]]
#   outcome_short <- substr(key_base[2], 1, 5)
#
#   moderator <- paste(key_base[4:length(key_base)], collapse = "_")
#   mod_short <- ifelse(
#     moderator %in% names(mod_abbr),
#     mod_abbr[[moderator]],
#     substr(moderator, 1, 8)
#   )
#
#   prefix <- paste(outcome_short, mod_short, sep = "_")
#
#   flat_result_list[[clean_sheet(paste0(prefix, "_ANOVA"))]] <- result_list[[nm]]$ANOVA
#   flat_result_list[[clean_sheet(paste0(prefix, "_EtaSq"))]] <- result_list[[nm]]$Eta_Squared
#   flat_result_list[[clean_sheet(paste0(prefix, "_Coef"))]] <- result_list[[nm]]$Coef_Summary
#
#   if (!is.null(result_list[[nm]]$Posthoc)) {
#     for (int_type in names(result_list[[nm]]$Posthoc)) {
#       ph <- result_list[[nm]]$Posthoc[[int_type]]
#       if (!is.null(ph) && is.data.frame(ph) && nrow(ph) > 0) {
#         flat_result_list[[clean_sheet(paste0(prefix, "*Posthoc*", int_type))]] <- ph
#       }
#     }
#   }
# }
#
# names(flat_result_list) <- gsub(":", "_", names(flat_result_list))
#
# write.xlsx(
#   flat_result_list,
#   file = "results/H3 moderation_effects/H3_Attitude_Change_Immediate_Moderation_POSTHOC.xlsx"
# )
```

#### Export Significant Effects Summary
```{r, message=FALSE, warning=FALSE}
export_sig_effects <- function(result_list, out_excel_path) {
  if (!dir.exists(dirname(out_excel_path))) {
    dir.create(dirname(out_excel_path), recursive = TRUE)
  }

  summary_sig_effects <- data.frame(
    DV = character(),
    Moderator = character(),
    Term = character(),
    NumDF = numeric(),
    DenDF = numeric(),
    F_value = numeric(),
    p_value = numeric(),
    eta_p = numeric(),
    stringsAsFactors = FALSE
  )

  for (res_name in names(result_list)) {
    split_name <- unlist(strsplit(res_name, "_by_"))
    DV <- split_name[1]
    Moderator <- split_name[2]

    ANOVA <- result_list[[res_name]]$ANOVA
    Eta <- result_list[[res_name]]$Eta_Squared

    if (is.null(ANOVA)) next
    if (!all(c("Pr(>F)", "F value") %in% names(ANOVA))) next

    sig_rows <- which(ANOVA$`Pr(>F)` < 0.05)
    if (length(sig_rows) == 0) next

    for (i in sig_rows) {
      this_term <- ANOVA$Variable[i]
      Ndf <- ANOVA$NumDF[i]
      Ddf <- ANOVA$DenDF[i]
      Fval <- ANOVA$`F value`[i]
      pval <- ANOVA$`Pr(>F)`[i]

      eta_val <- NA
      if (!is.null(Eta) && "Parameter" %in% names(Eta)) {
        eta_row <- Eta[Eta$Parameter == this_term, , drop = FALSE]
        if (nrow(eta_row) == 1) {
          if ("Eta2_partial" %in% names(eta_row)) eta_val <- eta_row$Eta2_partial
          if ("Eta2" %in% names(eta_row) && is.na(eta_val)) eta_val <- eta_row$Eta2
        }
      }

      summary_sig_effects <- rbind(
        summary_sig_effects,
        data.frame(
          DV = DV,
          Moderator = Moderator,
          Term = this_term,
          NumDF = Ndf,
          DenDF = Ddf,
          F_value = Fval,
          p_value = pval,
          eta_p = eta_val,
          stringsAsFactors = FALSE
        )
      )
    }
  }

  summary_sig_effects <- summary_sig_effects %>%
    dplyr::arrange(DV, Moderator, p_value)

  write.xlsx(summary_sig_effects, file = out_excel_path, rowNames = FALSE)

  cat(sprintf("Significant terms summary saved to %s\n", out_excel_path))

  invisible(summary_sig_effects)
}

export_sig_effects(
  result_list,
  out_excel_path = "results/H3 moderation_effects/H3_Attitude_Change_Moderation_Summary.xlsx"
)
```

### Post Survey Experience
#### Continous Moderation Effects
``` {r, message=FALSE, warning=FALSE}
moderators <- c(
  "Pre_GLAT_Objective_AI_Literacy",
  "Pre_AILS_CCS_Subjective_AI_Literacy",
  "Pre_AI_Trust",
  "Pre_AI_Usefulness",
  "Pre_AI_Affect",
  "Pre_AI_Self_Efficacy",
  "Pre_Behavioral_Intention"
)

df$Satisfaction <- as.factor(df$Satisfaction)

result_list <- list()
```

``` {r, message=FALSE, warning=FALSE}
for (mod in moderators) {
  df[[mod]] <- as.numeric(df[[mod]])

  if (grepl("^Pre_", mod)) {
    df[[mod]] <- scale(df[[mod]], scale = FALSE)
  }

  means_learning_mod <- df %>%
    group_by(Label) %>%
    summarise(
      Mean = round(mean(Stats_Improvement, na.rm = TRUE), 2),
      SD = round(sd(Stats_Improvement, na.rm = TRUE), 2),
      N = n(),
      .groups = "drop"
    )

  formula_learning <- paste0("Stats_Improvement ~ Label * ", mod)
  cat("\n===", "Stats Improvement +", mod, "===\n")
  anova_mod <- aov(as.formula(formula_learning), data = df)
  print(summary(anova_mod))

  anova_tbl <- as.data.frame(summary(anova_mod)[[1]])
  anova_tbl$Variable <- rownames(anova_tbl)
  anova_tbl <- anova_tbl[, c("Variable", setdiff(names(anova_tbl), "Variable"))]

  eta2_mod <- etaSquared(anova_mod, type = 2)

  mean_mod <- mean(df[[mod]], na.rm = TRUE)
  posthoc_learning_mod <- tryCatch(
    as.data.frame(
      emmeans(anova_mod, pairwise ~ Label, at = setNames(list(mean_mod), mod))$contrasts
    ),
    error = function(e) data.frame()
  )

  formula_satis <- paste0("Satisfaction ~ Label * ", mod)
  cat("\n===", "Satisfaction +", mod, "===\n")
  satis_model_mod <- MASS::polr(as.formula(formula_satis), data = df, Hess = TRUE)

  satis_aov <- Anova(satis_model_mod)
  print(satis_aov)

  coefs <- summary(satis_model_mod)$coefficients
  pvals <- 2 * pnorm(-abs(coefs[, "t value"]))
  Satisfaction_Coefficients <- as.data.frame(cbind(coefs, "p value" = pvals))

  posthoc_satis_mod <- tryCatch(
    {
      em_obj <- emmeans(
        satis_model_mod,
        pairwise ~ Label,
        at = setNames(list(mean_mod), mod)
      )
      as.data.frame(em_obj$contrasts)
    },
    error = function(e) data.frame()
  )

  means_satis <- df %>%
    group_by(Label) %>%
    summarise(
      Mean = round(mean(as.numeric(Satisfaction), na.rm = TRUE), 2),
      SD = round(sd(as.numeric(Satisfaction), na.rm = TRUE), 2),
      Median = median(as.numeric(Satisfaction), na.rm = TRUE),
      N = n(),
      .groups = "drop"
    )

  formula_signup <- paste0("Sign_Up ~ Label * ", mod)
  cat("\n===", "Sign Up +", mod, "===\n")
  logit_model_mod <- glm(as.formula(formula_signup), data = df, family = binomial)

  odds_ci_mod <- exp(cbind(OR = coef(logit_model_mod), confint(logit_model_mod)))

  table_signup <- table(df$Label, df$Sign_Up)
  chisq_test <- chisq.test(table_signup)
  print(chisq_test)

  cramers_v <- sqrt(
    chisq_test$statistic / (sum(table_signup) * (min(dim(table_signup)) - 1))
  )

  emm <- emmeans(logit_model_mod, ~Label, type = "response")
  contrast_table <- as.data.frame(pairs(emm, adjust = "tukey"))

  result_list[[mod]] <- list(
    Learning_ANOVA = anova_tbl,
    Learning_Eta2 = as.data.frame(eta2_mod),
    Learning_Posthoc = posthoc_learning_mod,
    Learning_Means = means_learning_mod,
    Satisfaction_Coefs = Satisfaction_Coefficients,
    Satisfaction_AOV = as.data.frame(satis_aov),
    Satisfaction_Posthoc = posthoc_satis_mod,
    Satisfaction_Means = means_satis,
    SignUp_Logit_Coefs = as.data.frame(summary(logit_model_mod)$coefficients),
    SignUp_Odds_CI = as.data.frame(odds_ci_mod),
    SignUp_ChiSq = data.frame(
      statistic = as.numeric(chisq_test$statistic),
      parameter = as.numeric(chisq_test$parameter),
      p.value   = as.numeric(chisq_test$p.value)
    ),
    SignUp_CramersV = data.frame(CramersV = as.numeric(cramers_v)),
    SignUp_Posthoc_Tukey = contrast_table
  )
}
```

##### Export Results
``` {r, message=FALSE, warning=FALSE}
# clean_sheet <- function(x) gsub("[:/\?\*[\] ]", "_", substr(x, 1, 31))
#
# flat_result_list <- list()
#
# for (mod in names(result_list)) {
#   for (nm in names(result_list[[mod]])) {
#     sheet_nm <- clean_sheet(paste(substr(mod, 1, 15), substr(nm, 1, 15), sep = "_"))
#     flat_result_list[[sheet_nm]] <- result_list[[mod]][[nm]]
#   }
# }
#
# write.xlsx(
#   flat_result_list,
#   file = "results/Post Survey Experience/Post_Survey_Moderation_Results.xlsx",
#   rowNames = TRUE
# )
```

#### Categorical Moderation Effects
``` {r, message=FALSE, warning=FALSE}
moderators <- c("Stats_Background", "Used_LLM_Frequency", "Used_LLM_Hours")

df <- df %>%
  mutate(
    Stats_Background   = as.factor(Stats_Background),
    Used_LLM_Frequency = as.factor(Used_LLM_Frequency),
    Used_LLM_Hours     = as.factor(Used_LLM_Hours),
    Satisfaction       = as.factor(Satisfaction)
  )

result_list <- list()
```

``` {r, message=FALSE, warning=FALSE}
for (mod in moderators) {
  formula_anova <- as.formula(paste0("Stats_Improvement ~ Label * ", mod))
  cat("\n===", "Stats Improvement +", mod, "===\n")
  anova_mod <- aov(formula_anova, data = df)
  print(summary(anova_mod))

  anova_tbl <- as.data.frame(summary(anova_mod)[[1]])
  anova_tbl$Variable <- rownames(anova_tbl)
  anova_tbl <- anova_tbl[, c("Variable", setdiff(names(anova_tbl), "Variable"))]

  means_learning_mod <- df %>%
    group_by(Label, !!sym(mod)) %>%
    summarise(
      Mean = round(mean(Stats_Improvement, na.rm = TRUE), 2),
      SD = round(sd(Stats_Improvement, na.rm = TRUE), 2),
      N = n(),
      .groups = "drop"
    )

  emm_formula_interaction <- as.formula(paste("pairwise ~ Label *", mod))

  posthoc_learning_mod <- tryCatch(
    as.data.frame(emmeans(anova_mod, emm_formula_interaction)),
    error = function(e) data.frame()
  )

  formula_satis <- as.formula(paste0("Satisfaction ~ Label * ", mod))
  cat("\n===", "Satisfaction +", mod, "===\n")
  satis_model_mod <- MASS::polr(formula_satis, data = df, Hess = TRUE)

  satis_aov <- Anova(satis_model_mod)
  print(satis_aov)

  coefs <- summary(satis_model_mod)$coefficients
  pvals <- 2 * pnorm(-abs(coefs[, "t value"]))
  Satisfaction_Coefficients <- as.data.frame(cbind(coefs, "p value" = pvals))

  means_satis <- df %>%
    group_by(Label, !!sym(mod)) %>%
    summarise(
      Mean = round(mean(as.numeric(Satisfaction), na.rm = TRUE), 2),
      SD = round(sd(as.numeric(Satisfaction), na.rm = TRUE), 2),
      Median = median(as.numeric(Satisfaction), na.rm = TRUE),
      N = n(),
      .groups = "drop"
    )

  posthoc_satis_mod <- tryCatch(
    as.data.frame(emmeans(satis_model_mod, emm_formula_interaction)),
    error = function(e) data.frame()
  )

  formula_logit <- as.formula(paste0("Sign_Up ~ Label * ", mod))
  cat("\n===", "Sign Up +", mod, "===\n")
  logit_model_mod <- glm(formula_logit, data = df, family = binomial)

  table_signup <- table(df$Label, df$Sign_Up)
  chisq_test <- chisq.test(table_signup)
  print(chisq_test)

  cramers_v <- sqrt(
    chisq_test$statistic / (sum(table_signup) * (min(dim(table_signup)) - 1))
  )

  emm <- emmeans(logit_model_mod, ~Label, type = "response")
  contrast_table <- as.data.frame(pairs(emm, adjust = "tukey"))

  result_list[[mod]] <- list(
    Learning_ANOVA = anova_tbl,
    Learning_Means = means_learning_mod,
    Learning_Posthoc = posthoc_learning_mod,
    Satisfaction_Coeffs = Satisfaction_Coefficients,
    Satisfaction_AOV = as.data.frame(satis_aov),
    Satisfaction_Means = means_satis,
    Satisfaction_Posthoc = posthoc_satis_mod,
    SignUp_Logit_Coeffs = as.data.frame(summary(logit_model_mod)$coefficients),
    SignUp_ChiSq = data.frame(
      statistic = as.numeric(chisq_test$statistic),
      parameter = as.numeric(chisq_test$parameter),
      p.value   = as.numeric(chisq_test$p.value)
    ),
    SignUp_CramersV = data.frame(CramersV = as.numeric(cramers_v)),
    SignUp_Posthoc_Tukey = contrast_table
  )
}
```

##### Export Results
``` {r, message=FALSE, warning=FALSE}
# clean_sheet <- function(x) gsub("[:/\?\*[\] ]", "_", substr(x, 1, 31))
# 
# flat_result_list <- list()
# 
# for (mod in names(result_list)) {
#   for (nm in names(result_list[[mod]])) {
#     sheet_nm <- clean_sheet(paste(substr(mod, 1, 15), substr(nm, 1, 15), sep = "_"))
#     flat_result_list[[sheet_nm]] <- result_list[[mod]][[nm]]
#   }
# }
# 
# write.xlsx(
#   flat_result_list,
#   file = "results/Post Survey Experience/Post_Survey_Moderation_Results_2.xlsx",
#   rowNames = TRUE
# )
```
