---
title: "Study 2 — Main (Initial-Session) Analyses"
author: "Siyuan Huang"
date: "2025-07-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, message = FALSE, warning = FALSE,
  cache = TRUE, autodep = TRUE, cache.lazy = FALSE
)

set.seed(42)
```

# Study 2 — Main (Initial-Session) Analyses

This document reports the primary Study 2 analyses on the initial
session (Pre, Stage 1–3, Post). Participants with a Stage-1 baseline
(task 0) accuracy of `>= 0.90` are excluded by a ceiling-effect screen,
consistent with all other Study 2 analyses.

The hypotheses are: **H1** learning progression in task performance
(accuracy) across stages by labelling condition; **H2** confidence,
willingness, usefulness, attitude change (Pre → Post), and post-survey
experience; and **H3** moderation of these effects by individual-
difference measures. Baseline equivalence across conditions is checked
first.

## Packages
```{r packages, cache = FALSE}
library(broom)
library(car)
library(DescTools)
library(dplyr)
library(DT)
library(effectsize)
library(emmeans)
library(ggplot2)
library(janitor)
library(lme4)
library(lmerTest)
library(lsr)
library(MASS)
library(openxlsx)
library(ordinal)
library(performance)
library(readxl)
library(stringr)
library(tidyr)
library(report)
library(interactions)
library(forcats)
library(tibble)

# Output directories: results are organised into per-section subfolders.
for (d in c("Baseline", "H1", "H2", "H3")) {
  dir.create(file.path("results", d), recursive = TRUE, showWarnings = FALSE)
}
```

## Data Processing

The data are loaded, the ceiling-effect screen
(`stage1_task0_accuracy < 0.9`) is applied, background variables are
recoded, and the data are reshaped to long format. The factor ordering
AI < AI + Human < Human is used throughout.

### Load Data
```{r load-data-1}
df <- read_excel("data/Study_2_Main_Results_Data.xlsx")
head(df)

# Set Label Factor
df <- df %>%
  mutate(Label = factor(Label, levels = c("AI", "AI Human", "Human")))
```

### Stage 1 Task 0 Accuracy Distribution
```{r stage-1-task-0-accuracy-distribution-1}
ggplot(df, aes(x = stage1_task0_accuracy)) +
  geom_histogram(binwidth = 0.05, fill = "skyblue", color = "black") +
  stat_bin(
    binwidth = 0.05,
    geom = "text",
    aes(label = ..count..),
    vjust = -0.3
  ) +
  scale_x_continuous(
    breaks = seq(0, 1, by = 0.05),
    labels = sprintf("%.2f", seq(0, 1, by = 0.05))
  ) +
  labs(
    title = "Distribution of stage1_task0_accuracy",
    x = "stage1_task0_accuracy",
    y = "Frequency"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Filter Stage 1 Task 0 Accuracy
```{r filter-stage-1-task-0-accuracy-1}
df_over90 <- df %>% filter(stage1_task0_accuracy >= 0.9)

sum(df$stage1_task0_accuracy >= 0.9)

df <- df %>% filter(stage1_task0_accuracy < 0.9)
```

### Recode Background Variables
```{r recode-background-variables-1}
df <- df %>%
  mutate(
    Stats_Background = cut(
      as.numeric(as.character(Stats_Background)),
      breaks = c(1, 3, 5, 8),
      labels = c("Low", "Medium", "High"),
      right = TRUE,
      include.lowest = TRUE
    ),
    Used_LLM_Frequency = forcats::fct_collapse(
      as.character(Used_LLM_Frequency),
      Rarely = c("Never", "Less than once a month", "1–3 times per month"),
      Often = c("Weekly", "Daily")
    ),
    Used_LLM_Hours = forcats::fct_collapse(
      as.character(Used_LLM_Hours),
      None = "0",
      Low = c("1–5", "6–10"),
      High = c("11–20", ">20")
    )
  )
```

### Convert to Long Format
```{r convert-to-long-format-1}
cols_to_long <- grep("^(Pre|Post|stage\\d+)_", colnames(df), value = TRUE)

df_long <- df %>%
  pivot_longer(
    cols = all_of(cols_to_long),
    names_to = "fullvar",
    values_to = "Value"
  ) %>%
  mutate(
    Phase = str_extract(fullvar, "^(Pre|Post|stage\\d+)"),
    tmp = str_remove(fullvar, "^(Pre|Post|stage\\d+)_"),
    task = ifelse(str_detect(tmp, "^task\\d+"), str_extract(tmp, "^task\\d+"), NA),
    measure = ifelse(!is.na(task), str_remove(tmp, "^task\\d+_"), tmp),
    tmp = NULL,
    fullvar = NULL
  )

head(df_long)
```

## Baseline Equivalence Across Conditions

Per-condition descriptive statistics and one-way ANOVAs on the seven
pre-survey measures verify that the labelling conditions did not differ
at baseline.

```{r baseline-equivalence-across-conditions-1}
varnames <- c(
  "Pre_GLAT_Objective_AI_Literacy",
  "Pre_AILS_CCS_Subjective_AI_Literacy",
  "Pre_AI_Trust",
  "Pre_AI_Usefulness",
  "Pre_AI_Affect",
  "Pre_AI_Self_Efficacy",
  "Pre_Behavioral_Intention"
)

label_summary_table <- bind_rows(lapply(varnames, function(v) {
  df %>%
    group_by(Label) %>%
    summarise(
      Mean = round(mean(.data[[v]], na.rm = TRUE), 2),
      SD = round(sd(.data[[v]], na.rm = TRUE), 2),
      n = sum(!is.na(.data[[v]])),
      .groups = "drop"
    ) %>%
    mutate(Variable = v) %>%
    relocate(Variable)
}))

label_summary_table
```

### Baseline ANOVA by Label
```{r baseline-anova-by-label-1}
anova_results_table <- bind_rows(lapply(varnames, function(v) {
  aov_res <- summary(aov(df[[v]] ~ df$Label))
  data.frame(
    Variable = v,
    F_value = round(aov_res[[1]][["F value"]][1], 2),
    p_value = round(aov_res[[1]][["Pr(>F)"]][1], 4)
  )
}))

anova_results_table
```

### Export Baseline Results
```{r export-baseline-results-1}
all_results <- list(
Label_Summary = label_summary_table,
ANOVA_Results = anova_results_table
)

write.xlsx(
all_results,
file = "results/Baseline/Baseline_Charateristics_By_Label.xlsx"
)
```

## Manipulation Check: Source Recall

A manipulation check was administered after the learning task, asking
participants to recall which type of guidance they had received (AI,
AI + Human, or Human). For a source-attribution experiment, this
source-recall rate is the key manipulation check: in the AI + Human
condition in particular, confusions with the Human or AI labels could
dilute the manipulation in ways that bear on interpretation.

### Recall Accuracy by Condition
```{r recall-accuracy-by-condition-1}
mc_df <- df %>%
  mutate(
    Recalled_Label = dplyr::recode(Recalled_Label, "AI + Human" = "AI Human"),
    Recalled_Label = factor(Recalled_Label, levels = c("AI", "AI Human", "Human")),
    Passed_Check = as.integer(as.character(Label) == as.character(Recalled_Label))
  )

# 3 x 3 confusion matrix (rows = assigned condition, columns = recalled)
confusion_counts <- mc_df %>%
  tabyl(Label, Recalled_Label) %>%
  adorn_totals(c("row", "col"))
confusion_counts

confusion_props <- mc_df %>%
  tabyl(Label, Recalled_Label) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 1) %>%
  adorn_ns()
confusion_props

# Per-condition correct-recall rate
recall_rate <- mc_df %>%
  group_by(Label) %>%
  summarise(
    N        = n(),
    N_Passed = sum(Passed_Check),
    Recall_Rate = mean(Passed_Check)
  )
recall_rate

# Overall recall rate and chi-square test of association
overall_rate <- mean(mc_df$Passed_Check)
cat("Overall correct-recall rate:", round(overall_rate, 3), "\n")

chisq_test <- chisq.test(table(mc_df$Label, mc_df$Recalled_Label))
print(chisq_test)
```

## H1: Learning Progression in Task Performance (Accuracy)

H1 tests whether task accuracy improves across the initial-session stages
(Stage 1 → 2 → 3) and whether this differs by labelling condition. Linear
mixed models are reported without and with the task factor.

### Data Filter
```{r data-filter-1}
performance_long <- df_long %>%
  rename(
    Task = task,
    Measure = measure
  ) %>%
  filter(
    Measure == "accuracy",
    Task != "task0"
  )

head(performance_long)
```

### Descriptive Summary
```{r descriptive-summary-1}
stage_summary <- performance_long %>%
  group_by(Phase, Label) %>%
  summarise(
    Mean = round(mean(Value, na.rm = TRUE), 2),
    SD = round(sd(Value, na.rm = TRUE), 2),
    N = n(),
    .groups = "drop"
  )

stage_summary
```

### Mixed Model (Without Task)
```{r mixed-model-without-task-1}
performance_long <- performance_long %>%
  mutate(
    Label = factor(Label),
    Phase = factor(Phase, levels = c("stage3", "stage2", "stage1")),
    Task = factor(Task),
    Stats_Background = factor(Stats_Background)
  )

model <- lmer(
  Value ~ Phase * Label + (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = performance_long
)

model_summary <- summary(model)$coefficients
anova_results <- anova(model)
eta_sq <- effectsize::eta_squared(model, partial = TRUE)

model_summary
anova_results
eta_sq
```

#### Post-hoc Comparisons
```{r post-hoc-comparisons-1}
posthoc_stage <- emmeans(model, pairwise ~ Phase)
posthoc_label <- emmeans(model, pairwise ~ Label)
posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)

cat("===Stage===\n")
posthoc_stage$contrasts
cat("\n===Label===\n")
posthoc_label$contrasts
cat("\n===Stage:Label===\n")
posthoc_stage_label$contrasts
cat("\n===Label:Stage===\n")
posthoc_label_stage$contrasts
```

#### Effect Sizes for Contrasts
```{r effect-sizes-for-contrasts-1}
cat("===Cohen's d: Stage===\n")
print(eff_size(posthoc_stage, sigma = sigma(model), edf = df.residual(model)))

cat("\n===Cohen's d: Label===\n")
print(eff_size(posthoc_label, sigma = sigma(model), edf = df.residual(model)))

cat("\n===Cohen's d: Stage | Label===\n")
print(eff_size(posthoc_stage_label, sigma = sigma(model), edf = df.residual(model)))

cat("\n===Cohen's d: Label | Stage===\n")
print(eff_size(posthoc_label_stage, sigma = sigma(model), edf = df.residual(model)))
```

#### Report and Export Results
```{r report-and-export-results-1}
report(anova_results)

write.xlsx(
  list(
    Model_Summary = as.data.frame(model_summary),
    ANOVA = as.data.frame(anova_results),
    Eta_Squared = as.data.frame(eta_sq),
    Posthoc_Stage = as.data.frame(posthoc_stage$contrasts),
    Posthoc_Label = as.data.frame(posthoc_label$contrasts),
    Posthoc_Stage_Label = as.data.frame(posthoc_stage_label$contrasts),
    Posthoc_Label_Stage = as.data.frame(posthoc_label_stage$contrasts)
  ),
  file = "results/H1/H1_Performance_Comparison_LMM.xlsx",
  rowNames = TRUE
)
```

### Mixed Model (With Task)
```{r mixed-model-with-task-1}
model_task <- lmer(
  Value ~ Phase * Label * Task + (1 | ID) + (1 | ID:Task),
  data = performance_long
)

model_task_summary <- summary(model_task)$coefficients
anova_task <- anova(model_task)
eta_task <- effectsize::eta_squared(model_task, partial = TRUE)

model_task_summary
anova_task
eta_task
```

#### Post-hoc With Task
```{r post-hoc-with-task-1}
posthoc_stage_task <- emmeans(model_task, pairwise ~ Phase)
posthoc_task <- emmeans(model_task, pairwise ~ Task)
posthoc_label_task <- emmeans(model_task, pairwise ~ Label)

posthoc_stage_by_label_task <- emmeans(model_task, pairwise ~ Phase | Label)
posthoc_label_by_phase_task <- emmeans(model_task, pairwise ~ Label | Phase)
posthoc_stage_by_task_task <- emmeans(model_task, pairwise ~ Phase | Task)
posthoc_3way_task <- emmeans(model_task, pairwise ~ Phase | Task | Label)

posthoc_stage_task$contrasts
posthoc_task$contrasts
posthoc_label_task$contrasts
posthoc_stage_by_label_task$contrasts
posthoc_label_by_phase_task$contrasts
posthoc_stage_by_task_task$contrasts
posthoc_3way_task$contrasts

cat("\n===Cohen's d: Stage===\n")
print(eff_size(posthoc_stage_task, sigma = sigma(model_task), edf = df.residual(model_task)))

cat("\n===Cohen's d: Task===\n")
print(eff_size(posthoc_task, sigma = sigma(model_task), edf = df.residual(model_task)))

cat("\n===Cohen's d: Label===\n")
print(eff_size(posthoc_label_task, sigma = sigma(model_task), edf = df.residual(model_task)))

cat("\n===Cohen's d: Stage | Label===\n")
print(eff_size(posthoc_stage_by_label_task, sigma = sigma(model_task), edf = df.residual(model_task)))

cat("\n===Cohen's d: Label | Phase===\n")
print(eff_size(posthoc_label_by_phase_task, sigma = sigma(model_task), edf = df.residual(model_task)))

cat("\n===Cohen's d: Stage | Task===\n")
print(eff_size(posthoc_stage_by_task_task, sigma = sigma(model_task), edf = df.residual(model_task)))

cat("\n===Cohen's d: Phase | Task | Label===\n")
print(eff_size(posthoc_3way_task, sigma = sigma(model_task), edf = df.residual(model_task)))
```

#### Export With Task
```{r export-with-task-1}
write.xlsx(
  list(
    Model_Summary = as.data.frame(model_task_summary),
    ANOVA = as.data.frame(anova_task),
    Eta_Squared = as.data.frame(eta_task),
    Posthoc_Stage = as.data.frame(posthoc_stage_task$contrasts),
    Posthoc_Task = as.data.frame(posthoc_task$contrasts),
    Posthoc_Label = as.data.frame(posthoc_label_task$contrasts),
    Posthoc_Stage_Label = as.data.frame(posthoc_stage_by_label_task$contrasts),
    Posthoc_Label_Stage = as.data.frame(posthoc_label_by_phase_task$contrasts),
    Posthoc_Stage_Task = as.data.frame(posthoc_stage_by_task_task$contrasts),
    Posthoc_3way = as.data.frame(posthoc_3way_task$contrasts)
  ),
  file = "results/H1/H1_Performance_Comparison_LMM_Task.xlsx",
  rowNames = TRUE
)
```

### Robustness: Item-Level Binomial GLMM

The primary H1 models treat task-level accuracy — a proportion of only 5–6
binary items — as a Gaussian outcome, which can strain linear-model
assumptions. As a robustness check we refit the learning-progression effect
as an **item-level binomial GLMM** (the response family used for the
early/late analysis), modelling each binary item response directly with
crossed participant and item intercepts plus a participant-by-item term
that absorbs repeated exposure and binomial overdispersion:

`correct ~ Stage * Label + (1 | ID) + (1 | Item) + (1 | ID:Item)`

Item responses are read from `correction_raw_data.xlsx` for the same cohort
as the main model (Stage-1 ceiling-screened), so the two describe the same
data on different scales. A task-level intercept is omitted (items nest in
only three tasks, so its variance sits near the boundary while `(1 | Item)`
already absorbs item clustering); this does not affect the Stage × Label
inference. Matching the Gaussian LMM confirms the conclusion is robust to
the modelling choice.

#### Build Item-Level Dataset (Main Cohort)
```{r itemlevel-data-1}
# Ground-truth key for the 17 items (task 1: 6, task 2: 5, task 3: 6).
item_names <- c(paste0("t1_q", 1:6), paste0("t2_q", 1:5), paste0("t3_q", 1:6))
item_truth <- c(rep(FALSE, 6), rep(FALSE, 5), FALSE, TRUE, TRUE, TRUE, FALSE, TRUE)
names(item_truth) <- item_names

# Analytic cohort = the same ceiling-screened participants used by the main model.
cohort_ids <- unique(as.character(df$ID))

stage_cols <- paste0(rep(c("stage1_", "stage2_", "stage3_"), each = length(item_names)), item_names)

item_long <- read_excel("data/correction_raw_data.xlsx") %>%
  mutate(ID = as.character(ID)) %>%
  filter(ID %in% cohort_ids) %>%
  dplyr::select(ID, Label, all_of(stage_cols)) %>%
  pivot_longer(
    cols = all_of(stage_cols),
    names_to = c("Stage", "Item"),
    names_pattern = "^(stage[123])_(t[123]_q\\d+)$",
    values_to = "Answer"
  ) %>%
  mutate(
    Truth = item_truth[as.character(Item)],
    correct = as.integer(as.logical(Answer) == Truth),
    Task = factor(sub("_q\\d+$", "", Item), levels = c("t1", "t2", "t3")),
    Item = factor(Item, levels = item_names),
    # Match the main model's factor ordering (reference = stage3 / AI).
    Stage = factor(Stage, levels = c("stage3", "stage2", "stage1")),
    Label = factor(Label, levels = c("AI", "AI Human", "Human")),
    ID = factor(ID)
  )

# Cohort check: should equal the main analytic n.
cat("Item-level cohort n =", dplyr::n_distinct(item_long$ID),
    "| item responses =", nrow(item_long), "\n")
head(item_long)
```

#### Fit Item-Level Binomial GLMM
```{r itemlevel-model-1}
itemlevel_model <- glmer(
  correct ~ Stage * Label + (1 | ID) + (1 | Item) + (1 | ID:Item),
  data = item_long,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(itemlevel_model)
```

#### Odds Ratios, Type-III Tests, and Contrasts
```{r itemlevel-inference-1}
# Odds ratios for fixed effects (Wald CIs).
itemlevel_or <- exp(cbind(
  OR = fixef(itemlevel_model),
  confint(itemlevel_model, parm = "beta_", method = "Wald")
))
itemlevel_or

# Type-III tests (matches the early/late analysis convention).
itemlevel_anova <- car::Anova(itemlevel_model, type = 3)
itemlevel_anova

# Stage contrasts overall and within each label, on the response scale.
itemlevel_emm_stage <- emmeans(itemlevel_model, pairwise ~ Stage, type = "response")
itemlevel_emm_stage_label <- emmeans(itemlevel_model, pairwise ~ Stage | Label, type = "response")
itemlevel_emm_label_stage <- emmeans(itemlevel_model, pairwise ~ Label | Stage, type = "response")
itemlevel_emm_stage$contrasts
itemlevel_emm_stage_label$contrasts
itemlevel_emm_label_stage$contrasts
```

#### Export Item-Level Robustness Results
```{r itemlevel-export-1}
write.xlsx(
  list(
    Fixed_Effects = as.data.frame(summary(itemlevel_model)$coefficients),
    Odds_Ratios = as.data.frame(itemlevel_or),
    Type3_ANOVA = as.data.frame(itemlevel_anova),
    Posthoc_Stage = as.data.frame(itemlevel_emm_stage$contrasts),
    Posthoc_Stage_by_Label = as.data.frame(itemlevel_emm_stage_label$contrasts)
  ),
  file = "results/H1/H1_Performance_ItemLevel_Binomial_GLMM.xlsx",
  rowNames = TRUE
)
```

## H1 Sensitivity: Manipulation Passers Only

Not every participant correctly recalled their assigned label. Because
source attribution is the manipulation, we refit the primary H1 model
(without the task factor) on participants who passed the check (assigned
`Label` == recalled label). If the Phase × Label pattern holds, the
conclusion is not driven by participants who misremembered their condition.

### Restrict to Passers
```{r passers-data-1}
# Passer = recalled label matches assigned label (Passed_Check == 1 in mc_df).
passer_ids <- mc_df %>%
  filter(Passed_Check == 1) %>%
  pull(ID) %>%
  as.character() %>%
  unique()

performance_long_pass <- performance_long %>%
  filter(as.character(ID) %in% passer_ids) %>%
  droplevels()

cat("Passers retained:", dplyr::n_distinct(performance_long_pass$ID),
    "of", dplyr::n_distinct(performance_long$ID), "participants\n")
print(performance_long_pass %>%
  group_by(Phase, Label) %>%
  summarise(Mean = round(mean(Value, na.rm = TRUE), 2),
            SD = round(sd(Value, na.rm = TRUE), 2),
            N = dplyr::n(), .groups = "drop"))
```

### Mixed Model (Without Task, Passers Only)
```{r passers-model-1}
model_pass <- lmer(
  Value ~ Phase * Label + (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = performance_long_pass
)

model_pass_summary <- summary(model_pass)$coefficients
anova_pass <- anova(model_pass)
eta_pass <- effectsize::eta_squared(model_pass, partial = TRUE)

model_pass_summary
anova_pass
eta_pass
```

#### Post-hoc Comparisons (Passers Only)
```{r passers-posthoc-1}
posthoc_stage_pass <- emmeans(model_pass, pairwise ~ Phase)
posthoc_label_pass <- emmeans(model_pass, pairwise ~ Label)
posthoc_stage_label_pass <- emmeans(model_pass, pairwise ~ Phase | Label)
posthoc_label_stage_pass <- emmeans(model_pass, pairwise ~ Label | Phase)

cat("===Stage===\n")
posthoc_stage_pass$contrasts
cat("\n===Label===\n")
posthoc_label_pass$contrasts
cat("\n===Stage:Label===\n")
posthoc_stage_label_pass$contrasts
cat("\n===Label:Stage===\n")
posthoc_label_stage_pass$contrasts

cat("\n===Cohen's d: Stage===\n")
print(eff_size(posthoc_stage_pass, sigma = sigma(model_pass), edf = df.residual(model_pass)))
cat("\n===Cohen's d: Label===\n")
print(eff_size(posthoc_label_pass, sigma = sigma(model_pass), edf = df.residual(model_pass)))
```

#### Report and Export Results (Passers Only)
```{r passers-export-1}
report(anova_pass)

write.xlsx(
  list(
    Model_Summary = as.data.frame(model_pass_summary),
    ANOVA = as.data.frame(anova_pass),
    Eta_Squared = as.data.frame(eta_pass),
    Posthoc_Stage = as.data.frame(posthoc_stage_pass$contrasts),
    Posthoc_Label = as.data.frame(posthoc_label_pass$contrasts),
    Posthoc_Stage_Label = as.data.frame(posthoc_stage_label_pass$contrasts),
    Posthoc_Label_Stage = as.data.frame(posthoc_label_stage_pass$contrasts)
  ),
  file = "results/H1/H1_Performance_Comparison_LMM_PassersOnly.xlsx",
  rowNames = TRUE
)
```

## H1 Sensitivity: Perceived Label (As-Recalled Condition)

Complementary to the passers-only analysis, this keeps the **full sample**
but replaces the assigned `Label` with the **perceived label** each
participant recalled (`Recalled_Label`) — the more proximal cause if the
manipulation operates through what participants *believe* they received.
Passers enter under their assigned label, non-passers under the one they
believed. The primary H1 structure (without the task factor) is otherwise
unchanged.

### Attach Perceived Label
```{r perceived-data-1}
perceived_lk <- mc_df %>%
  transmute(ID = as.character(ID), PerceivedLabel = Recalled_Label)

performance_long_perc <- performance_long %>%
  mutate(ID = as.character(ID)) %>%
  left_join(perceived_lk, by = "ID") %>%
  filter(!is.na(PerceivedLabel)) %>%
  mutate(
    PerceivedLabel = factor(PerceivedLabel, levels = c("AI", "AI Human", "Human")),
    ID = factor(ID)
  ) %>%
  droplevels()

cat("Participants with a recalled label:",
    dplyr::n_distinct(performance_long_perc$ID),
    "of", dplyr::n_distinct(performance_long$ID), "\n")
print(performance_long_perc %>%
  group_by(Phase, PerceivedLabel) %>%
  summarise(Mean = round(mean(Value, na.rm = TRUE), 2),
            SD = round(sd(Value, na.rm = TRUE), 2),
            N = dplyr::n(), .groups = "drop"))
```

### Mixed Model (Without Task, Perceived Label)
```{r perceived-model-1}
model_perc <- lmer(
  Value ~ Phase * PerceivedLabel + (1 | ID) + (1 | Task) + (1 | ID:Task),
  data = performance_long_perc
)

model_perc_summary <- summary(model_perc)$coefficients
anova_perc <- anova(model_perc)
eta_perc <- effectsize::eta_squared(model_perc, partial = TRUE)

model_perc_summary
anova_perc
eta_perc
```

#### Post-hoc Comparisons (Perceived Label)
```{r perceived-posthoc-1}
posthoc_stage_perc <- emmeans(model_perc, pairwise ~ Phase)
posthoc_label_perc <- emmeans(model_perc, pairwise ~ PerceivedLabel)
posthoc_stage_label_perc <- emmeans(model_perc, pairwise ~ Phase | PerceivedLabel)
posthoc_label_stage_perc <- emmeans(model_perc, pairwise ~ PerceivedLabel | Phase)

cat("===Stage===\n")
posthoc_stage_perc$contrasts
cat("\n===Perceived Label===\n")
posthoc_label_perc$contrasts
cat("\n===Stage:Perceived Label===\n")
posthoc_stage_label_perc$contrasts
cat("\n===Perceived Label:Stage===\n")
posthoc_label_stage_perc$contrasts

cat("\n===Cohen's d: Stage===\n")
print(eff_size(posthoc_stage_perc, sigma = sigma(model_perc), edf = df.residual(model_perc)))
cat("\n===Cohen's d: Perceived Label===\n")
print(eff_size(posthoc_label_perc, sigma = sigma(model_perc), edf = df.residual(model_perc)))
```

#### Report and Export Results (Perceived Label)
```{r perceived-export-1}
report(anova_perc)

write.xlsx(
  list(
    Model_Summary = as.data.frame(model_perc_summary),
    ANOVA = as.data.frame(anova_perc),
    Eta_Squared = as.data.frame(eta_perc),
    Posthoc_Stage = as.data.frame(posthoc_stage_perc$contrasts),
    Posthoc_Label = as.data.frame(posthoc_label_perc$contrasts),
    Posthoc_Stage_Label = as.data.frame(posthoc_stage_label_perc$contrasts),
    Posthoc_Label_Stage = as.data.frame(posthoc_label_stage_perc$contrasts)
  ),
  file = "results/H1/H1_Performance_Comparison_LMM_PerceivedLabel.xlsx",
  rowNames = TRUE
)
```

## H2: Confidence, Willingness, Usefulness, Attitude Change, and Post-Survey Experience

H2 examines self-reported confidence, willingness to use AI, and
perceived usefulness across stages; change in AI attitudes from Pre to
Post; and the post-survey experience measures (perceived learning,
satisfaction, and sign-up behaviour).

### Confidence, Willingness, and Usefulness
#### Recode for Modeling
```{r recode-for-modeling-1}
df_long <- df_long %>%
  dplyr::mutate(
    Phase = factor(Phase, levels = c("Post", "stage3", "stage2", "stage1", "Pre")),
    Task = factor(task),
    Label = factor(Label),
    ID = factor(ID)
  ) %>%
  dplyr::select(-task)
```

#### Fit Models
```{r fit-models-1}
measures <- c("confidence", "willing", "useful")
result_list <- list()

# One Phase x Label LMM per self-report measure, with full post-hoc + descriptives.
for (var in measures) {
  cat(paste0("\n===", var, "===\n"))

  df_sub <- df_long %>%
    filter(
      measure == var,
      Task != "task0"
    )

  model <- lmer(
    Value ~ Phase * Label + (1 | ID) + (1 | Task) + (1 | ID:Task),
    data = df_sub
  )

  anova_res <- anova(model)
  print(anova_res)
  ANOVA <- as.data.frame(anova_res) %>%
    tibble::rownames_to_column("Variable")

  eta_sq <- effectsize::eta_squared(model, partial = TRUE)
  print(eta_sq)

  coef_tbl <- as.data.frame(summary(model)$coefficients) %>%
    tibble::rownames_to_column("Variable")

  posthoc_stage <- emmeans(model, pairwise ~ Phase)
  cat("\n===t-test: Stage===\n")
  print(posthoc_stage$contrasts)
  effsize_stage <- eff_size(posthoc_stage, sigma = sigma(model), edf = df.residual(model))
  cat("\n===Cohen's d: Stage===\n")
  print(effsize_stage)

  posthoc_label <- emmeans(model, pairwise ~ Label)
  cat("\n===t-test: Label===\n")
  print(posthoc_label$contrasts)
  effsize_label <- eff_size(posthoc_label, sigma = sigma(model), edf = df.residual(model))
  cat("\n===Cohen's d: Label===\n")
  print(effsize_label)

  posthoc_stage_label <- emmeans(model, pairwise ~ Phase | Label)
  cat("\n===t-test: Phase | Label===\n")
  print(posthoc_stage_label$contrasts)
  effsize_pl <- eff_size(
    posthoc_stage_label,
    sigma = sigma(model),
    edf = df.residual(model)
  )
  cat("\n===Cohen's d: Phase | Label===\n")
  print(effsize_pl)

  posthoc_label_stage <- emmeans(model, pairwise ~ Label | Phase)
  cat("\n===t-test: Label | Phase===\n")
  print(posthoc_label_stage$contrasts)
  effsize_lp <- eff_size(posthoc_label_stage, sigma = sigma(model), edf = df.residual(model))
  cat("\n===Cohen's d: Label | Phase===\n")
  print(effsize_lp)

  means_by_label <- df_sub %>%
    group_by(Label) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  means_by_stage <- df_sub %>%
    group_by(Phase) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  means_by_task <- df_sub %>%
    group_by(Task) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  means_by_label_stage <- df_sub %>%
    group_by(Phase, Label) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  means_by_stage_task <- df_sub %>%
    group_by(Phase, Task) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  means_by_task_label <- df_sub %>%
    group_by(Task, Label) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  means_by_stage_task_label <- df_sub %>%
    group_by(Phase, Task, Label) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = sum(!is.na(Value)),
      .groups = "drop"
    )

  result_list[[var]] <- list(
    Model_Summary = coef_tbl,
    ANOVA = ANOVA,
    Eta_Squared = as.data.frame(eta_sq),
    M_Label = means_by_label,
    M_Stage = means_by_stage,
    M_Task = means_by_task,
    M_Label_Stage = means_by_label_stage,
    M_Stage_Task = means_by_stage_task,
    M_Task_Label = means_by_task_label,
    M_Stage_Task_Label = means_by_stage_task_label,
    Posthoc_Stage = as.data.frame(posthoc_stage$contrasts),
    Posthoc_Label = as.data.frame(posthoc_label$contrasts),
    Posthoc_Stage_Label = as.data.frame(posthoc_stage_label$contrasts),
    Posthoc_Label_Stage = as.data.frame(posthoc_label_stage$contrasts)
  )
}
```

#### Export Results
```{r export-results-1}
flat_result_list <- list()

for (name in names(result_list)) {
  for (subname in names(result_list[[name]])) {
    tab <- result_list[[name]][[subname]]
    if (is.data.frame(tab)) {
      sheet_name <- paste(name, subname, sep = "_")
      flat_result_list[[sheet_name]] <- tab
    }
  }
}

write.xlsx(
  flat_result_list,
  file = "results/H2/H2_Within_Task_Attitude_Perceptions.xlsx"
)
```

### Attitude Change Over Time
```{r attitude-change-over-time-1}
measures <- c("AI_Trust", "AI_Usefulness", "AI_Affect", "Behavioral_Intention")

change_stats <- list()
anova_results <- list()
eta_squared_results <- list()
posthoc_results <- list()
posthoc_results_PL <- list()
posthoc_results_LP <- list()
```

#### Compute Change Scores, Fit Mixed Models
```{r compute-change-scores-fit-mixed-models-1}
# Pre->Post change per attitude measure: descriptives, change score, and a
# Phase x Label LMM with post-hoc contrasts.
for (msr in measures) {
  cat(paste0("\n===", msr, "===\n"))

  d_sub <- df_long %>%
    filter(measure == msr, Phase %in% c("Pre", "Post"))

  stat_tab_0 <- d_sub %>%
    dplyr::select(ID, Label, Phase, Value, measure) %>%
    group_by(Label, Phase, measure) %>%
    summarise(
      Mean = round(mean(Value, na.rm = TRUE), 2),
      SD = round(sd(Value, na.rm = TRUE), 2),
      N = n(),
      .groups = "drop"
    )

  d_wide <- d_sub %>%
    dplyr::select(ID, Label, Phase, Value) %>%
    pivot_wider(names_from = Phase, values_from = Value) %>%
    mutate(change = Post - Pre)

  stat_tab <- d_wide %>%
    group_by(Label) %>%
    summarise(
      MeanChange = round(mean(change, na.rm = TRUE), 2),
      SD = round(sd(change, na.rm = TRUE), 2),
      N = n(),
      .groups = "drop"
    ) %>%
    mutate(Measure = msr) %>%
    relocate(Measure)

  change_stats[[msr]] <- stat_tab

  d_mod <- d_sub %>%
    filter(!is.na(Value)) %>%
    mutate(
      Phase = factor(Phase, levels = c("Post", "Pre")),
      Phase = relevel(as.factor(Phase), ref = "Post")
    )

  if (nrow(d_mod) > 0) {
    model <- lmer(Value ~ Phase * Label + (1 | ID), data = d_mod)

    aov_tab <- anova(model)
    print(aov_tab)

    eta <- eta_squared(model, partial = TRUE)
    print(eta)
    cat("\n")

    posthoc <- emmeans(model, pairwise ~ Phase)
    cat("\n===t-test: Phase===\n")
    print(posthoc$contrasts)
    cat("\n===Cohen's d: Phase===\n")
    print(eff_size(posthoc, sigma = sigma(model), edf = df.residual(model)))

    posthoc_PL <- emmeans(model, pairwise ~ Phase | Label)
    cat("\n===t-test: Phase | Label===\n")
    print(posthoc_PL$contrasts)
    cat("\n===Cohen's d: Phase | Label===\n")
    print(eff_size(posthoc_PL, sigma = sigma(model), edf = df.residual(model)))

    posthoc_LP <- emmeans(model, pairwise ~ Label | Phase)
    cat("\n===t-test: Label | Phase===\n")
    print(posthoc_LP$contrasts)
    cat("\n===Cohen's d: Label | Phase===\n")
    print(eff_size(posthoc_LP, sigma = sigma(model), edf = df.residual(model)))

    anova_results[[msr]] <- as.data.frame(aov_tab) %>%
      tibble::rownames_to_column("Effect") %>%
      mutate(Measure = msr, .before = 1)

    eta_squared_results[[msr]] <- as.data.frame(eta) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results[[msr]] <- as.data.frame(posthoc$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_PL[[msr]] <- as.data.frame(posthoc_PL$contrasts) %>%
      mutate(Measure = msr, .before = 1)

    posthoc_results_LP[[msr]] <- as.data.frame(posthoc_LP$contrasts) %>%
      mutate(Measure = msr, .before = 1)
  }
}
```

#### Export Results
```{r export-results-2}
final_output_list <- list(
  ChangeScore_Summary   = bind_rows(change_stats),
  ANOVA_Results         = bind_rows(anova_results),
  Eta_Squared_Results   = bind_rows(eta_squared_results),
  Posthoc_Results       = bind_rows(posthoc_results),
  Posthoc_PL_Results    = bind_rows(posthoc_results_PL),
  Posthoc_LP_Results    = bind_rows(posthoc_results_LP)
)

write.xlsx(
  final_output_list,
  file = "results/H2/H2_Attitude_Change_Immediate_Results.xlsx",
  overwrite = TRUE
)
```

### Post-Survey Experience & Sign-Up
#### Perceived Learning
```{r perceived-learning-1}
anova_learning <- aov(Stats_Improvement ~ Label, data = df)

means_learning <- df %>%
  group_by(Label) %>%
  summarise(
    Mean = round(mean(Stats_Improvement, na.rm = TRUE), 2),
    SD = round(sd(Stats_Improvement, na.rm = TRUE), 2),
    N = n(),
    .groups = "drop"
  )

eta2 <- etaSquared(anova_learning, type = 2)

posthoc_learning <- as.data.frame(
  emmeans(anova_learning, pairwise ~ Label)$contrasts
)

print(anova_learning)
print(eta2)
print(posthoc_learning)
```

#### Satisfaction
```{r satisfaction-1}
df$Satisfaction <- as.ordered(df$Satisfaction)
satis_model <- MASS::polr(Satisfaction ~ Label, data = df, Hess = TRUE)

summary(satis_model)

satis_aov <- Anova(satis_model)
print(satis_aov)

emmeans_satis <- emmeans(satis_model, pairwise ~ Label)
posthoc_satis <- as.data.frame(emmeans_satis$contrasts)

means_satis <- df %>%
  group_by(Label) %>%
  summarise(
    Mean = round(mean(as.numeric(Satisfaction), na.rm = TRUE), 2),
    SD = round(sd(as.numeric(Satisfaction), na.rm = TRUE), 2),
    Median = median(as.numeric(Satisfaction), na.rm = TRUE),
    N = n(),
    .groups = "drop"
  )
```

#### Sign-Up Behavior
```{r sign-up-behavior-1}
logit_model <- glm(Sign_Up ~ Label, data = df, family = binomial)

summary(logit_model)

odds_ci <- exp(cbind(OR = coef(logit_model), confint(logit_model)))

table_signup <- table(df$Label, df$Sign_Up)
chisq_test <- chisq.test(table_signup)

print(chisq_test)

cramers_v <- sqrt(
  chisq_test$statistic / (sum(table_signup) * (min(dim(table_signup)) - 1))
)
```

#### Export Results
```{r export-results-3}
write.xlsx(
  list(
    Learning_ANOVA        = as.data.frame(summary(anova_learning)[[1]]),
    Learning_Means        = means_learning,
    Learning_Eta2         = as.data.frame(eta2),
    Learning_Posthoc      = posthoc_learning,
    Satisfaction_Means    = means_satis,
    Satisfaction_Model    = tidy(satis_model),
    Satisfaction_Posthoc  = posthoc_satis,
    SignUp_Table          = as.data.frame(table_signup),
    SignUp_Logit_Summary  = tidy(logit_model),
    SignUp_Odds_CI        = as.data.frame(odds_ci),
    SignUp_ChiSq          = tidy(chisq_test),
    SignUp_CramersV       = data.frame(CramersV = as.numeric(cramers_v))
  ),
  file = "results/H2/Post_Survey_Experience.xlsx",
  rowNames = TRUE
)
```

## H3: Moderation of Initial-Session Outcomes

H3 screens whether individual-difference measures (objective/subjective
literacy, AI attitudes, statistics background, and LLM usage) moderate
the initial-session effects on performance/confidence/willingness/
usefulness and on attitude change (Pre → Post). Significant terms are
summarised per outcome.

### Accuracy, Confidence, Willingness, and Usefulness Moderation
```{r accuracy-confidence-willingness-and-usefulness-moderation-1}
moderators_raw <- c(
  "GLAT_Objective_AI_Literacy",
  "AILS_CCS_Subjective_AI_Literacy",
  "AI_Trust",
  "AI_Usefulness",
  "AI_Affect",
  "AI_Self_Efficacy",
  "Behavioral_Intention"
)

outcomes <- c("accuracy", "confidence", "willing", "useful")

df_mods <- df_long %>%
  filter(tolower(Phase) == "pre", measure %in% moderators_raw) %>%
  dplyr::select(ID, measure, Value) %>%
  pivot_wider(names_from = measure, names_prefix = "pre_", values_from = Value)

df_wide <- df_long %>%
  filter(measure %in% outcomes) %>%
  left_join(df_mods, by = "ID") %>%
  mutate(
    Stage = as.factor(Phase),
    Task  = as.factor(Task),
    Label = as.factor(Label),
    ID    = as.factor(ID)
  ) %>%
  dplyr::select(-Phase)
```

```{r accuracy-confidence-willingness-and-usefulness-moderation-2}
moderators <- c(
  "pre_GLAT_Objective_AI_Literacy",
  "pre_AILS_CCS_Subjective_AI_Literacy",
  "pre_AI_Trust",
  "pre_AI_Usefulness",
  "pre_AI_Affect",
  "pre_AI_Self_Efficacy",
  "pre_Behavioral_Intention",
  "Stats_Background",
  "Used_LLM_Frequency",
  "Used_LLM_Hours"
)

categorical_mods <- c("Stats_Background", "Used_LLM_Frequency", "Used_LLM_Hours")

result_list <- list()
```

#### Fit Mixed Models + ANOVA + Eta + Coefs + Post-hoc (Conditional)
```{r fit-mixed-models-anova-eta-coefs-1}
# Loop over every outcome x moderator pair; fit a 3-way moderation LMM each.
for (outcome in outcomes) {
  for (mod in moderators) {
    # Mean-center continuous (pre_) moderators so main effects stay interpretable.
    if (grepl("^pre_", mod)) {
      df_wide[[mod]] <- scale(df_wide[[mod]], scale = FALSE)
    }

    # This outcome only; drop baseline task0 and rows missing the moderator.
    df_task0 <- df_wide %>%
      filter(
        measure == outcome,
        Task != "task0",
        !is.na(.data[[mod]])
      )

    if (nrow(df_task0) == 0) next

    # Stage x Label x moderator, crossed ID/Task random effects.
    formula0 <- as.formula(
      paste0("Value ~ Stage * Label * ", mod, " + (1|ID) + (1|Task) + (1|ID:Task)")
    )

    model0 <- lmer(formula0, data = df_task0)

    anova0 <- anova(model0)
    cat(paste0("\n===", outcome, "+", mod, "===\n"))
    print(anova0)
    # Move term names into a column so they survive the xlsx export.
    ANOVA <- as.data.frame(anova0)
    ANOVA$Variable <- rownames(ANOVA)
    ANOVA <- ANOVA[, c("Variable", setdiff(names(ANOVA), "Variable"))]

    eta0 <- as.data.frame(eta_squared(model0, partial = TRUE))

    coef_tbl <- as.data.frame(summary(model0)$coefficients)
    coef_tbl$Variable <- rownames(coef_tbl)
    coef_tbl <- coef_tbl[, c("Variable", setdiff(names(coef_tbl), "Variable"))]

    posthoc_list <- list()

    # Follow up only the ANOVA terms that reached p < .05.
    sig_terms <- rownames(ANOVA)[which(ANOVA$`Pr(>F)` < 0.05)]

    for (term in sig_terms) {
      clean_term <- gsub("[:/\\?\\*\\[\\]]", "_", term)  # sanitize for list/sheet names
      term_vars <- unlist(strsplit(term, ":"))           # factors making up this term

      # Case 1: term involves a categorical moderator -> estimated means + pairwise.
      if (mod %in% categorical_mods && any(term_vars %in% c(mod, "ModeratorScore", mod))) {
        by_vars <- setdiff(term_vars, c(mod, "ModeratorScore"))
        specs <- c(mod, by_vars)

        em_out <- tryCatch(
          emmeans(model0, specs = specs),
          error = function(e) NULL
        )

        if (!is.null(em_out)) {
          posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
        }
      } else if (!(mod %in% categorical_mods) && any(term_vars %in% c(mod, "ModeratorScore", mod))) {
        # Case 2: term involves a continuous moderator -> simple slopes (emtrends).
        other_facs <- setdiff(term_vars, c(mod, "ModeratorScore"))

        # No other factor -> single overall slope; else slope per factor cell.
        if (length(other_facs) == 0) {
          specs <- ~1
        } else {
          specs <- as.formula(paste0("~", paste(other_facs, collapse = "*")))
        }

        et <- tryCatch(
          emtrends(
            model0,
            specs = specs,
            var = ifelse("ModeratorScore" %in% term_vars, "ModeratorScore", mod),
            infer = c(TRUE, TRUE)
          ),
          error = function(e) NULL
        )

        if (!is.null(et)) {
          posthoc_list[[paste0(clean_term, "_trends")]] <-
            as.data.frame(summary(et, infer = c(TRUE, TRUE)))

          # Slopes differ across factor cells -> also test slope differences.
          if (length(other_facs) > 0) {
            ph_pair <- tryCatch(as.data.frame(pairs(et)), error = function(e) NULL)
            if (!is.null(ph_pair)) {
              posthoc_list[[paste0(clean_term, "_trends_pairs")]] <- ph_pair
            }
          }
        }
      } else if (length(term_vars) > 0) {
        # Case 3: term has no moderator (e.g. Stage:Label) -> plain pairwise.
        em_out <- tryCatch(
          emmeans(model0, specs = term_vars),
          error = function(e) NULL
        )

        if (!is.null(em_out)) {
          posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
        }
      }
    }

    result_list[[paste0(outcome, "_by_", mod)]] <- list(
      Formula      = as.character(formula0),
      ANOVA        = ANOVA,
      Eta_Squared  = eta0,
      Coef_Summary = coef_tbl,
      Posthoc      = posthoc_list
    )
  }
}
```

#### Export Results
```{r export-results-4}
mod_abbr <- c(
  "pre_GLAT_Objective_AI_Literacy"       = "GLAT",
  "pre_AILS_CCS_Subjective_AI_Literacy"  = "AILSCCS",
  "pre_AI_Trust"                         = "Trust",
  "pre_AI_Usefulness"                    = "Useful",
  "pre_AI_Affect"                        = "Affect",
  "pre_AI_Self_Efficacy"                 = "SelfEff",
  "pre_Behavioral_Intention"             = "BehInt",
  "Stats_Background"                     = "StatsBG",
  "Used_LLM_Frequency"                   = "LLMFreq",
  "Used_LLM_Hours"                       = "LLMHr"
)

flat_result_list <- list()

# Flatten the nested result_list into one sheet per table, with short names
# (Excel caps sheet names at 31 chars).
for (nm in names(result_list)) {
  key_base <- strsplit(nm, "_")[[1]]
  outcome_letter <- substr(key_base[1], 1, 1)  # outcome -> single letter

  # Rebuild the moderator name (it spans key_base[4:]) and abbreviate it.
  moderator <- paste(key_base[4:length(key_base)], collapse = "_")
  mod_short <- ifelse(
    moderator %in% names(mod_abbr),
    mod_abbr[[moderator]],
    substr(moderator, 1, 8)
  )

  prefix <- paste(outcome_letter, mod_short, sep = "_")

  flat_result_list[[paste0(prefix, "_ANOVA")]] <- result_list[[nm]]$ANOVA
  flat_result_list[[paste0(prefix, "_EtaSq")]] <- result_list[[nm]]$Eta_Squared
  flat_result_list[[paste0(prefix, "_Coef")]] <- result_list[[nm]]$Coef_Summary

  # One extra sheet per non-empty post-hoc table.
  if (!is.null(result_list[[nm]]$Posthoc)) {
    for (int_type in names(result_list[[nm]]$Posthoc)) {
      ph <- result_list[[nm]]$Posthoc[[int_type]]
      if (!is.null(ph) && is.data.frame(ph) && nrow(ph) > 0) {
        flat_result_list[[paste0(prefix, "*PH*", substr(int_type, 1, 8))]] <- ph
      }
    }
  }
}

names(flat_result_list) <- gsub(":", "_", names(flat_result_list))  # ":" illegal in sheet names

write.xlsx(
  flat_result_list,
  file = "results/H3/H3_Within_Task_Moderation_ALL_Posthoc.xlsx"
)
```

#### Export Significant Effects Summary
```{r export-significant-effects-summary-1}
# Collapse every model's ANOVA into one flat summary table and write it out.
export_sig_effects <- function(
  result_list,
  out_excel_path
) {
  if (!dir.exists(dirname(out_excel_path))) {
    dir.create(dirname(out_excel_path), recursive = TRUE)
  }

  summary_sig_effects <- data.frame(
    DV = character(),
    Moderator = character(),
    Term = character(),
    NumDF = numeric(),
    DenDF = numeric(),
    F_value = numeric(),
    p_value = numeric(),
    eta_p = numeric(),
    stringsAsFactors = FALSE
  )

  for (res_name in names(result_list)) {
    split_name <- unlist(strsplit(res_name, "_by_"))
    DV <- split_name[1]
    Moderator <- split_name[2]

    ANOVA <- result_list[[res_name]]$ANOVA
    Eta <- result_list[[res_name]]$Eta_Squared

    if (is.null(ANOVA)) next
    if (!all(c("Pr(>F)", "F value") %in% names(ANOVA))) next

    # Keep every term: the p-value adjudication step builds the correction
    # family downstream and needs all focal interactions, significant or not.
    sig_rows <- which(ANOVA$`Pr(>F)` <= 1)
    if (length(sig_rows) == 0) next

    for (i in sig_rows) {
      this_term <- ANOVA$Variable[i]
      Ndf <- ANOVA$NumDF[i]
      Ddf <- ANOVA$DenDF[i]
      Fval <- ANOVA$`F value`[i]
      pval <- ANOVA$`Pr(>F)`[i]

      eta_val <- NA
      if (!is.null(Eta) && "Parameter" %in% names(Eta)) {
        eta_row <- Eta[Eta$Parameter == this_term, , drop = FALSE]
        if (nrow(eta_row) == 1) {
          if ("Eta2_partial" %in% names(eta_row)) eta_val <- eta_row$Eta2_partial
          if ("Eta2" %in% names(eta_row) && is.na(eta_val)) eta_val <- eta_row$Eta2
        }
      }

      summary_sig_effects <- rbind(
        summary_sig_effects,
        data.frame(
          DV = DV,
          Moderator = Moderator,
          Term = this_term,
          NumDF = Ndf,
          DenDF = Ddf,
          F_value = Fval,
          p_value = pval,
          eta_p = eta_val,
          stringsAsFactors = FALSE
        )
      )
    }
  }

  summary_sig_effects <- summary_sig_effects %>%
    arrange(DV, Moderator, p_value)

  write.xlsx(summary_sig_effects, file = out_excel_path, rowNames = FALSE)

  cat(sprintf("Significant terms summary saved to %s\n", out_excel_path))

  invisible(summary_sig_effects)
}
```

```{r export-significant-effects-summary-2}
export_sig_effects(
  result_list,
  out_excel_path = "results/H3/H3_Within_Task_Moderation_Summary.xlsx"
)
```

### Attitude Change Immediate Moderation
```{r attitude-change-immediate-moderation-1}
outcomes <- c("AI_Trust", "AI_Usefulness", "AI_Affect", "Behavioral_Intention")

moderators <- c(
  "GLAT_Objective_AI_Literacy",
  "AILS_CCS_Subjective_AI_Literacy",
  "AI_Trust",
  "AI_Usefulness",
  "AI_Affect",
  "AI_Self_Efficacy",
  "Behavioral_Intention",
  "Stats_Background",
  "Used_LLM_Frequency",
  "Used_LLM_Hours"
)

categorical_mods <- c("Stats_Background", "Used_LLM_Frequency", "Used_LLM_Hours")

result_list <- list()
```

#### Fit Models for Attitude Change (Pre/Post) with Moderation + Post-hoc
```{r fit-models-for-attitude-change-pre-1}
for (outcome in outcomes) {
  for (mod in moderators) {
    df_sub <- df_long %>%
      filter(measure == outcome, Phase %in% c("Pre", "Post"))

    if (nrow(df_sub) == 0) next

    df_sub <- df_sub %>%
      mutate(
        Phase = factor(Phase, levels = c("Pre", "Post")),
        Label = as.factor(Label),
        ID    = as.factor(ID)
      )

    posthoc_list <- list()

    # Three ways to bring in the moderator, depending on what it is:
    if (mod == outcome) {
      # (a) Moderator IS the outcome -> can't moderate itself; instead control
      #     for its own Pre score as a baseline covariate (no interaction).
      baseline_df <- df_sub %>%
        filter(Phase == "Pre") %>%
        dplyr::select(ID, BaselineScore = Value)

      df_sub <- df_sub %>%
        left_join(baseline_df, by = "ID") %>%
        mutate(BaselineScore = scale(BaselineScore, scale = FALSE))

      formula_str <- "Value ~ Phase * Label + BaselineScore + (1|ID)"
      model <- lmer(as.formula(formula_str), data = df_sub)
    } else if (mod %in% df_long$measure) {
      # (b) Moderator is another measured scale -> attach its Pre score (centered).
      mod_df <- df_long %>%
        filter(Phase == "Pre", measure == mod) %>%
        dplyr::select(ID, ModeratorScore = Value)

      df_sub <- df_sub %>%
        left_join(mod_df, by = "ID") %>%
        mutate(ModeratorScore = scale(ModeratorScore, scale = FALSE))

      formula_str <- "Value ~ Phase * Label * ModeratorScore + (1|ID)"
      model <- lmer(as.formula(formula_str), data = df_sub)
    } else {
      # (c) Moderator is a fixed demographic column -> use it as-is.
      df_sub <- df_sub %>%
        mutate(ModeratorScore = .data[[mod]])

      formula_str <- "Value ~ Phase * Label * ModeratorScore + (1|ID)"
      model <- lmer(as.formula(formula_str), data = df_sub)
    }

    anova_res <- anova(model)
    cat(paste0("\n===", outcome, "+", mod, "===\n"))
    print(anova_res)
    ANOVA <- as.data.frame(anova_res)
    ANOVA$Variable <- rownames(ANOVA)
    ANOVA <- ANOVA[, c("Variable", setdiff(names(ANOVA), "Variable"))]

    eta_sq <- effectsize::eta_squared(model, partial = TRUE)

    coef_tbl <- as.data.frame(summary(model)$coefficients)
    coef_tbl$Variable <- rownames(coef_tbl)
    coef_tbl <- coef_tbl[, c("Variable", setdiff(names(coef_tbl), "Variable"))]

    sig_terms <- rownames(ANOVA)[which(ANOVA$`Pr(>F)` < 0.05)]

    for (term in sig_terms) {
      clean_term <- gsub("[:/\\?\\*\\[\\]]", "_", term)   # sanitize for list names
      term_vars <- unlist(strsplit(term, ":"))            # factors in this term
      left_facs <- setdiff(term_vars, c(mod, "ModeratorScore"))  # the non-moderator ones

      # Case 1: categorical moderator -> Label contrasts within moderator levels.
      if (mod %in% categorical_mods && any(term_vars %in% c(mod, "ModeratorScore", mod))) {
        ph_em <- tryCatch(
          emmeans(model, pairwise ~ Label | ModeratorScore),
          error = function(e) NULL
        )

        if (!is.null(ph_em)) {
          posthoc_list[[clean_term]] <- as.data.frame(ph_em$contrasts)
        }
      } else if (!(mod %in% categorical_mods) && any(term_vars %in% c(mod, "ModeratorScore", mod))) {
        # Case 2: continuous moderator -> simple slopes, per factor cell if any.
        if (length(left_facs) == 0) {
          specs <- ~1
        } else {
          specs <- as.formula(paste0("~", paste(left_facs, collapse = "*")))
        }

        et <- tryCatch(
          emtrends(
            model,
            specs = specs,
            var = ifelse("ModeratorScore" %in% term_vars, "ModeratorScore", mod),
            infer = c(TRUE, TRUE)
          ),
          error = function(e) NULL
        )

        if (!is.null(et)) {
          posthoc_list[[paste0(clean_term, "_trends")]] <-
            as.data.frame(summary(et, infer = c(TRUE, TRUE)))

          # Also test whether slopes differ across the factor cells.
          if (length(left_facs) > 0) {
            ph_pair <- tryCatch(as.data.frame(pairs(et)), error = function(e) NULL)
            if (!is.null(ph_pair)) {
              posthoc_list[[paste0(clean_term, "_trends_pairs")]] <- ph_pair
            }
          }
        }
      } else if (length(term_vars) > 1) {
        # Case 3a: multi-factor term without moderator (e.g. Phase:Label) -> pairwise.
        em_formula <- as.formula(paste0("~", paste(term_vars, collapse = " * ")))
        em_out <- tryCatch(emmeans(model, em_formula), error = function(e) NULL)

        if (!is.null(em_out)) {
          posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
        }
      } else if (length(term_vars) == 1) {
        # Case 3b: single-factor main effect -> pairwise on that factor.
        em_formula <- as.formula(paste0("~", term))
        em_out <- tryCatch(emmeans(model, em_formula), error = function(e) NULL)

        if (!is.null(em_out)) {
          posthoc_list[[clean_term]] <- as.data.frame(pairs(em_out))
        }
      }
    }

    result_list[[paste0(outcome, "_by_", mod)]] <- list(
      Formula      = formula_str,
      ANOVA        = ANOVA,
      Eta_Squared  = as.data.frame(eta_sq),
      Coef_Summary = coef_tbl,
      Posthoc      = posthoc_list
    )
  }
}
```

####  Export Results
```{r export-results-5}
clean_sheet <- function(x) gsub("[:/\\?\\*\\[\\] ]", "_", substr(x, 1, 31))

mod_abbr <- c(
  "GLAT_Objective_AI_Literacy"          = "GLAT",
  "AILS_CCS_Subjective_AI_Literacy"     = "AILSCCS",
  "AI_Trust"                            = "Trust",
  "AI_Usefulness"                       = "Useful",
  "AI_Affect"                           = "Affect",
  "AI_Self_Efficacy"                    = "SelfEff",
  "Behavioral_Intention"                = "BehInt",
  "Stats_Background"                    = "StatsBG",
  "Used_LLM_Frequency"                  = "LLMFreq",
  "Used_LLM_Hours"                      = "LLMHr"
)

flat_result_list <- list()

for (nm in names(result_list)) {
  key_base <- strsplit(nm, "_")[[1]]
  outcome_short <- substr(key_base[2], 1, 5)

  moderator <- paste(key_base[4:length(key_base)], collapse = "_")
  mod_short <- ifelse(
    moderator %in% names(mod_abbr),
    mod_abbr[[moderator]],
    substr(moderator, 1, 8)
  )

  prefix <- paste(outcome_short, mod_short, sep = "_")

  flat_result_list[[clean_sheet(paste0(prefix, "_ANOVA"))]] <- result_list[[nm]]$ANOVA
  flat_result_list[[clean_sheet(paste0(prefix, "_EtaSq"))]] <- result_list[[nm]]$Eta_Squared
  flat_result_list[[clean_sheet(paste0(prefix, "_Coef"))]] <- result_list[[nm]]$Coef_Summary

  if (!is.null(result_list[[nm]]$Posthoc)) {
    for (int_type in names(result_list[[nm]]$Posthoc)) {
      ph <- result_list[[nm]]$Posthoc[[int_type]]
      if (!is.null(ph) && is.data.frame(ph) && nrow(ph) > 0) {
        flat_result_list[[clean_sheet(paste0(prefix, "*Posthoc*", int_type))]] <- ph
      }
    }
  }
}

names(flat_result_list) <- gsub(":", "_", names(flat_result_list))

write.xlsx(
  flat_result_list,
  file = "results/H3/H3_Attitude_Change_Immediate_Moderation_POSTHOC.xlsx"
)
```

#### Export Significant Effects Summary
```{r export-significant-effects-summary-3}
# Same as above (keeps every term; focal filtering happens in p-value adjudication).
export_sig_effects <- function(result_list, out_excel_path) {
  if (!dir.exists(dirname(out_excel_path))) {
    dir.create(dirname(out_excel_path), recursive = TRUE)
  }

  summary_sig_effects <- data.frame(
    DV = character(),
    Moderator = character(),
    Term = character(),
    NumDF = numeric(),
    DenDF = numeric(),
    F_value = numeric(),
    p_value = numeric(),
    eta_p = numeric(),
    stringsAsFactors = FALSE
  )

  for (res_name in names(result_list)) {
    split_name <- unlist(strsplit(res_name, "_by_"))
    DV <- split_name[1]
    Moderator <- split_name[2]

    ANOVA <- result_list[[res_name]]$ANOVA
    Eta <- result_list[[res_name]]$Eta_Squared

    if (is.null(ANOVA)) next
    if (!all(c("Pr(>F)", "F value") %in% names(ANOVA))) next

    # Keep every term (see note in the within-task version above): the adjudication
    # step needs the full set of focal interactions to build the correction family.
    sig_rows <- which(ANOVA$`Pr(>F)` <= 1)
    if (length(sig_rows) == 0) next

    for (i in sig_rows) {
      this_term <- ANOVA$Variable[i]
      Ndf <- ANOVA$NumDF[i]
      Ddf <- ANOVA$DenDF[i]
      Fval <- ANOVA$`F value`[i]
      pval <- ANOVA$`Pr(>F)`[i]

      eta_val <- NA
      if (!is.null(Eta) && "Parameter" %in% names(Eta)) {
        eta_row <- Eta[Eta$Parameter == this_term, , drop = FALSE]
        if (nrow(eta_row) == 1) {
          if ("Eta2_partial" %in% names(eta_row)) eta_val <- eta_row$Eta2_partial
          if ("Eta2" %in% names(eta_row) && is.na(eta_val)) eta_val <- eta_row$Eta2
        }
      }

      summary_sig_effects <- rbind(
        summary_sig_effects,
        data.frame(
          DV = DV,
          Moderator = Moderator,
          Term = this_term,
          NumDF = Ndf,
          DenDF = Ddf,
          F_value = Fval,
          p_value = pval,
          eta_p = eta_val,
          stringsAsFactors = FALSE
        )
      )
    }
  }

  summary_sig_effects <- summary_sig_effects %>%
    dplyr::arrange(DV, Moderator, p_value)

  write.xlsx(summary_sig_effects, file = out_excel_path, rowNames = FALSE)

  cat(sprintf("Significant terms summary saved to %s\n", out_excel_path))

  invisible(summary_sig_effects)
}

export_sig_effects(
  result_list,
  out_excel_path = "results/H3/H3_Attitude_Change_Moderation_Summary.xlsx"
)
```

### Post Survey Experience
#### Continuous Moderation Effects
```{r continous-moderation-effects-1}
moderators <- c(
  "Pre_GLAT_Objective_AI_Literacy",
  "Pre_AILS_CCS_Subjective_AI_Literacy",
  "Pre_AI_Trust",
  "Pre_AI_Usefulness",
  "Pre_AI_Affect",
  "Pre_AI_Self_Efficacy",
  "Pre_Behavioral_Intention"
)

df$Satisfaction <- as.factor(df$Satisfaction)

result_list <- list()
```

```{r continous-moderation-effects-2}
# Each continuous moderator x 3 post-survey outcomes (learning, satisfaction, sign-up).
for (mod in moderators) {
  df[[mod]] <- as.numeric(df[[mod]])

  # Mean-center the pre-measure moderators.
  if (grepl("^Pre_", mod)) {
    df[[mod]] <- scale(df[[mod]], scale = FALSE)
  }

  means_learning_mod <- df %>%
    group_by(Label) %>%
    summarise(
      Mean = round(mean(Stats_Improvement, na.rm = TRUE), 2),
      SD = round(sd(Stats_Improvement, na.rm = TRUE), 2),
      N = n(),
      .groups = "drop"
    )

  # Outcome 1: perceived learning (ANOVA).
  formula_learning <- paste0("Stats_Improvement ~ Label * ", mod)
  cat("\n===", "Stats Improvement +", mod, "===\n")
  anova_mod <- aov(as.formula(formula_learning), data = df)
  print(summary(anova_mod))

  anova_tbl <- as.data.frame(summary(anova_mod)[[1]])
  anova_tbl$Variable <- rownames(anova_tbl)
  anova_tbl <- anova_tbl[, c("Variable", setdiff(names(anova_tbl), "Variable"))]

  eta2_mod <- etaSquared(anova_mod, type = 2)

  # Label contrasts evaluated at the moderator's mean.
  mean_mod <- mean(df[[mod]], na.rm = TRUE)
  posthoc_learning_mod <- tryCatch(
    as.data.frame(
      emmeans(anova_mod, pairwise ~ Label, at = setNames(list(mean_mod), mod))$contrasts
    ),
    error = function(e) data.frame()
  )

  # Outcome 2: satisfaction (ordinal logistic / polr).
  formula_satis <- paste0("Satisfaction ~ Label * ", mod)
  cat("\n===", "Satisfaction +", mod, "===\n")
  satis_model_mod <- MASS::polr(as.formula(formula_satis), data = df, Hess = TRUE)

  satis_aov <- Anova(satis_model_mod)
  print(satis_aov)

  # polr gives no p-values; derive them from the t (Wald z) values.
  coefs <- summary(satis_model_mod)$coefficients
  pvals <- 2 * pnorm(-abs(coefs[, "t value"]))
  Satisfaction_Coefficients <- as.data.frame(cbind(coefs, "p value" = pvals))

  posthoc_satis_mod <- tryCatch(
    {
      em_obj <- emmeans(
        satis_model_mod,
        pairwise ~ Label,
        at = setNames(list(mean_mod), mod)
      )
      as.data.frame(em_obj$contrasts)
    },
    error = function(e) data.frame()
  )

  means_satis <- df %>%
    group_by(Label) %>%
    summarise(
      Mean = round(mean(as.numeric(Satisfaction), na.rm = TRUE), 2),
      SD = round(sd(as.numeric(Satisfaction), na.rm = TRUE), 2),
      Median = median(as.numeric(Satisfaction), na.rm = TRUE),
      N = n(),
      .groups = "drop"
    )

  # Outcome 3: sign-up (logistic regression + chi-square / Cramer's V).
  formula_signup <- paste0("Sign_Up ~ Label * ", mod)
  cat("\n===", "Sign Up +", mod, "===\n")
  logit_model_mod <- glm(as.formula(formula_signup), data = df, family = binomial)

  odds_ci_mod <- exp(cbind(OR = coef(logit_model_mod), confint(logit_model_mod)))

  table_signup <- table(df$Label, df$Sign_Up)
  chisq_test <- chisq.test(table_signup)
  print(chisq_test)

  cramers_v <- sqrt(
    chisq_test$statistic / (sum(table_signup) * (min(dim(table_signup)) - 1))
  )

  emm <- emmeans(logit_model_mod, ~Label, type = "response")
  contrast_table <- as.data.frame(pairs(emm, adjust = "tukey"))

  result_list[[mod]] <- list(
    Learning_ANOVA = anova_tbl,
    Learning_Eta2 = as.data.frame(eta2_mod),
    Learning_Posthoc = posthoc_learning_mod,
    Learning_Means = means_learning_mod,
    Satisfaction_Coefs = Satisfaction_Coefficients,
    Satisfaction_AOV = as.data.frame(satis_aov),
    Satisfaction_Posthoc = posthoc_satis_mod,
    Satisfaction_Means = means_satis,
    SignUp_Logit_Coefs = as.data.frame(summary(logit_model_mod)$coefficients),
    SignUp_Odds_CI = as.data.frame(odds_ci_mod),
    SignUp_ChiSq = data.frame(
      statistic = as.numeric(chisq_test$statistic),
      parameter = as.numeric(chisq_test$parameter),
      p.value   = as.numeric(chisq_test$p.value)
    ),
    SignUp_CramersV = data.frame(CramersV = as.numeric(cramers_v)),
    SignUp_Posthoc_Tukey = contrast_table
  )
}
```

##### Export Results
```{r export-results-6}
clean_sheet <- function(x) gsub("[:/\\?\\*\\[\\] ]", "_", substr(x, 1, 31))

flat_result_list <- list()

for (mod in names(result_list)) {
  for (nm in names(result_list[[mod]])) {
    sheet_nm <- clean_sheet(paste(substr(mod, 1, 15), substr(nm, 1, 15), sep = "_"))
    flat_result_list[[sheet_nm]] <- result_list[[mod]][[nm]]
  }
}

write.xlsx(
  flat_result_list,
  file = "results/H3/Post_Survey_Moderation_Results.xlsx",
  rowNames = TRUE
)
```

#### Categorical Moderation Effects
```{r categorical-moderation-effects-1}
moderators <- c("Stats_Background", "Used_LLM_Frequency", "Used_LLM_Hours")

df <- df %>%
  mutate(
    Stats_Background   = as.factor(Stats_Background),
    Used_LLM_Frequency = as.factor(Used_LLM_Frequency),
    Used_LLM_Hours     = as.factor(Used_LLM_Hours),
    Satisfaction       = as.factor(Satisfaction)
  )

result_list <- list()
```

```{r categorical-moderation-effects-2}
# Each categorical moderator x 3 post-survey outcomes (learning, satisfaction, sign-up).
for (mod in moderators) {
  # Outcome 1: perceived learning (ANOVA).
  formula_anova <- as.formula(paste0("Stats_Improvement ~ Label * ", mod))
  cat("\n===", "Stats Improvement +", mod, "===\n")
  anova_mod <- aov(formula_anova, data = df)
  print(summary(anova_mod))

  anova_tbl <- as.data.frame(summary(anova_mod)[[1]])
  anova_tbl$Variable <- rownames(anova_tbl)
  anova_tbl <- anova_tbl[, c("Variable", setdiff(names(anova_tbl), "Variable"))]

  means_learning_mod <- df %>%
    group_by(Label, !!sym(mod)) %>%
    summarise(
      Mean = round(mean(Stats_Improvement, na.rm = TRUE), 2),
      SD = round(sd(Stats_Improvement, na.rm = TRUE), 2),
      N = n(),
      .groups = "drop"
    )

  emm_formula_interaction <- as.formula(paste("pairwise ~ Label *", mod))

  posthoc_learning_mod <- tryCatch(
    as.data.frame(emmeans(anova_mod, emm_formula_interaction)),
    error = function(e) data.frame()
  )

  # Outcome 2: satisfaction (ordinal logistic / polr).
  formula_satis <- as.formula(paste0("Satisfaction ~ Label * ", mod))
  cat("\n===", "Satisfaction +", mod, "===\n")
  satis_model_mod <- MASS::polr(formula_satis, data = df, Hess = TRUE)

  satis_aov <- Anova(satis_model_mod)
  print(satis_aov)

  # polr gives no p-values; derive them from the t (Wald z) values.
  coefs <- summary(satis_model_mod)$coefficients
  pvals <- 2 * pnorm(-abs(coefs[, "t value"]))
  Satisfaction_Coefficients <- as.data.frame(cbind(coefs, "p value" = pvals))

  means_satis <- df %>%
    group_by(Label, !!sym(mod)) %>%
    summarise(
      Mean = round(mean(as.numeric(Satisfaction), na.rm = TRUE), 2),
      SD = round(sd(as.numeric(Satisfaction), na.rm = TRUE), 2),
      Median = median(as.numeric(Satisfaction), na.rm = TRUE),
      N = n(),
      .groups = "drop"
    )

  posthoc_satis_mod <- tryCatch(
    as.data.frame(emmeans(satis_model_mod, emm_formula_interaction)),
    error = function(e) data.frame()
  )

  # Outcome 3: sign-up (logistic regression + chi-square / Cramer's V).
  formula_logit <- as.formula(paste0("Sign_Up ~ Label * ", mod))
  cat("\n===", "Sign Up +", mod, "===\n")
  logit_model_mod <- glm(formula_logit, data = df, family = binomial)

  table_signup <- table(df$Label, df$Sign_Up)
  chisq_test <- chisq.test(table_signup)
  print(chisq_test)

  cramers_v <- sqrt(
    chisq_test$statistic / (sum(table_signup) * (min(dim(table_signup)) - 1))
  )

  emm <- emmeans(logit_model_mod, ~Label, type = "response")
  contrast_table <- as.data.frame(pairs(emm, adjust = "tukey"))

  result_list[[mod]] <- list(
    Learning_ANOVA = anova_tbl,
    Learning_Means = means_learning_mod,
    Learning_Posthoc = posthoc_learning_mod,
    Satisfaction_Coeffs = Satisfaction_Coefficients,
    Satisfaction_AOV = as.data.frame(satis_aov),
    Satisfaction_Means = means_satis,
    Satisfaction_Posthoc = posthoc_satis_mod,
    SignUp_Logit_Coeffs = as.data.frame(summary(logit_model_mod)$coefficients),
    SignUp_ChiSq = data.frame(
      statistic = as.numeric(chisq_test$statistic),
      parameter = as.numeric(chisq_test$parameter),
      p.value   = as.numeric(chisq_test$p.value)
    ),
    SignUp_CramersV = data.frame(CramersV = as.numeric(cramers_v)),
    SignUp_Posthoc_Tukey = contrast_table
  )
}
```

##### Export Results
```{r export-results-7}
clean_sheet <- function(x) gsub("[:/\\?\\*\\[\\] ]", "_", substr(x, 1, 31))

flat_result_list <- list()

for (mod in names(result_list)) {
  for (nm in names(result_list[[mod]])) {
    sheet_nm <- clean_sheet(paste(substr(mod, 1, 15), substr(nm, 1, 15), sep = "_"))
    flat_result_list[[sheet_nm]] <- result_list[[mod]][[nm]]
  }
}

write.xlsx(
  flat_result_list,
  file = "results/H3/Post_Survey_Moderation_Results_2.xlsx",
  rowNames = TRUE
)
```

## Reproducibility

```{r session-info}
sessionInfo()
```
