---
title: "Study 1 — Objective Benchmark: Thinking-Mode Mixed Models"
author: "Siyuan Huang"
date: "2026-01-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

set.seed(42)
```

# Overview

This document tests whether enabling a model's "thinking" mode affects
objective benchmark **accuracy** and **stability** (run-to-run SD). Both
outcomes are aggregated to the model × question level, logit-transformed,
and analysed with linear mixed models that include a thinking-mode ×
question interaction, a software fixed effect, and a by-model random
intercept.

## Packages

```{r packages}
library(dplyr)
library(readxl)
library(lme4)
library(lmerTest)
library(emmeans)
library(effectsize)
library(report)
```

## Load Data

Categorical design variables are coerced to factors; `Thinking_Model` is
ordered so that level `"1"` (thinking) is the reference.

```{r load-data}
df_obj <- read_excel("data/Study_1_Objective_Data.xlsx")

df_obj <- df_obj %>%
  mutate(
    Thinking_Model = factor(Thinking_Model, levels = c("1", "0")),
    software = factor(software),
    question = factor(question),
    model = factor(model),
    iteration = factor(iteration)
  )
```

## Subset Thinking-Mode Platforms

Only platforms that offer a distinct thinking mode are retained.

```{r subset-thinking}
thinking_model <- c("claude", "Grok", "deepseek", "gemini", "chatgpt")

df_obj_thinking <- df_obj %>%
  filter(software %in% thinking_model)
```

## Accuracy

### Aggregation

Accuracy is aggregated to the model × question × mode level and
logit-transformed (after bounding away from 0/1).

```{r accuracy-aggregation}
df_thinking_agg <- df_obj_thinking %>%
  group_by(model, question, Thinking_Model, software) %>%
  summarise(
    n = n(),
    Prop_Correct = mean(accuracy_rate),
    SD_Correct = sd(accuracy_rate),
    .groups = "drop"
  ) %>%
  mutate(
    Prop_Correct_adj = pmin(pmax(Prop_Correct, 1e-5), 1 - 1e-5),
    Logit_Prop = qlogis(Prop_Correct_adj)
  )
```

### Mixed Model

```{r accuracy-model}
mod_acc <- lmer(
  Logit_Prop ~ Thinking_Model * question + software + (1 | model),
  data = df_thinking_agg
)

summary(mod_acc)
anova(mod_acc)
effectsize::eta_squared(mod_acc, partial = TRUE)
emmeans(mod_acc, pairwise ~ Thinking_Model)
```

## Stability (Run-to-Run SD)

### Aggregation

The same aggregation is applied to the run-to-run SD of accuracy, again
logit-transformed.

```{r stability-aggregation}
df_SD_thinking_agg <- df_obj_thinking %>%
  group_by(model, software, question, Thinking_Model) %>%
  summarise(
    n = n(),
    Prop_Correct = mean(accuracy_rate),
    SD_Correct = sd(accuracy_rate),
    .groups = "drop"
  ) %>%
  mutate(
    Prop_SD_adj = pmin(pmax(SD_Correct, 1e-5), 1 - 1e-5),
    Logit_Prop_SD = qlogis(Prop_SD_adj)
  )
```

### Mixed Model

```{r stability-model}
mod_sd <- lmer(
  Logit_Prop_SD ~ Thinking_Model * question + software + (1 | model),
  data = df_SD_thinking_agg
)

summary(mod_sd)
anova(mod_sd)
effectsize::eta_squared(mod_sd, partial = TRUE)
emmeans(mod_sd, pairwise ~ Thinking_Model)
```

## Sensitivity Analysis: Paired-Only Platforms (Claude, Grok)

The main contrast pools five platforms, but only Claude (3.7 Sonnet vs
3.7 Sonnet Extended) and Grok (Grok 3 vs Grok 3 Think) toggle thinking
mode on the same underlying model; the DeepSeek, Gemini, and OpenAI pairs
cross model families or generations. Restricting the contrast to Claude
and Grok removes this cross-family confound (SI Appendix, Text S3).

```{r sensitivity-subset}
paired_platforms <- c("claude", "Grok")

df_obj_paired <- df_obj_thinking %>%
  filter(software %in% paired_platforms) %>%
  mutate(software = droplevels(software))
```

### Accuracy (Paired-Only)

```{r sensitivity-accuracy}
df_paired_agg <- df_obj_paired %>%
  group_by(model, question, Thinking_Model, software) %>%
  summarise(
    n = n(),
    Prop_Correct = mean(accuracy_rate),
    SD_Correct = sd(accuracy_rate),
    .groups = "drop"
  ) %>%
  mutate(
    Prop_Correct_adj = pmin(pmax(Prop_Correct, 1e-5), 1 - 1e-5),
    Logit_Prop = qlogis(Prop_Correct_adj)
  )

mod_acc_paired <- lmer(
  Logit_Prop ~ Thinking_Model * question + software + (1 | model),
  data = df_paired_agg
)

summary(mod_acc_paired)
anova(mod_acc_paired)
effectsize::eta_squared(mod_acc_paired, partial = TRUE)
emmeans(mod_acc_paired, pairwise ~ Thinking_Model)
```

### Stability (Paired-Only)

```{r sensitivity-stability}
df_SD_paired_agg <- df_obj_paired %>%
  group_by(model, software, question, Thinking_Model) %>%
  summarise(
    n = n(),
    Prop_Correct = mean(accuracy_rate),
    SD_Correct = sd(accuracy_rate),
    .groups = "drop"
  ) %>%
  mutate(
    Prop_SD_adj = pmin(pmax(SD_Correct, 1e-5), 1 - 1e-5),
    Logit_Prop_SD = qlogis(Prop_SD_adj)
  )

mod_sd_paired <- lmer(
  Logit_Prop_SD ~ Thinking_Model * question + software + (1 | model),
  data = df_SD_paired_agg
)

summary(mod_sd_paired)
anova(mod_sd_paired)
effectsize::eta_squared(mod_sd_paired, partial = TRUE)
emmeans(mod_sd_paired, pairwise ~ Thinking_Model)
```

### Robustness: OLS Without By-Model Random Intercept

In the paired-only subset each `model` maps to a single `Thinking_Model`
level, so the by-model random intercept has no within-model variance and
the mixed model is singular (variance = 0). Fixed-effect inference is
unaffected; as a robustness check we refit both with `lm()` (dropping
`(1 | model)`).

```{r sensitivity-ols}
mod_acc_paired_ols <- lm(
  Logit_Prop ~ Thinking_Model * question + software,
  data = df_paired_agg
)
summary(mod_acc_paired_ols)
anova(mod_acc_paired_ols)
effectsize::eta_squared(mod_acc_paired_ols, partial = TRUE)
emmeans(mod_acc_paired_ols, pairwise ~ Thinking_Model)

mod_sd_paired_ols <- lm(
  Logit_Prop_SD ~ Thinking_Model * question + software,
  data = df_SD_paired_agg
)
summary(mod_sd_paired_ols)
anova(mod_sd_paired_ols)
effectsize::eta_squared(mod_sd_paired_ols, partial = TRUE)
emmeans(mod_sd_paired_ols, pairwise ~ Thinking_Model)
```

## Supplementary Analysis: Distribution-Appropriate Models (No logit + clamp)

The models above logit-transform the proportions and SDs after clamping
them away from 0/1 with a fixed constant (`1e-5`). As a robustness
check we refit both outcomes with likelihoods that handle the 0/1
boundaries directly, with no clamp.

### Accuracy: Item-Level Binomial GLMM

Each iteration's outcome is the number of items correct out of those
scored for the task (Q1 = 6, Q2 = 5, Q3 = 6), with the same by-model random
intercept. The thinking × question interaction is not identifiable here
(several cells at 100% accuracy cause complete separation), so the model is
additive in thinking and question. (The interaction was non-significant in
the main analysis.)

```{r supp-accuracy}
items_per_task <- df_obj_thinking %>%
  filter(accuracy_rate > 0) %>%
  mutate(task_items = round(sum_score / accuracy_rate)) %>%
  distinct(question, task_items)

df_acc_glmm <- df_obj_thinking %>%
  left_join(items_per_task, by = "question") %>%
  mutate(correct = sum_score, incorrect = task_items - sum_score)

mod_acc_glmm <- glmer(
  cbind(correct, incorrect) ~ Thinking_Model + question + software + (1 | model),
  family = binomial, data = df_acc_glmm
)

summary(mod_acc_glmm)
# Thinking-mode contrast on the response (odds-ratio) scale, no clamp:
emmeans(mod_acc_glmm, pairwise ~ Thinking_Model, type = "response")
```

### Stability: Binary Run-to-Run Instability

```{r supp-stability}
df_stab_bin <- df_obj_thinking %>%
  group_by(model, software, question, Thinking_Model) %>%
  summarise(SD = sd(accuracy_rate), .groups = "drop") %>%
  mutate(unstable = as.integer(SD > 0))

# 1 = thinking (reference), 0 = standard
table(Thinking_Model = df_stab_bin$Thinking_Model,
      unstable = df_stab_bin$unstable)

# Exact test (no distributional assumptions, handles the small/zero cells)
fisher.test(table(df_stab_bin$Thinking_Model, df_stab_bin$unstable))

# Simple logistic regression for the odds ratio
mod_stab_bin <- glm(unstable ~ Thinking_Model, family = binomial, data = df_stab_bin)
summary(mod_stab_bin)
exp(cbind(OR = coef(mod_stab_bin), confint(mod_stab_bin)))
```

## Reproducibility

```{r session-info}
sessionInfo()
```
