---
title: "Study 1 — Objective Benchmark: Descriptive Results"
author: "Siyuan Huang"
date: "2026-01-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

set.seed(42)
```

# Overview

This document summarises the Study 1 objective benchmark: the per-item
accuracy of each large language model (platform × model × thinking mode)
on the six-question statistics task. Table 1 ranks models by overall
accuracy and flags the two best and two worst, which define the "Top"
and "Bottom" models carried into Study 2.

## Packages

```{r packages}
library(readxl)
library(dplyr)
library(stringr)
```

## Load Data

```{r load-data}
path <- "data/Study_1_Objective_Data.xlsx"
df <- read_excel(path)

if (!("accuracy_rate" %in% names(df))) {
  if ("sum_score" %in% names(df)) {
    df <- df %>% mutate(accuracy_rate = as.numeric(sum_score) / 6)
  } else if (all(paste0("score", 1:6) %in% names(df))) {
    df <- df %>%
      mutate(
        accuracy_rate = rowSums(across(all_of(paste0("score", 1:6))), na.rm = TRUE) / 6
      )
  } else {
    stop("Cannot find accuracy_rate (or sum_score / score1-6) to compute accuracy.")
  }
}
df <- df %>% mutate(accuracy_rate = as.numeric(accuracy_rate))
```

## Table 1: Model Accuracy Ranking

Two quantities are reported per platform × model × mode:

- **Accuracy** — items correct / items answered across all 17 items × 10
  iterations. Each task is item-weighted (Q1 = 6, Q2 = 5, Q3 = 6), so this
  is *not* the unweighted mean of the three task accuracies.
- **Stability** — mean of the within-task SDs (SD across the 10 iterations
  of a task, averaged over the 3 tasks); 0 = identical scores on every
  repetition. Unlike the SD of the pooled 30 scores, it excludes
  between-task difficulty.

Models are ranked by accuracy; the two highest and two lowest are flagged
as those carried into Study 2.

```{r table1}
tbl1_base <- df %>%
  mutate(
    Platform = case_when(
      software == "chatgpt" ~ "OpenAI",
      software == "deepseek" ~ "DeepSeek",
      software == "tongyi" ~ "Alibaba",
      software == "gemini" ~ "Google",
      software == "claude" ~ "Anthropic",
      software == "Grok" ~ "xAI",
      TRUE ~ as.character(software)
    ),
    Model = case_when(
      software == "chatgpt" & model == "o1" ~ "OpenAI o1",
      software == "chatgpt" & model == "gpt-4o" ~ "GPT-4o",
      software == "chatgpt" & model == "gpt-4.5" ~ "GPT-4.5",
      software == "chatgpt" & model == "gpt-o3" ~ "OpenAI o3",
      software == "chatgpt" & model == "gpt-o4-mini" ~ "OpenAI o4-mini",
      software == "chatgpt" & model == "gpt-o4-mini-high" ~ "OpenAI o4-mini-high",
      software == "deepseek" & model == "V3" ~ "DeepSeek-V3",
      software == "deepseek" & model == "R1" ~ "DeepSeek-R1",
      software == "tongyi" & model == "2.5" ~ "Qwen 2.5",
      software == "gemini" & str_detect(model, "2\\.5") ~ "Gemini 2.5 Pro",
      software == "gemini" & str_detect(model, "2\\.0") ~ "Gemini 2.0 Flash",
      software == "claude" & model == "3.7 Sonnet" ~ "Claude 3.7 Sonnet",
      software == "claude" & str_detect(model, "Extended") ~ "Claude 3.7 Sonnet (Extended)",
      software == "Grok" & model == "Grok 3 Think" ~ "Grok 3 Think",
      software == "Grok" & model == "Grok 3" ~ "Grok 3",
      TRUE ~ as.character(model)
    ),
    Mode = if_else(as.integer(Thinking_Model) == 1, "Thinking", "Standard")
  )

# Number of scored items per task (constant within task: Q1 = 6, Q2 = 5,
# Q3 = 6; 17 items total). Derived from the data so it stays correct if the
# task set changes. Used to weight each task's accuracy by its item count.
items_per_task <- tbl1_base %>%
  filter(accuracy_rate > 0) %>%
  mutate(task_items = round(sum_score / accuracy_rate)) %>%
  distinct(question, task_items)

tbl1_base <- tbl1_base %>%
  left_join(items_per_task, by = "question")

# Within-iteration (run-to-run) stability: SD across the 10 iterations of
# each task, then averaged over the 3 tasks. 0 = perfectly stable.
stability <- tbl1_base %>%
  group_by(Platform, Model, Mode, question) %>%
  summarise(task_sd = sd(accuracy_rate, na.rm = TRUE), .groups = "drop") %>%
  group_by(Platform, Model, Mode) %>%
  summarise(Stability = mean(task_sd, na.rm = TRUE), .groups = "drop")

tbl1 <- tbl1_base %>%
  group_by(Platform, Model, Mode) %>%
  summarise(
    n = n(),
    # Item-weighted accuracy: total items correct / total items answered
    # (each task contributes in proportion to its number of items).
    M = weighted.mean(accuracy_rate, w = task_items, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  left_join(stability, by = c("Platform", "Model", "Mode")) %>%
  mutate(
    Accuracy = sprintf("%.2f", M),
    Stability = sprintf("%.2f", Stability)
  ) %>%
  arrange(desc(M), Platform, Model) %>%
  mutate(
    Rank = row_number(),
    `Used in Study 2` = case_when(
      Rank <= 2 ~ "Top",
      Rank >= n() - 1 ~ "Bottom",
      TRUE ~ ""
    )
  ) %>%
  select(Rank, Platform, Model, Mode, Accuracy, Stability, `Used in Study 2`, n)

tbl1
```

## Reproducibility

```{r session-info}
sessionInfo()
```
